### 2013-04-20 article/sigproc-sp.tex
article artifacts

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}
\usepackage{url}

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%

\begin{document}

\title{Similar Article Detection Using Minhash Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Samet Ayhan\\
       \affaddr{University of Maryland, Department of Computer Science}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{sayhan@cs.umd.edu}
% 2nd. author
\alignauthor Joshua Bradley\\
       \affaddr{University of Maryland, Department of Computer Science}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{jgbradley@cs.umd.edu}
% 3rd. author
\alignauthor Sarah Weissman\\
       \affaddr{University of Maryland, College of Information Studies}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{sweissman@umd.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

\date{19 April 2013}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
In this paper, we describe a novel similarity detection algorithm that utilizes locality sensitive hashing technique on MapReduce framework. The algorithm has been designed and implemented to detect similar articles using large Wikipedia dumps, in compressed or uncompressed forms.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.2.4}{Information Systems}{Database Management}[Systems]

\terms{Algorithms, Design, Performance}

\keywords{Big Data, Data Analytics, Data Warehouse, Data Stream Management} % NOT required for Proceedings

\section{Introduction}
Wikipedia has a history of generating controversy over editorial quality and factual correctness. Although some studies have found Wikipedia’s accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors [1]. Since Wikipedia may be edited anonymously, information is often freely copied between web sources or other Wikipedia articles. Additionally, many articles in Wikipedia lack citations. There is little mechanism for detecting and correcting such errors. One potential source of error on Wikipedia is factual information that varies over time and is not updated. Wilkinson found that the distribution of article edits has a long tail, meaning that a small number of articles have many edits while most articles have few, and that number of edits is directly related to article quality. Articles with low edits, and low editorial attention, are less likely to be updated when new information becomes available \cite{wilkinson:wiki}.

As a step toward identifying factual errors, we investigated the problem of finding near duplicate sentences on Wikipedia. Such near duplicate sentences may reflect factual information that has been updated in one article and not another, or merely inconsistencies that should be flagged and addressed. We used the MapReduce computing framework and locality sensitive hashing techniques to compare sentences and identify near duplicates.

The rest of this paper is organized as follows: In Section 2, we present related work, in Section 3, we explain the algorithm utilizing locality sensitive hashing, in Section 4, we present the working application within MapReduce framework. In Section 5, we discuss our experiments with various Wikipedia datasets. The final section contains concluding remarks and future work.

\section{Related Work}
Related work goes here...

\section{Algorithm Utilizing Locality Sensitive Hashing}
In this section, we introduce the algorithm that utilizes the locality sensitive hashing.

\subsection{Design}
We explain the design here...

\subsection{Implementation}
We explain the implementation here...

\section{Working Application}
We explain the working application here...

\begin{figure}
\centering
\epsfig{file=figure1.eps,height=1in,width=2.2in}
\caption{Workflow within MapReduce Framework.}
\end{figure}

\section{Experiments and Discussion}
In this section, we discuss some of the issues we encountered regarding data representation, and archived data loading. We also present the performance optimizations we realized.

\subsection{Optimizations}	 
We explain optimizations here...

\subsubsection{Optimization-1}
An optimization we realized...

\subsubsection{Optimization-2}
Another optimization we realized...

\begin{figure*}
\centering
\epsfig{file=figure2.eps,height=1.5in,width=7in}
\caption{Some figure.}
\end{figure*}

Illustrated in Figure 2, explain the figure here...

\section{Conclusion and Future Work}
Conclusion goes here...

\section{Acknowledgments}
We would like to thank all of the anonymous contributors. We would especially like to thank Jimmy Lin for his advise and directions.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\balancecolumns
% That's all folks!
\end{document}

### 2013-04-20 src/main/MinhashWikipediaPages.java
Added error checking to wiki processing.

@@ -130,6 +130,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
 
         public void map(LongWritable key, WikipediaPage p, OutputCollector<ArrayListOfLongsWritable, Text> output,
                 Reporter reporter) throws IOException {
+
             if (p.isRedirect()) {
                 reporter.incrCounter(PageTypes.REDIRECT, 1);
 
@@ -146,9 +147,11 @@ public class MinhashWikipediaPages extends Configured implements Tool {
             } else {
                 reporter.incrCounter(PageTypes.NON_ARTICLE, 1);
             }
-            if(!p.isArticle()) return;   
+            if(!p.isArticle() || p.isEmpty()) return;   
             //System.out.println(p.getTitle());
-            String line = p.getContent().replace("\n", " ");
+            String content = p.getContent();
+            if(content == null) return;
+            String line = content.replace("\n", " ");
             Matcher m = sentenceregex.matcher(line);
 
             // Assume each doc is on its own line; track sentence number by counting
@@ -218,7 +221,6 @@ public class MinhashWikipediaPages extends Configured implements Tool {
               }
               sentencect++;
             }
-            //System.out.println("done");           
           }
     
     public void configure(JobConf job) {

### 2013-04-20 src/main/courseproj/wikipedia/WikipediaPage.java

@@ -163,7 +163,7 @@ public abstract class WikipediaPage extends Indexable {
    */
   public String getContent() {
     String s = getWikiMarkup();
-
+    if(s == null) return null;
     // Bliki doesn't seem to properly handle inter-language links, so remove manually.
     if(LANG_LINKS.matcher(s).matches()){
         s = LANG_LINKS.matcher(s).replaceAll(" ");
@@ -215,9 +215,9 @@ public abstract class WikipediaPage extends Indexable {
    * Returns the text of this page.
    */
   public String getWikiMarkup() {
-    if (textStart == -1)
+    if (textStart == -1 || textStart + 27 > textEnd)
       return null;
-
+    
     return page.substring(textStart + 27, textEnd);
   }
 

### 2013-04-20 src/main/courseproj/wikipedia/language/EnglishWikipediaPage.java

@@ -54,18 +54,22 @@ public class EnglishWikipediaPage extends WikipediaPage {
     // parse out title
     int start = s.indexOf(XML_START_TAG_TITLE);
     int end = s.indexOf(XML_END_TAG_TITLE, start);
+    if(start < 0 || end < 0){
+        textStart = -1;
+        return;
+    }
     this.title = StringEscapeUtils.unescapeHtml(s.substring(start + 7, end));
-
+    
     // determine if article belongs to the article namespace
     start = s.indexOf(XML_START_TAG_NAMESPACE);
     end = s.indexOf(XML_END_TAG_NAMESPACE);
-    this.isArticle = start == -1 ? true : s.substring(start + 4, end).trim().equals("0");
+    this.isArticle = (start == -1 || end == -1 || start > end) ? true : s.substring(start + 4, end).trim().equals("0");
     // add check because namespace tag not present in older dumps
     
     // parse out the document id
     start = s.indexOf(XML_START_TAG_ID);
     end = s.indexOf(XML_END_TAG_ID);
-    this.mId = s.substring(start + 4, end);
+    this.mId = (start == -1 || end == -1 || start > end) ? "0" : s.substring(start + 4, end);
 
     // parse out actual text of article
     this.textStart = s.indexOf(XML_START_TAG_TEXT);

### 2013-04-20 src/main/MinhashWikipediaPages.java
Changed the output val class to separate docid from sentence text. Removing exact duplicates from output for now.

@@ -17,6 +17,7 @@
 
 
 import java.io.IOException;
+import java.util.HashMap;
 import java.util.Iterator;
 import java.util.Random;
 import java.util.regex.Matcher;
@@ -53,6 +54,7 @@ import courseproj.wikipedia.WikipediaPage;
 import courseproj.wikipedia.WikipediaPageInputFormat;
 import edu.umd.cloud9.io.array.ArrayListOfLongsWritable;
 import edu.umd.cloud9.io.pair.PairOfLongInt;
+import edu.umd.cloud9.io.pair.PairOfStrings;
 
 public class MinhashWikipediaPages extends Configured implements Tool {
   private static final Logger LOG = Logger.getLogger(MinhashWikipediaPages.class);
@@ -86,7 +88,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
   };
 
   private static class SentenceMapperRegex extends MapReduceBase implements
-      Mapper<LongWritable, WikipediaPage, ArrayListOfLongsWritable, Text> {
+      Mapper<LongWritable, WikipediaPage, ArrayListOfLongsWritable, PairOfStrings> {
 	  
         static long rseed;
         static long seeds[];
@@ -108,7 +110,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
         // The document-sentence identifier
         static final PairOfLongInt DOCSENT = new PairOfLongInt();
         // for testing
-        static final Text SENTENCE = new Text();
+        static final PairOfStrings SENTENCE_ID = new PairOfStrings();
 	    
 	    
 	    //Adapted from http://stackoverflow.com/questions/5553410/regular-expression-match-a-sentence
@@ -128,7 +130,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
 	        Pattern.MULTILINE | Pattern.COMMENTS);
 	    
 
-        public void map(LongWritable key, WikipediaPage p, OutputCollector<ArrayListOfLongsWritable, Text> output,
+        public void map(LongWritable key, WikipediaPage p, OutputCollector<ArrayListOfLongsWritable, PairOfStrings> output,
                 Reporter reporter) throws IOException {
 
             if (p.isRedirect()) {
@@ -204,7 +206,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
               // If the sentence meads min shingle ct requirements, emit the signature and the sentence/doc ID
               if(shinglect > MINLEN){
                   DOCSENT.set(key.get(), sentencect);
[…]

### 2013-04-20 src/main/MinhashWikipediaPages.java
Fixed bug where extra entries were added to minhash ector. Removing commas and double quotes from input string.

@@ -34,7 +34,6 @@ import org.apache.hadoop.conf.Configured;
 import org.apache.hadoop.fs.FileSystem;
 import org.apache.hadoop.fs.Path;
 import org.apache.hadoop.io.LongWritable;
-import org.apache.hadoop.io.Text;
 import org.apache.hadoop.mapred.FileInputFormat;
 import org.apache.hadoop.mapred.FileOutputFormat;
 import org.apache.hadoop.mapred.JobClient;
@@ -109,7 +108,8 @@ public class MinhashWikipediaPages extends Configured implements Tool {
         
         // The document-sentence identifier
         static final PairOfLongInt DOCSENT = new PairOfLongInt();
-        // for testing
+        // for testing - output sentence and ID - we could output just an ID or a hash of the 
+        // entire sentence instead of the sentence itself in real implementation
         static final PairOfStrings SENTENCE_ID = new PairOfStrings();
 	    
 	    
@@ -153,7 +153,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
             //System.out.println(p.getTitle());
             String content = p.getContent();
             if(content == null) return;
-            String line = content.replace("\n", " ");
+            String line = content.replace("\n", " ").replace("  ", " ").replace(",","");
             Matcher m = sentenceregex.matcher(line);
 
             // Assume each doc is on its own line; track sentence number by counting
@@ -244,8 +244,10 @@ public class MinhashWikipediaPages extends Configured implements Tool {
         sigseed = r.nextLong();
         hashfamily = new MultiplyShiftHash(NHASHOUTPUTBITS,seeds);
         MINHASH = new long[NHASH];
-        for(int i=0; i<K; i++){
-            SIG.add(0);
+        if(SIG.size() != K){
+            for(int i=0; i<K; i++){
+                SIG.add(0);
+            }
         }
         
     }
@@ -276,6 +278,8 @@ public class MinhashWikipediaPages extends Configured implements Tool {
     }
     */
 
+      // Uniquify the results so that we don't keep identical sentences (although these
+      // may be interesting in their own right
       static final HashMap<String,String> uniqueMap = new HashMap<String,String>();
       static final PairOfStrings SENTENCE_ID = new PairOfStrings();
       @Override
@@ -289,6 +293,7 @@ public class MinhashWikipediaPages extends Configured implements Tool {
             PairOfStrings val = values.next();
             uniqueMap.put(val.getLeftElement(), val.getRightElement());
[…]

### 2013-04-21 article/sigproc-sp.tex
completed Related Work section

@@
 \section{Related Work}
-Related work goes here...
+A number of techniques have been implemented to identify similarity between documents in the literature.
+These techniques usually differ in terms of corpus of interest, signature representing the document, feature-set determined by the system, and the end goal.
+In addition to these differences, one can also consider the efficiency and scalability of the system, overall.
+
+In this section, we will go over some of theses techniques offered in the literature. Additionally, we will highlight our novel contribution.
+
+Broder et al.
+introduced shingling to compute document similarity and containment.
+They also presented methods for using a subset of shingles while still allowing similarity and containment computations \cite{broder:resemblance}.
+
+Seo et al.
+defined a general framework for text reuse detection.
+They introduced Discrete Cosine Transform (DCT) fingerprinting for general or local text reuse detection with high accuracy and efficiency \cite{seo:dct}.
+
+Zhang et al.
+presented partial duplicate detection algorithm using sequence matching that transforms partial-duplicate detection task into three MapReduce jobs: 1.Indexing, 2.Sequence Duplicate Detection, 3.Sequence Matching \cite{zhang:pdc}.
+
+Hajishirzi et al.
+introduced an adaptive near-duplicate detection (ANDD) method by extending term-weighting framework to learn k-gram vectors.
+Provided that each document was represented by an informative real k-gram vector, similarity measures were computed to come up with predicted values of near-duplicates \cite{hajishirzi:andd}.
+
+Lin described three MapReduce algorithms for computing pairwise similarity on document collections: 1.Based on brute force, 2.Treated as large-scale ad hoc retrieval, 3.Based on Cartesian product of postings lists \cite{lin:brute}.
+
+Manku et al.
+used Charikar's fingerprinting technique for developing near-duplicate detection system.
+They presented an algorithmic technique for identifying existing f-bit fingerprints that differ from a given fingerprint in at most k bit-positions, for small k.
+They demonstrated that their system is useful not only for batch but also for online processing \cite{manku:web}.
+
+Bendersky et al.
+examined two information flow representations: the timeline and the link graph.
+They proposed several simple unsupervised techniques for timeline construction link graph analysis \cite{bendersky:timeline}.
+
+In order to handle large Wikipedia dumps with the order of tens or hundreds of gigabytes and even a few terabytes, we used MapReduce framework in this work, that was introduced by Dean and Ghemawat \cite{dean:mapreduce}.
+The implementation is able to stream the compressed bz2 dumps and feed into mappers and reducers for further processing, which will be detailed in the following sections.
 

### 2013-04-21 article/sigproc-sp.tex
Updated abstract, and intro sections

@@
 
-\title{Similar Article Detection Using Minhash Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
+\title{Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
 %
@@
 \begin{abstract}
-In this paper, we describe a novel similarity detection algorithm that utilizes locality sensitive hashing technique on MapReduce framework.
+The growth of Internet has enabled collaboration and cooperation on a large scale, resulting in an abundant number of near-duplicate web documents.
+The range of occurrences is even more evident within Wikipedia articles, due to its editing largely being open.
+Except for particularly sensitive and/or vandalism-prone pages that are "protected" to some degree from editing, the reader of an article can edit the text by copying from another article without needing approval.
+Although we are not inspired to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
+
+In this paper, we describe a novel similarity detection algorithm that utilizes locality sensitive hashing (LSH) technique on MapReduce framework.
 The algorithm has been designed and implemented to detect similar articles using large Wikipedia dumps, in compressed or uncompressed forms.
+Experimental results appear to support that our method is able to efficiently and effectively detect similar articles from large Wikipedia dumps.
 \end{abstract}
@@
 % A category with the (minimum) three required fields
-\category{H.2.4}{Information Systems}{Database Management}[Systems]
+\category{H.3.3}{Information Storage and Retrieval}[Information Search and Retrieval]
 
@@
 
-\keywords{Big Data, Data Analytics, Data Warehouse, Data Stream Management} % NOT required for Proceedings
+\section{Introduction}
+The online encyclopedia Wikipedia is a multilingual, free resource with its 26 million articles.
+All these articles with over 4.2 million in the English Wikipedia alone, are written collaboratively by volunteers around the world.
+Almost all of its articles can be edited by anyone with access to the site, and it has about 100,000 active contributors.
+In light of these facts, it is clear that unprecedented example of such a large-scale collaboration may result in duplicate or near duplicate articles in relatively granular level such as at sentence or multi-gram granularity \cite{wiki:weblink}
 
-\section{Introduction}
-Wikipedia has a history of generating controversy over editorial quality and factual correctness.
-Although some studies have found Wikipedia’s accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors [1].
+Furthermore, Wikipedia has a history of generating controversy over editorial quality and factual correctness.
+Although some studies have found Wikipedia’s accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.
 Since Wikipedia may be edited anonymously, information is often freely copied between web sources or other Wikipedia articles.
@@
 Such near duplicate sentences may reflect factual information that has been updated in one article and not another, or merely inconsistencies that should be flagged and addressed.
-We used the MapReduce computing framework and locality sensitive hashing techniques to compare sentences and identify near duplicates.
+
+In order to come up with a novel algorithm that would allow us to detect near duplicate Wikipedia articles, we decided that we needed to answer the following questions, first:
+\begin{itemize}
+\item What is the most appropriate LSH technique to apply? Edit distance seems like a reasonable metric for near duplicate sentences, but no LSH family for edit distance is known to exist.
+\item Compare different sentence similarity techniques for effectiveness. 
+\item What is the appropriate granularity for analysis? Is comparing multiple consecutive sentences more effective than comparing single sentences? Similarly, what is the best shingle size?
+\item How well do techniques for detecting near duplicate documents work when applied at the sentence level?
+\item Do near duplicate sentences correspond to factual errors? Can these errors be automatically flagged or corrections suggested?
+\end{itemize}
+
+Along with these questions, we also considered the scalability and efficiency issues due to large size of Wikipedia dumps.
+To address these issues, we used the MapReduce computing framework and LSH techniques to group sentences with the same signatures and identify near duplicates.
 

### 2013-04-27 src/main/EditDistance.java
Class for edit distance calculation and clustering of results.

@@ -1,0 +1,167 @@
+
+
+import java.io.BufferedReader;
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+public class EditDistance {
+
+	
+	static public long dist(String s1, String s2){
+		long distance[][] = new long[s1.length()+1][s2.length()+1];
+		for(int i=0;i<=s1.length();i++){
+			distance[i][0] = i;
+		}
+
+		for(int j=0;j<=s2.length();j++){
+			distance[0][j] = j;
+		}
+
+		for(int i=1;i<=s1.length();i++){
+			int cost;
+			for(int j=1;j<=s2.length();j++){
+			    if(s1.substring(i-1,i).equals(s2.substring(j-1,j))){
+					cost = 0;
+			    }else{
+					cost = 1;
+			    }
+
+			    distance[i][j] = Math.min(distance[i-1][j] + 1,
+					     Math.min(distance[i][j-1] + 1,
+						 		distance[i-1][j-1] + cost));
+			    //System.out.println("i= " + i + " j= " + j);
+			    //System.out.println(s1.substring(i-1,i) + " " + s2.substring(j-1,j));
+			    if(i>1 && j>1 && s1.substring(i-1,i).equals(s2.substring(j-2,j-1))
+			       && s1.substring(i-2,i-1).equals(s2.substring(j-1,j))){
+			    	distance[i][j] = Math.min(distance[i][j],distance[i-1][j-2] + cost);
+			    }
+
+			    //# Some way to weight differences at beginning of addressss more?
+			    //#if($i < length($s1/2) && $j < length($s2/2)){
+				//#$d{$i}{$j} += 1;
+			    //#}
+			}
+	    }
+/*
+		     for(int i=0;i<=s1.length();i++){
+		     	for(int j=0;j<=s2.length();j++){
+		     	    System.out.println("d["+i+"]["+j+"] = " + distance[i][j]);
+		     	}
+		    }
+*/
+		    return distance[s1.length()][s2.length()];
+	}
+	
+	public static void main(String args[]){
+		
+		  if(args.length != 1){
+				System.out.println("Usage: EditDistance <filein>\n");
+				System.exit(-1);
+			}
[…]

### 2013-04-27 article/sigproc-sp.tex

@@
 \section{Conclusion and Future Work}
-Conclusion goes here...
+This paper presents our work on near-duplicate detection of Wikipedia articles at various granularity levels using LSH technique.
+Our novel MapReduce algorithm tackles the problem by transforming it into more manageable pieces where each piece handled in parallel.
+Our unique contribution includes empirical analysis of signatures belonging to Wikipedia articles at k-gram level.
+Experimental results verify that the proposed method is able to effectively and efficiently detect similar articles.
+
+In the future, we would like to investigate revision histories of these articles, correlate them with their timestamps, and better relate similarities based on temporal dimensions.
 

### 2013-04-27 src/main/courseproj/wikipedia/BuildWikipediaDocnoMapping.java
Added code from cloud9 for making the docno mapping.

@@ -1,0 +1,226 @@
+/*
+ * Cloud9: A MapReduce Library for Hadoop
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License"); you
+ * may not use this file except in compliance with the License. You may
+ * obtain a copy of the License at
+ *
+ * http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or
+ * implied. See the License for the specific language governing
+ * permissions and limitations under the License.
+ */
+
+package courseproj.wikipedia;
+
+import java.io.IOException;
+import java.util.Iterator;
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.GnuParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.ParseException;
+import org.apache.hadoop.conf.Configured;
+import org.apache.hadoop.fs.FileSystem;
+import org.apache.hadoop.fs.Path;
+import org.apache.hadoop.io.IntWritable;
+import org.apache.hadoop.io.LongWritable;
+import org.apache.hadoop.mapred.Counters;
+import org.apache.hadoop.mapred.FileInputFormat;
+import org.apache.hadoop.mapred.FileOutputFormat;
+import org.apache.hadoop.mapred.JobClient;
+import org.apache.hadoop.mapred.JobConf;
+import org.apache.hadoop.mapred.MapReduceBase;
+import org.apache.hadoop.mapred.Mapper;
+import org.apache.hadoop.mapred.OutputCollector;
+import org.apache.hadoop.mapred.Reducer;
+import org.apache.hadoop.mapred.Reporter;
+import org.apache.hadoop.mapred.RunningJob;
+import org.apache.hadoop.mapred.TextOutputFormat;
+import org.apache.hadoop.util.Tool;
+import org.apache.hadoop.util.ToolRunner;
+import org.apache.log4j.Logger;
+
+/**
+ * Tool for building the mapping between Wikipedia internal ids (docids) and sequentially-numbered
+ * ints (docnos).
+ *
+ * @author Jimmy Lin
[…]

### 2013-04-29 article/sigproc-sp.tex
Started algorithm and implementation sections.

@@
        \affaddr{College Park, Maryland 20740}\\
-       \email{sweissman@umd.edu}
+       \email{sew@umd.edu}
 }
@@
 \section{Algorithm Utilizing Locality Sensitive Hashing}
+
 In this section, we introduce the algorithm that utilizes the locality sensitive hashing.
 
+In order to measure document similarity we use a common LSH technique known as minhashing \cite{}.
+A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
+In our case input documents are sentences.
+Each sentence is broken up into n-gram ``shingles''.
+For each shingle set $S$ we calculate $\{min_{s \in S}(F_i(s)\}$, the set of minimum hashes over the hash family.
+The signature on a document d is a vector of $K$ minhashes from the set of minimum hashes.
+In order to minimize false negatives we apply the technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.
+
 \subsection{Design}
-We explain the design here...
+Since signature techniques such as LSH are easily parallelized we designed our algorithm around the MapReduce framework.
 
-\subsection{Implementation}
-We explain the implementation here...
+Describe MapReduce.
+
+Because the minhash technique is parametrized by several values, including shingle length, signature vector size and number of signatures calculated, these values can also be considered as inputs for the MapReduce algorithm.
+
+\begin{table}
+MapReduce pseudocode:
+\begin{verbatim}
+initialize(){
+ # configure and set up algorithm parameters
+ # F = hash family;
+ # L = shingle length;
+ # K = vector length;
+ # N = number of signatures to emit;
+}
+
+map(docid d, wikipage p){
+  int sentence ct = 0;
+  while s = nextSentence(p){
+    shingles = shingleSet(s,L);
+    minhashes = new List(|F|);
+    for i = 1 ... |F|:
+      minhashes[i] = Infinity;
+    for g in shingles:
+      for i = 1 ... |F|:
+        minhashes[i] = min(F_i(g),minhashes[i]);
+    for i = 1 ... N:
+      sig = select(K, minhahses);
+      emit(sig,(docid,sentencect));
+    sentencect++;
+  }
+}
+\end{verbatim}
+
+\begin{verbatim}
+reduce(signature sig, sentenceids [(d1,s1),(d2,s2) ...]){
+  if [[(d1,s1),(d2,s2) ... ]| > 1:
+    emit(sig, [(d1,s1), (d2,s2), ...]);
+}
+\end{verbatim}
+\end{table}
+
+\subsection{Implementation Details}
+
+Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 library for parsing Wikipedia page text from the Wikipedia XML dump format.
+Sentences are parsed out over each document using a regular expression.
+Sentences that are too large or too small are discarded.
+The family of hash functions is implemented using a ``Multiply Shift''  \cite{} hashing scheme and is generated from a random seed using the Java Random class.
+The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
 
@@
 
-\subsection{Optimizations}	 
+\subsection{Optimization}
+
 We explain optimizations here...
 
-\subsubsection{Optimization-1}
+\subsubsection{Parameter Optimization}
+
+As mentioned above the minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
+Each of these parameters has an impact on the error rates in the minhash output.
+
 An optimization we realized...

### 2013-04-30 article/sigproc-sp.tex
Added new section on parameter tuning and how Jaccard and edit distance compare.

@@
 
+\section{Parameter Tuning}
+
+As mentioned above the minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
+Each of these parameters has an impact on the error rates in the minhash output.
+
+\subsection{Jaccard Similarity and Edit Distance}
+
+Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
+A more natural measure to use for this application is edit distance.
+There is no known locality sensitive hashing family for edit distance \citation{}.
+
+In order to estimate Jaccard similarity of sentences $X$ and $Y$ in terms of edit distance we assume that $X$ and $Y$ are both of length $N$ and that their shingle sets are of maximum size (i.e.
+all shingles are unique).
+Also assume that $X$ and $Y$ have edit distance $e$.
+Additionally, to simplify our calculations, we assume that edits are localized so that no shingle overlaps more than one edit.
+
+(WLOG) Let $S$ be the set of shingles for X and let $S_o$ be the set of shingles of X that overlap edits.
+The maximum number of unique shingles for a sentence of length $N$ is $N - L + 1 = |S|$.
+Also, we can see that $e \le |S_o| \le e + L - 1$.
+Since edits at the start or end of the sentence will overlap with fewer shingles than edit mid-sentence.
+
+Now we can define $|X \cup Y|$ and $|X \cap Y|$ in terms $S$ and $S_o$ as follows:
+\begin{eqnarray*}
+|X \cap Y| & = & |S| - |S_o| \\
+|X \cup Y| & = & 2*|S_o| + |X \cap Y| \\
+           & = & |S_o| + |S|
+\end{eqnarray*}
+
+Plugging in the values above for $|S_o|$ and $|S|$ we get:
+
+\begin{eqnarray*}
+E + N - L + 1  \le & |X \cup Y| & \le E + N \\
+N - L + 1 - E  \ge & |X \cap Y| & \ge N - 2L - E + 2 \\
+\end{eqnarray*}
+\begin{eqnarray*}
+\frac{N - L - E + 1 }{N - L + e + 1} >= & J(X,Y) & >= \frac{N - 2L - E + 2}{N + E}
+\end{eqnarray*}
+
+Note that, at least under this set of assumptions, the Jaccard similarity is always less than the ``edit similarity'' (1 - normalized edit distance):
+
+\begin{eqnarray*}
+J(X,Y) & <= & \frac{N - E}{E + N - L + 1} - \frac{L - 1}{E + N - L + 1} \\
+       & <= & \frac{N - E}{N} \\ 
+       & =  & 1 - \frac{E}{N}
+\end{eqnarray*}
+
+Finally we can divide through the equations for J(X,Y) by N, which gives us:
+
+\begin{eqnarray*}
+\frac{1 - l - e}{1 - l + e} >= J(X,Y) >= \frac{1 - 2l - e}{1 + e}
+\end{eqnarray*}
+
+where $l$ is relative shingle size and $e$ is normalized edit distance.
+
+Note that as relative shingle size goes to 0 there is a nice convergence for Jaccard similarity:
+\[\lim_{l->0}J(X,Y) = \frac{1 - e}{1 + e}\]
+
+\begin{figure*}
+\centering
+\epsfig{file=jac-ed-chart.eps,height=4in,width=6in}
+\caption{Jaccard Similarity vs. normalized edit distance.}
+\label{jac-ed}
+\end{figure*}
+
+As we would expect, Jaccard similarity decreases as edit distance increases, but it also decreases as shingle length increases.
+Figure \ref{fig:jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$.
+At $l = .05$ and $e = .2$ our estimate for Jaccard similarity has already fallen to the range [0.58,0.65].
+Clearly setting $l$ too high can increase the false positive rate, but setting $l$ too low will increase the false positive rate, since it will increase the size of the intersection of the shingle sets.
+
+\subsection{False positives}
+
+\begin{figure*}
+\centering
+\epsfig{file=edgrid.eps,width=7in}
+\caption{}
+\label{ed-grid}
+\end{figure*}
+
 \section{Experiments and Discussion}
@@
 
-\subsubsection{Parameter Optimization}
-
-As mentioned above the minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
-Each of these parameters has an impact on the error rates in the minhash output.
+\subsubsection{Optimization1}
 

### 2013-05-08 article/sigproc-sp.tex
Updated/cleaned introduction a little.

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
@@
 
-%
 \def\sharedaffiliation{%
@@
 \begin{tabular}{c}}
-%
 
@@
 \title{Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
 
-\numberofauthors{5} %  in this sample file, there are a *total*
+\numberofauthors{3} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 The growth of Internet has enabled collaboration and cooperation on a large scale, resulting in an abundant number of near-duplicate web documents.
-The range of occurrences is even more evident within Wikipedia articles, due to its editing largely being open.
-Except for particularly sensitive and/or vandalism-prone pages that are "protected" to some degree from editing, the reader of an article can edit the text by copying from another article without needing approval.
+The range of near-duplicate occurrences is even more evident within Wikipedia articles, due to its editing largely being open to the online community.
+Except for particularly sensitive and/or vandalism-prone pages that are "protected" to some degree from editing, the reader of an article can edit the text by copying from another article without prior approval.
+There is no current automated mechanism for truth validation.
 Although we are not inspired to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
 
-In this paper, we describe a novel similarity detection algorithm that utilizes locality sensitive hashing (LSH) technique on MapReduce framework.
+In this paper, we describe a novel similarity detection algorithm that utilizes a locality sensitive hashing (LSH) technique on the MapReduce framework.
 The algorithm has been designed and implemented to detect similar articles using large Wikipedia dumps, in compressed or uncompressed forms.
-Experimental results appear to support that our method is able to efficiently and effectively detect similar articles from large Wikipedia dumps.
+Experimental results appear to support that our method is able to efficiently and effectively detect similar articles across Wikipedia.
 \end{abstract}
@@
 
-\terms{Algorithms, Design, Performance}
+\terms{Algorithms, Design, MapReduce}
 
@@
 The online encyclopedia Wikipedia is a multilingual, free resource with its 26 million articles.
-All these articles with over 4.2 million in the English Wikipedia alone, are written collaboratively by volunteers around the world.
-Almost all of its articles can be edited by anyone with access to the site, and it has about 100,000 active contributors.
-In light of these facts, it is clear that unprecedented example of such a large-scale collaboration may result in duplicate or near duplicate articles in relatively granular level such as at sentence or multi-gram granularity \cite{wiki:weblink}
+All these articles, with over 4.2 million in English alone, are written collaboratively by volunteer contributors around the world.
+Most articles can be edited by anyone with internet access, thus there are currently approximately 100,000 active contributors.
+In light of these facts, it is clear that the unprecedented example of such a large-scale collaboration effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity \cite{wiki:weblink}
 
@@
 Although some studies have found Wikipedia’s accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.
-Since Wikipedia may be edited anonymously, information is often freely copied between web sources or other Wikipedia articles.
+Since Wikipedia may be edited anonymously, information is often freely copied between web sources and even between Wikipedia articles.
 Additionally, many articles in Wikipedia lack citations.
@@
 One potential source of error on Wikipedia is factual information that varies over time and is not updated.
-Wilkinson found that the distribution of article edits has a long tail, meaning that a small number of articles have many edits while most articles have few, and that number of edits is directly related to article quality.
-Articles with low edits, and low editorial attention, are less likely to be updated when new information becomes available \cite{wilkinson:wiki}.
+Wilkinson found that the distribution of article edits has a long tail, meaning that a small number of articles have many edits while most articles have few, and that the number of edits is directly related to article quality.
+Articles with low edits and low editorial attention, are less likely to be updated when new information is available \cite{wilkinson:wiki}.
 
@@
 \begin{itemize}
-\item What is the most appropriate LSH technique to apply? Edit distance seems like a reasonable metric for near duplicate sentences, but no LSH family for edit distance is known to exist.
+\item What is the most appropriate LSH technique to apply?
+Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
+Currently, no LSH family for edit distance is known to exist.
 \item Compare different sentence similarity techniques for effectiveness. 
@@
 \item How well do techniques for detecting near duplicate documents work when applied at the sentence level?
-\item Do near duplicate sentences correspond to factual errors? Can these errors be automatically flagged or corrections suggested?
+\item Do near duplicate sentences correspond to factual errors? Can these errors be automatically detected and/or corrections suggested?
 \end{itemize}
 
-Along with these questions, we also considered the scalability and efficiency issues due to large size of Wikipedia dumps.
+Along with these questions, we also considered the scalability and efficiency issues due to the large size of Wikipedia.
 To address these issues, we used the MapReduce computing framework and LSH techniques to group sentences with the same signatures and identify near duplicates.
@@
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
 \bibliographystyle{abbrv}
 \bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
+
 %APPENDICES are optional

### 2013-05-08 article/sigproc-sp.tex
Fixed wrong email address
Fixed some font formatting errors

@@
 \usepackage{url}
+\usepackage{verbatim}
+\usepackage{microtype}
 
@@
        \affaddr{College Park, Maryland 20740}\\
-       \email{jgbradley@cs.umd.edu}
+       \email{jgbrad1@cs.umd.edu}
 % 3rd. author
@@
 
-In this section, we introduce the algorithm that utilizes the locality sensitive hashing.
+In this section, we introduce the algorithm that utilizes locality sensitive hashing.
 
-In order to measure document similarity we use a common LSH technique known as minhashing \cite{}.
+In order to measure document similarity we use a common LSH technique known as MinHash \cite{}.
 A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
-In our case input documents are sentences.
+In our case, we denote ''documents'' to mean sentences found within the content of Wikipedia articles.
 Each sentence is broken up into n-gram ``shingles''.
-For each shingle set $S$ we calculate $\{min_{s \in S}(F_i(s)\}$, the set of minimum hashes over the hash family.
-The signature on a document d is a vector of $K$ minhashes from the set of minimum hashes.
-In order to minimize false negatives we apply the technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.
+For each shingle set $S$ we calculate the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family.
+The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes.
+In order to minimize false negatives we apply a technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.
 
 \subsection{Design}
-Since signature techniques such as LSH are easily parallelized we designed our algorithm around the MapReduce framework.
+Since signature techniques such as LSH are embarrassingly parallel, we designed our algorithm around the MapReduce framework.
 
@@
 
-Because the minhash technique is parametrized by several values, including shingle length, signature vector size and number of signatures calculated, these values can also be considered as inputs for the MapReduce algorithm.
+Because the minhash technique is parametrized by several variables, including shingle length, signature size, and number of signatures to be calculated per document, these values can also be considered as inputs for the MapReduce algorithm.
 
@@
 
-\subsubsection{Optimization1}
+\subsubsection{Optimization-1}
 

### 2013-05-08 article/sigproc-sp.tex
Updated psedocode for algorithm

--- 2013-05-08 article/sigproc-sp.tex
@@
 \usepackage{url}
+\usepackage{algpseudocode}
 
@@
 
-In this section, we introduce the algorithm that utilizes the locality sensitive hashing.
-
 In order to measure document similarity we use a common LSH technique known as minhashing \cite{}.
@@
 \begin{table}
-MapReduce pseudocode:
-\begin{verbatim}
-initialize(){
- # configure and set up algorithm parameters
- # F = hash family;
- # L = shingle length;
- # K = vector length;
- # N = number of signatures to emit;
-}
+Minhash MapReduce pseudocode:
+\begin{algorithmic}
+\Function{initialize}{}
+%\Comment{configure and set up algorithm parameters}
+ \State $F \gets $ hash family;
+ \State $L \gets $ shingle length;
+ \State $K \gets $ vector length;
+ \State $N \gets $ number of signatures to emit;
+\EndFunction
 
-map(docid d, wikipage p){
-  int sentence ct = 0;
-  while s = nextSentence(p){
-    shingles = shingleSet(s,L);
-    minhashes = new List(|F|);
-    for i = 1 ... |F|:
-      minhashes[i] = Infinity;
-    for g in shingles:
-      for i = 1 ... |F|:
-        minhashes[i] = min(F_i(g),minhashes[i]);
-    for i = 1 ... N:
-      sig = select(K, minhahses);
-      emit(sig,(docid,sentencect));
-    sentencect++;
-  }
-}
-\end{verbatim}
+\Function{map}{docid $d$, wikipage $p$}
+ \State sentencect $\gets 0$
+ %\Comment {Break up article text into sentence}
+ \While{$s \gets$ nextSentence($p$)}
+  %\Comment{Break up sentence into shingles}
+  \State shingles $\gets$ shingleSet($s$,$L$);
+  \State minhashes = new List(|F|);
+   \For{$i \gets 1 \ldots |F|$}
+    \State minhashes[$i$] $\gets \infty$;
+   \EndFor
+   %\Comment{Calculate set of minhash signature for each sentence}
+   \For{$g \in$ shingles}
+    \For{$i \gets 1 \ldots |F|$}
+     \State minhashes[$i$] $\gets$ min($F_i(g)$,minhashes[$i$]);
+    \EndFor
+   \EndFor
+   %\Comment{Emit $N$ $K$-length signatures}
+  \For{$i \gets 1 \ldots N$}
+   \State sig = select($K$, minhahses);
+   \State emit(sig,(docid,sentencect));
+  \EndFor
+  \State  sentencect++;
+ \EndWhile
+\EndFunction
+\end{algorithmic}
 
-\begin{verbatim}
-reduce(signature sig, sentenceids [(d1,s1),(d2,s2) ...]){
-  if [[(d1,s1),(d2,s2) ... ]| > 1:
-    emit(sig, [(d1,s1), (d2,s2), ...]);
-}
-\end{verbatim}
+\begin{algorithmic}
+\Function{reduce}{signature sig, sentenceids $S$}
+\If{$|S| > 1$}
+\State    emit(sig, $S$);
+\EndIf
+\EndFunction
+\end{algorithmic}
 \end{table}

### 2013-05-08 article/sigproc-sp.tex

--- 2013-05-08 article/sigproc-sp.tex
@@
 \usepackage{url}
+\usepackage{algpseudocode}
 \usepackage{verbatim}
@@
 
-In this section, we introduce the algorithm that utilizes locality sensitive hashing.
+%In order to measure document similarity we use a common LSH technique known as minhashing \cite{}.
+A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
+In our case input documents are sentences.
+Each sentence is broken up into n-gram ``shingles''.
+For each shingle set $S$ we calculate $\{min_{s \in S}(F_i(s)\}$, the set of minimum hashes over the hash family.
+The signature on a document d is a vector of $K$ minhashes from the set of minimum hashes.
+In order to minimize false negatives we apply the technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.
 

### 2013-05-08 article/sigproc-sp.tex
updated

@@
 \alignauthor Samet Ayhan\\
-       \affaddr{University of Maryland, Department of Computer Science}\\
+       \affaddr{University of Maryland, Dept. of Computer Science}\\
        \affaddr{College Park, Maryland 20740}\\
@@
 \alignauthor Joshua Bradley\\
-       \affaddr{University of Maryland, Department of Computer Science}\\
+       \affaddr{University of Maryland, Dept. of Computer Science}\\
        \affaddr{College Park, Maryland 20740}\\
@@
 The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes.
-In order to minimize false negatives we apply a technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.
+In order to minimize false negatives we apply a technique sometimes known as ``banding'' \cite{ullman:massive} where multiple signatures are produced for each input document.
 
@@
 The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
-
-\section{Working Application}
-We explain the working application here...
-
-\begin{figure}
-\centering
-\epsfig{file=figure1.eps,height=1in,width=2.2in}
-\caption{Workflow within MapReduce Framework.}
-\end{figure}
 
@@
 \section{Experiments and Discussion}
-In this section, we discuss some of the issues we encountered regarding data representation, and archived data loading. We also present the performance optimizations we realized.
-
-\subsection{Optimization}
-
-We explain optimizations here...
-
-\subsubsection{Optimization-1}
-
-An optimization we realized...
-
-\subsubsection{Optimization-2}
-Another optimization we realized...
-
-\begin{figure*}
-\centering
-\epsfig{file=figure2.eps,height=1.5in,width=7in}
-\caption{Some figure.}
-\end{figure*}
-
-Illustrated in Figure 2, explain the figure here...
+In this section, we discuss ...
 

### 2013-05-08 src/main/analysis/HistogramClusters.java
Initial commit of histogram clusters

@@ -1,0 +1,102 @@
+package analysis;
+
+
+
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.TreeMap;
+import java.util.TreeSet;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+public class HistogramClusters {
+
+    public static void main(String args[]){
+		
+	    if(args.length != 1){
+	        System.out.println("Usage: FilterClusters <cluster output file>n");
+			System.exit(-1);
+	    }
+		Pattern linepat = Pattern.compile("([0-9]+)\t(.*)\t(.*)$");
+		    
+		FileInputStream fin;
+		
+		TreeMap<Integer,Integer> histogram = new TreeMap<Integer,Integer>();
+		HashSet<String> articleset = new HashSet<String>();
+		ArrayList<String> cluster = new ArrayList<String>();
+        int clusterct = 0;
+		try {
+
+            File filedir = new File(args[0]);
+            String line;
+
+            for(File file : filedir.listFiles()){
+                System.out.println("Reading files " + file.getName() + "...");
+                fin = new FileInputStream(file);
+                BufferedReader bin = new BufferedReader(new InputStreamReader(fin));
+                
+                String clustcurr = null;
+                while((line = bin.readLine()) != null){
+	                Matcher m = linepat.matcher(line);
+	                String clust = "";
+	                String title = "";
+	                String sentence = "";
+	                if(m.matches()){
+	                    clust = m.group(1);
+	                    title = m.group(2);
+	                    sentence = m.group(3);
+
+                    }else{
+                        System.out.println("Bad line: " + line);
+                        System.exit(-1);
+                    }
+
+					if(clustcurr == null){
+	                      clustcurr = clust;  
+	                }
+					
+	                if(!clustcurr.equals(clust)){
+	                    if(clusterct % 1000 == 0) System.out.println("clusterct = " + clusterct);
+
+	                    int size = cluster.size();
+	                    if(!histogram.containsKey(size)){
+	                        histogram.put(size, 0);    
+	                    }
+	                    histogram.put(size, histogram.get(size) + 1);
+	                    cluster.clear();
+                        clusterct++;
+	                }
+	                
[…]

### 2013-05-08 src/main/analysis/HistogramClusters.java
updated histogram clusters

@@ -38,7 +38,7 @@ public class HistogramClusters {
             String line;
 
             for(File file : filedir.listFiles()){
-                System.out.println("Reading files " + file.getName() + "...");
+                System.err.println("Reading file " + file.getName() + "...");
                 fin = new FileInputStream(file);
                 BufferedReader bin = new BufferedReader(new InputStreamReader(fin));
                 
@@ -54,7 +54,7 @@ public class HistogramClusters {
 	                    sentence = m.group(3);
 
                     }else{
-                        System.out.println("Bad line: " + line);
+                        System.err.println("Bad line: " + line);
                         System.exit(-1);
                     }
 
@@ -63,13 +63,20 @@ public class HistogramClusters {
 	                }
 					
 	                if(!clustcurr.equals(clust)){
-	                    if(clusterct % 1000 == 0) System.out.println("clusterct = " + clusterct);
+	                    if(clusterct % 10000 == 0) System.err.println("clusterct = " + clusterct);
 
 	                    int size = cluster.size();
 	                    if(!histogram.containsKey(size)){
 	                        histogram.put(size, 0);    
 	                    }
 	                    histogram.put(size, histogram.get(size) + 1);
+	                    if(cluster.size() > 100){
+                            System.err.println("Big cluster:");
+	                        for(String l : cluster){
+	                            System.out.println("\t" + l);
+	                        }
+	                    }
+	                    
 	                    cluster.clear();
                         clusterct++;
 	                }
@@ -93,7 +100,7 @@ public class HistogramClusters {
 		    
             System.out.println("N clusters: " + clusterct);            
             for(int b : histogram.keySet()){
-                System.out.println(b + "\t" + histogram.get(b));
+                System.err.println(b + "\t" + histogram.get(b));
             }
 
 	}

### 2013-05-08 src/main/analysis/HistogramClusters.java
updated histogram clustering code with a few other counts

@@ -30,8 +30,10 @@ public class HistogramClusters {
 		
 		TreeMap<Integer,Integer> histogram = new TreeMap<Integer,Integer>();
 		HashSet<String> articleset = new HashSet<String>();
+		HashSet<String> sentenceset = new HashSet<String>();
 		ArrayList<String> cluster = new ArrayList<String>();
         int clusterct = 0;
+        int sentencect = 0;
 		try {
 
             File filedir = new File(args[0]);
@@ -44,6 +46,7 @@ public class HistogramClusters {
                 
                 String clustcurr = null;
                 while((line = bin.readLine()) != null){
+                    sentencect++;
 	                Matcher m = linepat.matcher(line);
 	                String clust = "";
 	                String title = "";
@@ -70,12 +73,16 @@ public class HistogramClusters {
 	                        histogram.put(size, 0);    
 	                    }
 	                    histogram.put(size, histogram.get(size) + 1);
-	                    if(cluster.size() > 100){
-                            System.err.println("Big cluster:");
-	                        for(String l : cluster){
-	                            System.out.println("\t" + l);
+	                    /*
+	                    if(cluster.size() > 10000){
+                            int ct = 0;
+                            for(String l : cluster){
+	                            if(ct > 20) break;
+                                System.out.println(l);
+	                            ct++;
 	                        }
 	                    }
+	                    */
 	                    
 	                    cluster.clear();
                         clusterct++;
@@ -84,7 +91,7 @@ public class HistogramClusters {
 	                clustcurr = clust;
                     cluster.add(line);
                     articleset.add(title);
-
+                    sentenceset.add(sentence);
 	            }
 	              bin.close();
 	              fin.close();
@@ -98,7 +105,10 @@ public class HistogramClusters {
 		     }
 		    
 		    
-            System.out.println("N clusters: " + clusterct);            
+		System.out.println("N clusters: " + clusterct);            
+		System.out.println("N unique articles: " + articleset.size());
+		System.out.println("N sentences: " + sentencect);
+		System.out.println("N unique sentences: " + sentenceset.size());
             for(int b : histogram.keySet()){
                 System.err.println(b + "\t" + histogram.get(b));
             }

### 2013-05-08 src/main/analysis/HistogramClusters.java
fixed output

@@ -110,7 +110,7 @@ public class HistogramClusters {
 		System.out.println("N sentences: " + sentencect);
 		System.out.println("N unique sentences: " + sentenceset.size());
             for(int b : histogram.keySet()){
-                System.err.println(b + "\t" + histogram.get(b));
+                System.out.println(b + "\t" + histogram.get(b));
             }
 
 	}

### 2013-05-08 src/main/analysis/HistogramClusters.java
Fixed usage statement

@@ -9,10 +9,8 @@ import java.io.FileNotFoundException;
 import java.io.IOException;
 import java.io.InputStreamReader;
 import java.util.ArrayList;
-import java.util.HashMap;
 import java.util.HashSet;
 import java.util.TreeMap;
-import java.util.TreeSet;
 import java.util.regex.Matcher;
 import java.util.regex.Pattern;
 
@@ -21,7 +19,7 @@ public class HistogramClusters {
     public static void main(String args[]){
 		
 	    if(args.length != 1){
-	        System.out.println("Usage: FilterClusters <cluster output file>n");
+	        System.out.println("Usage: HistogramClusters <cluster output file>n");
 			System.exit(-1);
 	    }
 		Pattern linepat = Pattern.compile("([0-9]+)\t(.*)\t(.*)$");

### 2013-05-08 src/main/analysis/HistogramClusters.java
Updated output text to be more accurate.

@@ -102,10 +102,9 @@ public class HistogramClusters {
 		 			e.printStackTrace();
 		     }
 		    
-		    
+        System.out.println("N lines: " + sentencect);
 		System.out.println("N clusters: " + clusterct);            
 		System.out.println("N unique articles: " + articleset.size());
-		System.out.println("N sentences: " + sentencect);
 		System.out.println("N unique sentences: " + sentenceset.size());
             for(int b : histogram.keySet()){
                 System.out.println(b + "\t" + histogram.get(b));

### 2013-05-08 src/main/analysis/HistogramClusters.java
Added unique title/sentence histograms

@@ -27,9 +27,13 @@ public class HistogramClusters {
 		FileInputStream fin;
 		
 		TreeMap<Integer,Integer> histogram = new TreeMap<Integer,Integer>();
+		TreeMap<Integer,Integer> titlehistogram = new TreeMap<Integer,Integer>();
+		TreeMap<Integer,Integer> sentencehistogram = new TreeMap<Integer,Integer>();
 		HashSet<String> articleset = new HashSet<String>();
 		HashSet<String> sentenceset = new HashSet<String>();
 		ArrayList<String> cluster = new ArrayList<String>();
+		HashSet<String> clustertitles = new HashSet<String>();
+		HashSet<String> clustersentences = new HashSet<String>();
         int clusterct = 0;
         int sentencect = 0;
 		try {
@@ -67,27 +71,50 @@ public class HistogramClusters {
 	                    if(clusterct % 10000 == 0) System.err.println("clusterct = " + clusterct);
 
 	                    int size = cluster.size();
-	                    if(!histogram.containsKey(size)){
-	                        histogram.put(size, 0);    
-	                    }
-	                    histogram.put(size, histogram.get(size) + 1);
-	                    /*
+                        if(!histogram.containsKey(size)){
+                            histogram.put(size, 0);    
+                        }
+                        histogram.put(size, histogram.get(size) + 1);
+	                    
+                        size = clustertitles.size();
+                        if(!titlehistogram.containsKey(size)){
+                            titlehistogram.put(size, 0);    
+                        }
+                        titlehistogram.put(size, titlehistogram.get(size) + 1);
+                        
+                        size = clustersentences.size();
+                        if(!sentencehistogram.containsKey(size)){
+                            sentencehistogram.put(size, 0);    
+                        }
+                        sentencehistogram.put(size, sentencehistogram.get(size) + 1);
+	                    
+                        /*
 	                    if(cluster.size() > 10000){
                             int ct = 0;
+                            System.out.println("Cluster size: " + cluster.size());
+                            System.out.println("N unique sentences " +  clustersentences.size());
+                            System.out.println("N unique titles " +  clustertitles.size());
+
                             for(String l : cluster){
-	                            if(ct > 20) break;
+	                            if(ct > 10) break;
                                 System.out.println(l);
 	                            ct++;
 	                        }
+                            System.out.println();
 	                    }
 	                    */
 	                    
 	                    cluster.clear();
[…]

### 2013-05-08 src/main/analysis/HistogramClusters.java
Fixed an error that was missing a few clusters.

@@ -26,15 +26,25 @@ public class HistogramClusters {
 		    
 		FileInputStream fin;
 		
+		// Overall histogram: cluster sizes -> cluster cts
 		TreeMap<Integer,Integer> histogram = new TreeMap<Integer,Integer>();
+		
+		// Unique title histogram: # unique titles in cluster -> cluster cts
 		TreeMap<Integer,Integer> titlehistogram = new TreeMap<Integer,Integer>();
+		
+		// Unique sentence histogra: # unique sentences in cluster -> cluster cts
 		TreeMap<Integer,Integer> sentencehistogram = new TreeMap<Integer,Integer>();
-		HashSet<String> articleset = new HashSet<String>();
+		
+		// Sets to keep track of overall unique title and sentences
+		HashSet<String> titleset = new HashSet<String>();
 		HashSet<String> sentenceset = new HashSet<String>();
+		
+		// Per cluster data structures
 		ArrayList<String> cluster = new ArrayList<String>();
 		HashSet<String> clustertitles = new HashSet<String>();
 		HashSet<String> clustersentences = new HashSet<String>();
-        int clusterct = 0;
+       
+		int clusterct = 0;
         int sentencect = 0;
 		try {
 
@@ -42,6 +52,7 @@ public class HistogramClusters {
             String line;
 
             for(File file : filedir.listFiles()){
+                if(file.getName().startsWith("_")) continue;
                 System.err.println("Reading file " + file.getName() + "...");
                 fin = new FileInputStream(file);
                 BufferedReader bin = new BufferedReader(new InputStreamReader(fin));
@@ -70,6 +81,7 @@ public class HistogramClusters {
 	                if(!clustcurr.equals(clust)){
 	                    if(clusterct % 10000 == 0) System.err.println("clusterct = " + clusterct);
 
+	                    // Once we've found a new cluster Update each histogram
 	                    int size = cluster.size();
                         if(!histogram.containsKey(size)){
                             histogram.put(size, 0);    
@@ -89,6 +101,7 @@ public class HistogramClusters {
                         sentencehistogram.put(size, sentencehistogram.get(size) + 1);
 	                    
                         /*
+                         // Code for examining cluster contents
 	                    if(cluster.size() > 10000){
                             int ct = 0;
                             System.out.println("Cluster size: " + cluster.size());
@@ -104,9 +117,11 @@ public class HistogramClusters {
 	                    }
 	                    */
 	                    
-	                    cluster.clear();
-	                    clustersentences.clear();
[…]

### 2013-05-08 article/sigproc-sp.tex
Updated experiment and discussion section.

@@
 \usepackage{microtype}
-
-\def\sharedaffiliation{%
-\end{tabular}
-\begin{tabular}{c}}
+\usepackage{enumerate}
+\usepackage{enumitem}
+\usepackage{epsfig}
+\usepackage{algorithmicx}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 
-\numberofauthors{3} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
+\numberofauthors{3}
+
 \author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
 \alignauthor Samet Ayhan\\
@@
        \email{sayhan@cs.umd.edu}
-% 2nd. author
 \alignauthor Joshua Bradley\\
@@
        \email{jgbrad1@cs.umd.edu}
-% 3rd. author
 \alignauthor Sarah Weissman\\
@@
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
 
 \date{19 April 2013}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
 
@@
 
-Lin described three MapReduce algorithms for computing pairwise similarity on document collections: 1.Based on brute force, 2.Treated as large-scale ad hoc retrieval, 3.Based on Cartesian product of postings lists \cite{lin:brute}.
+Lin described three MapReduce algorithms for computing pairwise similarity on document collections \cite{lin:brute}.
+\begin{enumerate}[noitemsep,nolistsep]
+\item Based on brute force.
+\item Treated as large-scale ad hoc retrieval.
+\item Based on Cartesian product of postings lists.
+\end{enumerate}
 
@@
 \subsection{Design}
-Since signature techniques such as LSH are embarrassingly parallel, we designed our algorithm around the MapReduce framework.
+Many signature techniques such as LSH are embarrassingly parallel. In our project, we designed our algorithm around the MapReduce framework.
 
@@
 \begin{table}
-Minhash MapReduce pseudocode:
+\begin{algorithm}[H]
+\caption{Minhash MapReduce Pseudocode}
 \begin{algorithmic}
@@
 \EndFunction
-\end{algorithmic}
 
-\begin{algorithmic}
 \Function{reduce}{signature sig, sentenceids $S$}
@@
 \end{algorithmic}
+\end{algorithm}
 \end{table}
@@
 \centering
-\epsfig{file=jac-ed-chart.eps,height=4in,width=6in}
+\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
 \caption{Jaccard Similarity vs. normalized edit distance.}
@@
 \section{Experiments and Discussion}
-In this section, we discuss ...
+For this project, we performed several analyses to provide more insight into the occurence of duplicate sentences.
+In particular, we were interested in detecting the occurrence of templatification which is a precursor to the problem of finding factual drift between articles.
+\emph{Templatification} occurs when one sentence is an exact duplicate of another sentence, but the main topic has been changed by only a few pieces of key information having been modified.
+For example, it could be said that the following two sentences follow a particular \emph{template}.
+\begin{itemize}[noitemsep,nolistsep]
+\item Bush had an approval rating of 22\% by the end of his term in 2008.
+\item Obama had an approval rating of 56\% by the end of his term in 2012.
+\end{itemize}
+From the perspective of editing/writing Wikipedia articles, this is a strong indicator that the author copied the original sentence and modified the relevant information to pertain to a different topic.
+What remains shared between both sentences though is the inherent structure.
+
+\emph{Factual drift} most notably occurs when the same sentence has been copied and only one piece of factual information about the \emph{same} topic has changed.
+For example, factual drift can be seen in the following two sentences.
+\begin{itemize}[noitemsep,nolistsep]
+\item Obama had an approval rating of 56\% by the end of his term in 2012.
+\item Obama had an approval rating of 46\% by the end of his term in 2012.
+\end{itemize}
+
+\begin{center}
+\includegraphics[scale=0.43, keepaspectratio = true]{Top10ArticlePairs.jpg}
+\end{center}
+
+Based on our preliminary analysis, templatification and factual drift tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics.
+For example, of the top 10 pairs of articles with the highest similarity count, one article pair was the articles titled ''List of birds of Zambia'' and ''List of birds of Tanzania''.
+With both countries sharing the same geographic region, it is not unexpected that their respective wikipedia articles on the countrys' bird species would be highly comparable.
+For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature.
+Overall, we found $\approx 6500$ wikipedia article pairs that had a similarity count greater than $50$.
+
+After performing minhash on all of Wikipedia, we were able to cluster all unique sentences.
+Looking at the distribution of cluster sizes in FIGURE SARAH'S HISTOGRAM, we can see the expected behavior of monotonically decreasing number of clusters of size $k$ as $k$ grows large.
+What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$.
+Based on the fact that we found $\approx 6500$ article pairs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common.
+As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in TOP 10 SIMILARITY COUNTS FIGURE).
 
@@
 This paper presents our work on near-duplicate detection of Wikipedia articles at various granularity levels using LSH technique.
-Our novel MapReduce algorithm tackles the problem by transforming it into more manageable pieces where each piece handled in parallel.
-Our unique contribution includes empirical analysis of signatures belonging to Wikipedia articles at k-gram level.
+Our novel MapReduce algorithm tackles the problem by transforming it into more manageable pieces where each piece is handled in parallel.
+Our unique contribution includes empirical analysis of signatures belonging to Wikipedia articles at the sentence level.
 Experimental results verify that the proposed method is able to effectively and efficiently detect similar articles.
@@
 
-%APPENDICES are optional
-%\balancecolumns
 \balancecolumns
-% That's all folks!
 \end{document}

### 2013-05-08 src/main/analysis/HistogramClusters.java
Added some statements to print out mathematica graphing commands.

@@ -174,21 +174,55 @@ public class HistogramClusters {
 		System.out.println("N clusters: " + clusterct);            
 		System.out.println("N unique titles: " + titleset.size());
 		System.out.println("N unique sentences: " + sentenceset.size());
-        
-		System.out.println("Cluster histogram");
+
+        StringBuffer histvals = new StringBuffer();
+        StringBuffer histkeys = new StringBuffer();
+		
+        System.out.println("Cluster histogram");
         for(int b : histogram.keySet()){
+            histkeys.append(",");
+            histkeys.append("\"");
+            histkeys.append(b);
+            histkeys.append("\"");
+            histvals.append(",");
+            histvals.append(histogram.get(b));
             System.out.println(b + "\t" + histogram.get(b));
+
         }
+        //Mathematic output:
+        System.out.println("BarChart[{"+histvals.substring(1)+"}, ChartLabels ->Placed[{"+histkeys.substring(1)+"},Top]]");
+        histkeys.setLength(0);
+        histvals.setLength(0);
         
         System.out.println("Unique Title histogram");
         for(int b : titlehistogram.keySet()){
+            histkeys.append(",");
+            histkeys.append("\"");
+            histkeys.append(b);
+            histkeys.append("\"");
+            histvals.append(",");
+            histvals.append(titlehistogram.get(b));
             System.out.println(b + "\t" + titlehistogram.get(b));
         }
+        //Mathematica output
+        System.out.println("BarChart[{"+histvals.substring(1)+"}, ChartLabels ->Placed[{"+histkeys.substring(1)+"},Top]]");
+        histkeys.setLength(0);
+        histvals.setLength(0);
         
         System.out.println("Uniqe Sentence histogram");
         for(int b : sentencehistogram.keySet()){
+            histkeys.append(",");
+            histkeys.append("\"");
+            histkeys.append(b);
+            histkeys.append("\"");
+            histvals.append(",");
+            histvals.append(sentencehistogram.get(b));
             System.out.println(b + "\t" + sentencehistogram.get(b));
         }
+        //Mathematica output
+        System.out.println("BarChart[{"+histvals.substring(1)+"}, ChartLabels ->Placed[{"+histkeys.substring(1)+"},Top]]");
+        histkeys.setLength(0);
+        histvals.setLength(0);
 
 	}
 

### 2013-05-08 article/sigproc-sp.tex
Added back working application section
Updated graphics formats for images not showing. Scaled up fonts in images and resized some images to make them fit better into the article. Added cluster histogram

@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
+\includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
+%\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
 \caption{Jaccard Similarity vs. normalized edit distance.}
 \label{jac-ed}
-\end{figure*}
+\end{figure}
 
 As we would expect, Jaccard similarity decreases as edit distance increases, but it also decreases as shingle length increases.
-Figure \ref{fig:jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$.
+Figure \ref{jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$.
 At $l = .05$ and $e = .2$ our estimate for Jaccard similarity has already fallen to the range [0.58,0.65].
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\epsfig{file=edgrid.eps,width=7in}
+\epsfig{file=edgrid.eps,width=3.5in}
 \caption{}
 \label{ed-grid}
-\end{figure*}
+\end{figure}
+
+\section{Working Application}
+\begin{itemize}
+\item MinhashWikipediaPages
+\item DedupSentences
+\item MergeClusters
+\item GetSentenceClusters
+\item Edit Distance Filter
+\end{itemize}
+
+\subsection{Limitations of Approach}
 
@@
 
+\begin{figure}
 \begin{center}
@@
 \end{center}
+\caption{Top 10 Similarity Counts}
+\label{toparticles}
+\end{figure}
 
@@
 After performing minhash on all of Wikipedia, we were able to cluster all unique sentences.
-Looking at the distribution of cluster sizes in FIGURE SARAH'S HISTOGRAM, we can see the expected behavior of monotonically decreasing number of clusters of size $k$ as $k$ grows large.
+Looking at the distribution of cluster sizes in FIGURE SARAH'S HISTOGRAM \ref{clust}, we can see the expected behavior of monotonically decreasing number of clusters of size $k$ as $k$ grows large.
 What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$.
 Based on the fact that we found $\approx 6500$ article pairs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common.
-As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in TOP 10 SIMILARITY COUNTS FIGURE).
+As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in Figure \ref{toparticles}).
+
+\begin{figure}
+\centering
+\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
+\caption{Histogram of Cluster Sizes (log scale).}
+\label{clust}
+\end{figure}
 

### 2013-05-08 article/sigproc-sp.tex
Removed unused graphics file.
Added some summarizing statistics about the cluster output.

@@
 \includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
-%\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
 \caption{Jaccard Similarity vs. normalized edit distance.}
@@
 \section{Experiments and Discussion}
+
+To test our application we ran the first four steps (up to but not including the final edit distance filtering pass) on a dump of current English-language Wikipedia articles (as of 5/2013) obtained from dumps.wikimedia.org.
+The dump is approximately 40G in size and contains 4,113,785 articles (after excluding certain non-article page types).
+After minhashing and deduplification, we found a total of 9,465,881 similar sentence pairs.
+After clustering these pairs, the total number of similar sentence clusters was 415,936, including 1,792,748 unique article/sentence pairs over 759,297 article titles.
+The total number of unique sentences over all cluster was 1,305,359.
+
+Cluster sizes ranged from 2 to 28,008.
+(See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, but the distribution of cluster exhibits a long tail.
+As a result, while 99\% of our clusters have size below or equal to 30, about 1/3 of the output sentence/article pairs fall into clusters with size greater than 30.
+One explanation for this distribution of sentences is the phenomenon we call ''tempatification,'' which we describe more in detail below.)
+
+\subsection{Similar Sentence Types}
+
+Sentence Clusters (without an Edit Distance Filter).
+
+\begin{itemize}
+\item Factual Drift
+\item Templatification
+\item References
+\item Copy Editing
+\end{itemize}
+
 For this project, we performed several analyses to provide more insight into the occurence of duplicate sentences.
@@
 \includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
-\caption{Histogram of Cluster Sizes (log scale).}
+\caption{Histogram of Cluster Sizes (for cluster size $< 300$, log scale).}
 \label{clust}

### 2013-05-08 article/sigproc-sp.tex
Expanded experiments and discussion section with overall cluster stats and full breakdown of sentence types. still some placeholders need to be filled.

--- 2013-05-08 article/sigproc-sp.tex
@@
 \begin{itemize}
+\item Repack Wikipedia Pages as Sequence Files using Cloud9 library utility
 \item MinhashWikipediaPages
@@
 
+DOCUMENT LIMITATIONS HERE
+
 \section{Experiments and Discussion}
-For this project, we performed several analyses to provide more insight into the occurence of duplicate sentences.
-In particular, we were interested in detecting the occurrence of templatification which is a precursor to the problem of finding factual drift between articles.
+
+We performed several analyses to provide more insight into the occurence of duplicate sentences.
+In particular, we were interested in detecting similar sentences that arose from copying text from one article to another since such instances would represent content that is either redundant, or content that has diverged in the sense that either the original or the copy was edited for clarification of factual correctness and the other was not.
+Such instances give insight into the Wikipedia editing process, and also represent an opportunity to improve article quality on Wikipedia by identifying places where further editing or article merging may be needed.
+
+All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 4/2013) obtained from dumps.wikimedia.org.
+The enwiki dump is approximately 40G in size and contains 4,113,785 articles (after excluding certain non-article page types).
+Running the first four steps of our application (up to but not including the final edit distance filtering pass) against the enwiki dump on a shared cluster of 16 nodes with (15 GB RAM and 4 cores each) took XXXX (HOW MUCH TIME DID THIS TAKE, SAMET?) minutes.
+
+After minhashing and deduplification, we found a total of 9,465,881 similar article/sentence pairs.
+After clustering these pairs, the total number of similar sentence clusters was 415,936, including 1,792,748 unique article/sentence pairs over 759,297 article titles.
+The total number of unique sentences over all cluster was 1,305,359.
+
+Cluster sizes ranged from 2 to 28,008.
+(See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, but the distribution of cluster sizes exhibits a long tail.
+As a result, while 99\% of our clusters have size below or equal to 30, about 1/3 of the output sentence/article pairs fall into clusters with size greater than 30.
+One explanation for this distribution of sentences is the phenomenon we call ''templatification,'' which we describe in more detail below.)
+
+\begin{figure}
+\centering
+\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
+\caption{Histogram of Cluster Sizes (for cluster size $< 300$, log scale).}
+\label{clust}
+\end{figure}
+
+\subsection{Similar Sentence Types}
+
+Manual inspection of cluster output reveals several different similar sentence types. These types can be summarized as follows:
+
+\begin{itemize}
+\item Templatification
+\item References
+\item Direct Copying
+\item Direct Copying with Copy Editing
+\item Direct Copying with Factual Drift
+\end{itemize}
+
  \emph{Templatification} occurs when one sentence is an exact duplicate of another sentence, but the main topic has been changed by only a few pieces of key information having been modified.
@@
 
-\emph{Factual drift} most notably occurs when the same sentence has been copied and only one piece of factual information about the \emph{same} topic has changed.
+\emph{Direct Copying} occurs when the same sentence has been copied into another (or possibly the same) article.
+This can happen for many reasons, including articles that deal with similar subjects, or articles that are subtopics of other topics.
+(SOME EXAMPLES?).
+Similarly, \emph{Direct Copying with Copy Editing} occurs when the same sentence has been copied into another article and then one or both sentences has been edited for style or clarity.
+For example:
+
+\begin{itemize}[noitemsep,nolistsep]
+\item EXAMPLE HERE.
+\item EXAMPLE HERE.
+\end{itemize}
+
+\emph{Factual drift} most notably occurs when the same sentence has been copied and a piece of factual information about the \emph{same} topic has changed.
 For example, factual drift can be seen in the following two sentences.
@@
 \end{itemize}
+Although factual drift is similar to copy editing and may occur along with copy editing, we distinguish the two cases since factual errors are more severe than style issues.
+
+\emph{References} refers to citations, typically occurring at the end of a Wikipedia article.
+Since Wikipedia does not adhere to one single citation style, the same work may be referenced on multiple pages in different styles.
+Similarly different portions of the same work may be referenced in different articles.
+Although citation errors might be harder to distinguish from factual errors, errors in citation are arguably no less important.
+(It would also be interesting to compare whether articles that share similar sentences also share similar citations.)
+
+\begin{itemize}[noitemsep,nolistsep]
+\item EXAMPLE HERE.
+\item EXAMPLE HERE.
+\end{itemize}
+
+\subsubsection{Break down of sentence types}
+
+By manually counting a small sample of NNNN output clusters, we came up with the following breakdown of sentence types:
+
+INSERT CLASSIFY CLUSTER BREAKDOWN HERE
+
+\subsection{Sentence Similarity as a Measure of Article Similarity}
 
@@
 
-Based on our preliminary analysis, templatification and factual drift tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics.
+Based on our preliminary analysis, templatification tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics.
 For example, of the top 10 pairs of articles with the highest similarity count, one article pair was the articles titled ''List of birds of Zambia'' and ''List of birds of Tanzania''.
@@
 For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature.
+Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences.
 Overall, we found $\approx 6500$ wikipedia article pairs that had a similarity count greater than $50$.
 
-After performing minhash on all of Wikipedia, we were able to cluster all unique sentences.
-Looking at the distribution of cluster sizes in FIGURE SARAH'S HISTOGRAM \ref{clust}, we can see the expected behavior of monotonically decreasing number of clusters of size $k$ as $k$ grows large.
+Looking at the distribution of cluster sizes in Figure \ref{clust}, we can see the expected behavior of decreasing number of clusters of size $k$ as $k$ grows large.
 What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
-\caption{Histogram of Cluster Sizes (log scale).}
-\label{clust}
-\end{figure}
+JOSH, CAN YOU LOOK UP WHAT THE ACTUAL ARTICLES ARE? THAT MIGHT BE INTERESTING.
 

### 2013-05-08 article/sigproc-sp.tex
Added description of false positives analysis. Working on application and Limitation sections.

@@
 
+In order to estimate the affect of shingle length on false positive rate we ran a number of experiments for a 1 G collection of wikipedia documents.
+For fixed $N=10$ we ran experiments for three values of $K=\{8,9,10\}$ and $5 \le L \le 15$.
+Setting a normalized edit distance threshold of $e = .25$, we calculated the total number of ''good'' ($e <= .25$) and ''bad'' ($e > .25$) (unique) sentence pairs as well as the false positive rate (\# bad pairs divided by the total number of sentences).
+Results are presented in Figure \ref{ed-grid}.
+
+We can see from the graphs in Figure \ref{ed-grid} that all three statistics hit a low at shingle length 12 or 13.
+This means that in order to achieve the lowest false positive rate we should use parameter settings around $N=10, K=10$ and $L=12$ or $L=13$.
+However the number of \emph{good} pairs also hits a minimum at $L = 12$, which means that while overall the output is more precise, we are also missing output pairs.
+
+Another feature of the graphs in Figure \ref{ed-grid} that stands out is that while the false positive rate and total number of bad pairs bottoms out at around $L=12$, for $L > 12$ the output quality actually decreases.
+This is counter to our intuition that output quality increases as the length of the shingle increases.
+One would expect larger shingles to correspond to closer edit distance scores, since larger shingles correspond to longer consecutive sequences of identical text.
+One explanation for these counter-intuitive results could be limitations of the underlying hash family.
+If longer shingle lengths lead to greater hash collisions this could explain the increased numbers of bad pairs.
+Improving the hash function to reduce collisions could improve results.
+
+Since minimizing the false positive rate also means minimizing reducing good pairs, another option is to let parameters to maximize good output and use edit distance as a secondary filter.
+With this approach our experimental results suggest that the best parameter combination would be $N=10, K=8, L=10$.
+
 \begin{figure}
@@
 \epsfig{file=edgrid.eps,width=3.5in}
-\caption{}
+\caption{False Positive Rate, Good Count, Bad Count for $N=10, K \in \{8,9,10\}, 5 \le L \le 15$}
 \label{ed-grid}
@@
 \section{Working Application}
-\begin{itemize}
-\item Repack Wikipedia Pages as Sequence Files using Cloud9 library utility
-\item MinhashWikipediaPages
-\item DedupSentences
-\item MergeClusters
-\item GetSentenceClusters
-\item Edit Distance Filter
-\end{itemize}
+
+While the Minhash signature code provides the raw similarity scores, it is one part of a larger framework composed of several pieces, described below.
+The input to the process is an XML dump format.
+(See http://en.wikipedia.org/wiki/Wikipedia:Database\_download for details.) The output of the process is a list of sentence clusters containing the original article title and sentence text.
+Decomposing the sentence clustering into several pieces allows us to minimize the amount of raw wikipedia text that gets passed between mappers and reducers, thus improving scalability.
+
+The process can be summarized as follows:
+
+\begin{enumerate}
+\item Preprocess Wikipedia Pages - 
+\item Minhash Wikipedia Sentences -
+\item Dedup Sentence Buckets - 
+\item Computer Sentence Clusters - 
+\item Get Sentence Text - 
+\item Edit Distance Filter -
+\end{enumerate}
 
@@
 
-DOCUMENT LIMITATIONS HERE
+\begin{itemize}
+\item Aforementioned hash issues.
+\item Non-deterministic behavior
+\item Regular expression depth
+\item Dirty wikipedia data
+\item large clusters of relatively uninteresting results
+\end{itemize}
 

### 2013-05-08 article/sigproc-sp.tex
Improved application details and limitations section.

@@
 \usepackage{algorithm}
-\usepackage{algpseudocode}
 
@@
 
-Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 library for parsing Wikipedia page text from the Wikipedia XML dump format.
+Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 library (\url{https://github.com/lintool/Cloud9}) for parsing Wikipedia page text from the Wikipedia XML dump format.
 Sentences are parsed out over each document using a regular expression.
@@
 The input to the process is an XML dump format.
-(See http://en.wikipedia.org/wiki/Wikipedia:Database\_download for details.) The output of the process is a list of sentence clusters containing the original article title and sentence text.
-Decomposing the sentence clustering into several pieces allows us to minimize the amount of raw wikipedia text that gets passed between mappers and reducers, thus improving scalability.
+(See \url{http://en.wikipedia.org/wiki/Wikipedia:Database_download} for details.) The output of the process is a list of sentence clusters containing the original article title and sentence text.
+Decomposing the sentence clustering into several pieces allows us to minimize the amount of raw text that gets passed between mappers and reducers, thus improving scalability.
 
@@
 \begin{enumerate}
-\item Preprocess Wikipedia Pages - 
-\item Minhash Wikipedia Sentences -
-\item Dedup Sentence Buckets - 
-\item Computer Sentence Clusters - 
-\item Get Sentence Text - 
-\item Edit Distance Filter -
+\item \textbf{Preprocess Wikipedia Pages} - Using a utility from the Cloud9 library, preprocess the raw Wikipedia dump into a SequenceFile format.
+Working with SequenceFiles gives the option to use block or record compressed input compatible with the MapReduce framework.
+\item \textbf{Minhash Wikipedia Sentences} - Reads processed Wikipedia input, and uses a regular expression to match sentences in the article text.
+Outputs a file of signature ``buckets'' organized by signature.
+Each output sentence is represented by a (docid,sentenceid) pair.
+\item \textbf{Dedup Sentence Buckets} - Because multiple sentences may occur in each bucket, a second MapReduce job is used to map from buckets to raw sentence pairs, removing duplicates.
+\item \textbf{Compute Sentence Clusters} - Performs a local (i.e., non-MapReduce) connected component analysis on the dedup-ed pairs to form sentence clusters.
+\item \textbf{Get Sentence Text} - Maps clustered sentences (represented by (docid,sentenceid) pairs) back to sentence text by streaming over the Wikipedia input a second time and recovering the corresponding sentences by ID.
+\item \textbf{Edit Distance Filter} - \emph{(optional)} For each output cluster and filter all pairs within the cluster by desired edit distance threshold.
 \end{enumerate}
 
-\subsection{Limitations of Approach}
+\subsection{Limitations to Our Approach}
 
-\begin{itemize}
-\item Aforementioned hash issues.
-\item Non-deterministic behavior
-\item Regular expression depth
-\item Dirty wikipedia data
-\item large clusters of relatively uninteresting results
-\end{itemize}
+In addition to the aforementioned hash issue there are other limitations in our implementation and improvements that could be made.
+
+\emph{Data cleanliness} - The Cloud9 utilities that process Wikipedia code do some preprocessing of non-text elements from Wikipedia pages.
+However there is still improvements that could be made.
+Section headings can confuse our regular expression mapping, causing pieces of extraneous text to be appended to sentences.
+Parsing page text with a better understanding of how Wikipedia articles are structured could improve our input data.
+Additionally, keeping track of the order in which sentences occur on a page could improve analysis.
+For example, references and external links are typically found at the bottom of a Wikipeda page.
+More carefully filtering text based on sentence depth could improve results.
+
+\emph{Sentence matching} - Since Wikipedia data is not chunked by sentence, we rely on regular expression matching to break up input text into sentences.
+Since sentences have recursive structure, our regular expression can lead to stack overflow exceptions from the underlying recursive pattern match search.
+Setting bounds on the sentence structure nesting could provide more reliable results.
+The encyclopedic style of Wikipedia may lend itself to simpler sentence structures that don't require a general purpose sentence matching algorithm.
+
+\emph{Large clusters} - Since we rely on a connected component analysis to compute the final sentence clusters, our large clusters can be a bottleneck.
+Unfortunately, the Wikipedia data does contain large clusters of similar sentences (see the discussion of templatification below).
+Since our initial experimental results suggest that more interesting clusters (for example, sentence clusters representing copied data with factual errors) are much smaller (on the order of 2 or 3 sentences per cluster), we set a limit on maximum bucket size and only consider the first $n$ sentences in any bucket up to that limit.
+Setting a limit on cluster size helps ensure more predictable runtime and discards large portions of relatively uninteresting clusters, making output data more manageable.
+
+\emph{Non-determinism} - Our current implementation of Minhash suffers from a yet unidentified source of non-determinism.
+This affects the number of output records produced from the Minhashing stage of our implementation from one run to the next and has unknown effects on output quality.
 

### 2013-05-09 article/sigproc-sp.tex
Added a table of counts of different sentence types.

@@
 \item Obama had an approval rating of 56\% by the end of his term in 2012.
+
 \end{itemize}
@@
 For example:
-
 \begin{itemize}[noitemsep,nolistsep]
@@
 
-By manually counting a small sample of NNNN output clusters, we came up with the following breakdown of sentence types:
+By manually counting a small sample of 824 output clusters, we came up with the following breakdown of sentence types:
 
-INSERT CLASSIFY CLUSTER BREAKDOWN HERE
+\begin{tabular}{l l}
+NOT\_SIMILAR & 3 \\
+FACTUAL\_DRIFT & 65 \\
+TEMPLATE & 52 \\
+REFERENCE & 23 \\
+COPY\_EDIT & 214 \\
+OTHER & 12 \\
+IDENTICAL & 455 \\
+\end{tabular}
 

### 2013-05-09 article/sigproc-sp.tex
Added some clarifying text to the ed/jaccard analysis section.
Updates to the report

--- 2013-05-08 article/sigproc-sp.tex
@@
 \alignauthor Samet Ayhan\\
-       \affaddr{University of Maryland, Dept. of Computer Science}\\
-       \affaddr{College Park, Maryland 20740}\\
+       \affaddr{University of Maryland}\\
+       \affaddr{Dept. of Computer Science}
        \email{sayhan@cs.umd.edu}
 \alignauthor Joshua Bradley\\
-       \affaddr{University of Maryland, Dept. of Computer Science}\\
-       \affaddr{College Park, Maryland 20740}\\
+       \affaddr{University of Maryland}\\
+       \affaddr{Dept. of Computer Science}
        \email{jgbrad1@cs.umd.edu}
 \alignauthor Sarah Weissman\\
-       \affaddr{University of Maryland, College of Information Studies}\\
-       \affaddr{College Park, Maryland 20740}\\
+       \affaddr{University of Maryland}\\
+       \affaddr{College of Information Studies}\\
        \email{sew@umd.edu}
@@
 
-\date{19 April 2013}
+\date{9 May 2013}
 
@@
 In this paper, we describe a novel similarity detection algorithm that utilizes a locality sensitive hashing (LSH) technique on the MapReduce framework.
-The algorithm has been designed and implemented to detect similar articles using large Wikipedia dumps, in compressed or uncompressed forms.
+The algorithm has been designed and implemented to detect similar articles using large Wikipedia dumps.
 Experimental results appear to support that our method is able to efficiently and effectively detect similar articles across Wikipedia.
@@
 Furthermore, Wikipedia has a history of generating controversy over editorial quality and factual correctness.
-Although some studies have found Wikipedia’s accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.
+Although some studies have found Wikipedia's accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.
 Since Wikipedia may be edited anonymously, information is often freely copied between web sources and even between Wikipedia articles.
@@
 
-In order to come up with a novel algorithm that would allow us to detect near duplicate Wikipedia articles, we decided that we needed to answer the following questions, first:
-\begin{itemize}
-\item What is the most appropriate LSH technique to apply?
-Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
-Currently, no LSH family for edit distance is known to exist.
+In order to come up with a novel algorithm that would allow us to detect near-duplicate sentences within Wikipedia articles, we decided that we needed to answer the following questions, first:
+\begin{itemize}[noitemsep,nolistsep]
+\item What is the most appropriate LSH technique to apply? Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
 \item Compare different sentence similarity techniques for effectiveness. 
@@
 
-The rest of this paper is organized as follows: In Section 2, we present related work, in Section 3, we explain the algorithm utilizing locality sensitive hashing, in Section 4, we present the working application within MapReduce framework.
-In Section 5, we discuss our experiments with various Wikipedia datasets.
+The rest of this paper is organized as follows: In Section 2, we present related work, in Section 3, we explain the algorithm utilizing locality sensitive hashing, in Section 4, we discuss parameter tuning for Minhash.
+In Section 5, we present the working application within the MapReduce framework.
+In Section 6, we discuss our experiments with various Wikipedia datasets.
 The final section contains concluding remarks and future work.
@@
 
-\section{Algorithm Utilizing Locality Sensitive Hashing}
+\section{Algorithm Utilizing Locality \\ Sensitive Hashing}
 
@@
 
-Describe MapReduce.
+DESCRIBE MAPREDUCE.
 
@@
 Sentences that are too large or too small are discarded.
-The family of hash functions is implemented using a ``Multiply Shift''  \cite{} hashing scheme and is generated from a random seed using the Java Random class.
+The family of hash functions is implemented using a ``Multiply Shift''  CORRECT CITATION GOES HERE hashing scheme and is generated from a random seed using the Java Random class.
 The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
@@
 Also assume that $X$ and $Y$ have edit distance $e$.
+We limit type of edits to changing characters in place.
 Additionally, to simplify our calculations, we assume that edits are localized so that no shingle overlaps more than one edit.
@@
 The enwiki dump is approximately 40G in size and contains 4,113,785 articles (after excluding certain non-article page types).
-Running the first four steps of our application (up to but not including the final edit distance filtering pass) against the enwiki dump on a shared cluster of 16 nodes with (15 GB RAM and 4 cores each) took XXXX (HOW MUCH TIME DID THIS TAKE, SAMET?) minutes.
+Running the first four steps of our application (up to but not including the final edit distance filtering pass) against the enwiki dump on a shared cluster of 16 nodes with (15 GB RAM and 4 cores each) took $\approx 2$ hours.
 
@@
 As a result, while 99\% of our clusters have size below or equal to 30, about 1/3 of the output sentence/article pairs fall into clusters with size greater than 30.
-One explanation for this distribution of sentences is the phenomenon we call ''templatification,'' which we describe in more detail below.)
+One explanation for this distribution of sentences is the phenomenon we call ''templatification,'' which we describe in more detail below.
 
@@
 For example:
-
 \begin{itemize}[noitemsep,nolistsep]
-\item EXAMPLE HERE.
-\item EXAMPLE HERE.
+\item Bush had an approval rating of 22\% by the end of his term in 2008.
+\item Bush, a US President, had an approval rating of 22\% by the end of his term in 2008.
 \end{itemize}
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item EXAMPLE HERE.
-\item EXAMPLE HERE.
+\item Neotropical Ichthyology 11 (1): 73-80.
+\item Neotropical Ichthyology 10 (2): 245-253.
 \end{itemize}
@@
 
-By manually counting a small sample of NNNN output clusters, we came up with the following breakdown of sentence types:
+By manually counting a small sample of 824 output clusters, we came up with a breakdown of sentence types in Table 1.
 
-INSERT CLASSIFY CLUSTER BREAKDOWN HERE
+\begin{table}
+\centering
+\caption{Sentence Breakdown Counts}
+\begin{tabular}{| l | c |}
+\hline
+Not Similar & 3 \\ \hline
+Factual Drift & 65 \\ \hline
+Template & 52 \\ \hline
+Reference & 23 \\ \hline
+Copy Edit & 214 \\ \hline
+Other & 12 \\ \hline
+Identical & 455 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-JOSH, CAN YOU LOOK UP WHAT THE ACTUAL ARTICLES ARE? THAT MIGHT BE INTERESTING.
+\begin{table}
+\centering
+\caption{Top 10 Article Pair Titles}
+\begin{tabular}{| l | c |}
+    \hline
+    \textbf{Article ID} & \textbf{Title} \\ \hline
+    21986867 & 2000 New Year Honours \\ \hline
+    21986897 & 1999 New Year Honours \\ \hline
+    3951586 & Instruments of the United Kingdom, 1994 \\ \hline
+    3951664 & Instruments of the United Kingdom, 1995 \\ \hline
+    1903966 & Management of baldness \\ \hline
+    38088660 & Management of androgenic alopecia \\ \hline
+    1503105 & Jayne Torvill \\ \hline
+    1503115 & Christopher Dean \\ \hline
+    184843 & Henry VI, Part 1 \\ \hline
+    184846 & Henry VI, Part 2 \\ \hline
+    184847 & Henry VI, Part 3 \\ \hline
+    10701462 & List of birds of Zambia \\ \hline
+    10930255 & List of birds of Zimbabwe \\ \hline
+    10930111 & List of birds of Mozambique \\ \hline
+    48711 & Oregon Trail \\ \hline
+    31518964 & History of the Oregon Trail \\
+    \hline
+\end{tabular}
+\end{table}
 
 \section{Conclusion and Future Work}
-This paper presents our work on near-duplicate detection of Wikipedia articles at various granularity levels using LSH technique.
+This paper presents our work on near-duplicate detection of Wikipedia articles at the sentence-granularity level using MinHash, a LSH technique.
 Our novel MapReduce algorithm tackles the problem by transforming it into more manageable pieces where each piece is handled in parallel.
@@
 \section{Acknowledgments}
-We would like to thank all of the anonymous contributors. We would especially like to thank Jimmy Lin for his advise and directions.
+We would especially like to thank Dr. Jimmy Lin for his advise and directions.
 

### 2013-05-09 article/sigproc-sp.tex
Fixing some citations and adding references

@@
 
-\title{Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
+\title{Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
 
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item What is the most appropriate LSH technique to apply? Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
-\item Compare different sentence similarity techniques for effectiveness. 
+\item How effectively does Minhashing approximate edit distance?
+Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
 \item What is the appropriate granularity for analysis? Is comparing multiple consecutive sentences more effective than comparing single sentences? Similarly, what is the best shingle size?
@@
 
-In order to measure document similarity we use a common LSH technique known as MinHash \cite{}.
+In order to measure document similarity we use a common LSH technique known as MinHash \cite{Broder97onthe}.
 A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
@@
 Many signature techniques such as LSH are embarrassingly parallel. In our project, we designed our algorithm around the MapReduce framework.
-
-DESCRIBE MAPREDUCE.
 
@@
 Sentences that are too large or too small are discarded.
-The family of hash functions is implemented using a ``Multiply Shift''  CORRECT CITATION GOES HERE hashing scheme and is generated from a random seed using the Java Random class.
+The family of hash functions is implemented using a ``Multiply Shift'' (http://en.wikipedia.org/wiki/Universal_hashing) hashing scheme and is generated from a random seed using the Java Random class.
 The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
@@
 Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
-A more natural measure to use for this application is edit distance.
-There is no known locality sensitive hashing family for edit distance \citation{}.
+A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \citw{Kirsch06distance-sensitivebloom}.
 
@@
 \emph{Direct Copying} occurs when the same sentence has been copied into another (or possibly the same) article.
-This can happen for many reasons, including articles that deal with similar subjects, or articles that are subtopics of other topics.
-(SOME EXAMPLES?).
-Similarly, \emph{Direct Copying with Copy Editing} occurs when the same sentence has been copied into another article and then one or both sentences has been edited for style or clarity.
+This can happen for many reasons, including articles that deal with similar subjects, or articles that are subtopics of other topics Similarly, \emph{Direct Copying with Copy Editing} occurs when the same sentence has been copied into another article and then one or both sentences has been edited for style or clarity.
 For example:

### 2013-05-09 article/sigproc-sp.tex
Fixing up some other citation junk

@@
 Sentences that are too large or too small are discarded.
-The family of hash functions is implemented using a ``Multiply Shift'' (http://en.wikipedia.org/wiki/Universal_hashing) hashing scheme and is generated from a random seed using the Java Random class.
+The family of hash functions is implemented using a ``Multiply Shift'' (\url{http://en.wikipedia.org/wiki/Universal_hashing}) hashing scheme and is generated from a random seed using the Java Random class.
 The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
@@
 Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
-A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \citw{Kirsch06distance-sensitivebloom}.
+A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \cite{Kirsch06distance-sensitivebloom}.
 

### 2013-08-20 src/main/wikiduper/clir/minhashwiki/DocSentence.java
Fixed comparison and equality for custom datatypes.

@@ -135,5 +135,18 @@ public void setLanguage(String language) {
     this.language = language;
 }
 
+@Override
+public int hashCode(){
+    String str = id + "," + sentence + "," + language;
+    return str.hashCode();
+}
+@Override
+public boolean equals(Object o){
+    if(!(o instanceof DocSentence)){
+        return false;
+    }
+    DocSentence otherdoc = (DocSentence) o;
+    return (otherdoc.id==this.id) && otherdoc.language.equals(this.language) && (otherdoc.sentence==this.sentence);
+}
 
 }

### 2013-08-20 src/main/wikiduper/clir/minhashwiki/GetSentenceClusters.java

@@ -58,6 +58,7 @@ import org.wikiclean.WikiCleanBuilder;
 import wikiduper.wikipedia.WikipediaPage;
 import edu.umd.cloud9.io.array.ArrayListWritable;
 import edu.umd.cloud9.io.pair.PairOfLongInt;
+import edu.umd.cloud9.io.pair.PairOfLongString;
 import edu.umd.cloud9.io.pair.PairOfLongs;
 import edu.umd.cloud9.io.pair.PairOfStrings;
 
@@ -125,21 +126,18 @@ public class GetSentenceClusters extends Configured implements Tool {
             elang = job.get("wiki.language.e","en");
             flang = job.get("wiki.language.f","de");
             
-            int ecode = job.getInt("wiki.language.code.e",-1);
-            int fcode = job.getInt("wiki.language.code.f",1);
-            
-            
+
             try{
                 FileSystem fs = FileSystem.get(job);
                 FSDataInputStream in = fs.open(new Path(docMapFile));
                 SequenceFile.Reader reader;
                 reader = new SequenceFile.Reader(job, SequenceFile.Reader.stream(in));
-                PairOfLongs docidcode = new PairOfLongs();
+                PairOfLongString docidlang = new PairOfLongString();
                 ArrayListWritable<PairOfLongs> sentlist = new ArrayListWritable<PairOfLongs>();
-                while(reader.next(docidcode, sentlist)){
-                    long docid = docidcode.getLeftElement();
-                    long incode = docidcode.getRightElement();
-                    if(incode == ecode){
+                while(reader.next(docidlang, sentlist)){
+                    long docid = docidlang.getLeftElement();
+                    String inlang = docidlang.getRightElement();
+                    if(inlang.equals(elang)){
                         edocmap.put(docid, new TreeMap<Long, Long>());
                         for(PairOfLongs p : sentlist){
                             if(edocmap.get(docid).containsKey(p.getLeftElement())){
@@ -148,7 +146,7 @@ public class GetSentenceClusters extends Configured implements Tool {
                             edocmap.get(docid).put(p.getLeftElement(), p.getRightElement());
                         }
                     }
-                    if(incode == fcode){
+                    if(inlang.equals(flang)){
                         fdocmap.put(docid, new TreeMap<Long, Long>());
                         for(PairOfLongs p : sentlist){
                             if(fdocmap.get(docid).containsKey(p.getLeftElement())){
[…]

### 2013-08-20 src/main/wikiduper/clir/minhashwiki/MergeClusters.java

@@ -49,6 +49,7 @@ import org.apache.log4j.Logger;
 
 import edu.umd.cloud9.io.array.ArrayListOfLongsWritable;
 import edu.umd.cloud9.io.array.ArrayListWritable;
+import edu.umd.cloud9.io.pair.PairOfLongString;
 import edu.umd.cloud9.io.pair.PairOfLongs;
 import edu.umd.cloud9.io.pair.PairOfStringInt;
 
@@ -110,13 +111,14 @@ public class MergeClusters extends Configured implements Tool {
             TreeMap<Integer, HashSet<DocSentence>> clustermap = new TreeMap<Integer, HashSet<DocSentence>>();
             //TreeMap<Integer, HashSet<ArrayListOfLongsWritable>> clustermap = new TreeMap<Integer, HashSet<ArrayListOfLongsWritable>>();
             // map from doc id to sentence numbers
-            TreeMap<PairOfLongs, TreeSet<PairOfLongs>> docmap = new TreeMap<PairOfLongs, TreeSet<PairOfLongs>>();
-            readBuckets2(filein,conf,clustermap);
+            TreeMap<PairOfLongString, TreeSet<PairOfLongs>> docmap = new TreeMap<PairOfLongString, TreeSet<PairOfLongs>>();
+            readBuckets22(filein,conf,clustermap);
             
             // Renumber components
             int componentct = 0;
             for(Integer cnum : clustermap.keySet()){
                 HashSet<DocSentence> comp = clustermap.get(cnum);
+                System.out.println("cnum="+cnum + "," + comp.size()+"\n");
                 for(DocSentence p : comp){
                 //for(ArrayListOfLongsWritable p : comp){
                     
@@ -127,9 +129,9 @@ public class MergeClusters extends Configured implements Tool {
                        // System.out.println(m.group(1));// + " " + m.group(2) + " " + m.group(3));
                     long docid = p.getId();
                     long sentencenum = p.getSentence();
-                    long lang = p.getLanguage().equals("en")?1:-1;
+                    String lang = p.getLanguage();
 
-                    PairOfLongs doclang = new PairOfLongs();
+                    PairOfLongString doclang = new PairOfLongString();
                     doclang.set(docid, lang);
                     if(!docmap.containsKey(doclang)){
                          docmap.put(doclang, new TreeSet<PairOfLongs>());
@@ -146,12 +148,12 @@ public class MergeClusters extends Configured implements Tool {
[…]

### 2013-08-20 src/main/wikiduper/clir/minhashwiki/Signature.java

@@ -152,6 +152,12 @@ public int compareTo(Signature s) {
 
 }
 
+@Override
+public boolean equals(Object o){
+    if(!(o instanceof Signature)) return false;
+    return (this.compareTo((Signature) o) == 0);
+
+}
 
 
 

### 2013-10-27 article/article-draft.tex
New draft of article

--- 2013-05-09 article/sigproc-sp.tex
@@
 \usepackage{algorithm}
+\usepackage{natbib}
 
@@
 
-\title{Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}}
+\title{Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia}
 
@@
        \email{jgbrad1@cs.umd.edu}
-\alignauthor Sarah Weissman\\
+\alignauthor Sarah E. Weissman\\
        \affaddr{University of Maryland}\\
@@
 
-\date{9 May 2013}
+\date{October 9, 2013}
 
@@
 \begin{abstract}
-The growth of Internet has enabled collaboration and cooperation on a large scale, resulting in an abundant number of near-duplicate web documents.
-The range of near-duplicate occurrences is even more evident within Wikipedia articles, due to its editing largely being open to the online community.
-Except for particularly sensitive and/or vandalism-prone pages that are "protected" to some degree from editing, the reader of an article can edit the text by copying from another article without prior approval.
-There is no current automated mechanism for truth validation.
-Although we are not inspired to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
+The growth of the Internet has enabled collaboration and cooperation on a large scale, resulting in an abundant number of near-duplicate web documents.
+Information is propagated on a large scale, which means that finding (and correcting) factual errors is made more difficult, since such errors may be duplicated many times over in different locations.
+Wikipedia articles, which are written and edited by an open community of mostly anonymous users are a prime candidate for copying of information.
+With few exceptions, the reader of any article can edit the text by copying from another article or an outside source without prior approval or confirmation of correctness.
+Although Wikipedia has its own policies and procedures for maintaining articles and improving quality, questions of the quality and accuracy of information on the website remain.
+Although we do not directy attempt to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
+Such near duplicate sentences may reflect factual information that has been updated in one article and not another, or merely inconsistencies that should be flagged and addressed.
 
-In this paper, we describe a novel similarity detection algorithm that utilizes a locality sensitive hashing (LSH) technique on the MapReduce framework.
-The algorithm has been designed and implemented to detect similar articles using large Wikipedia dumps.
-Experimental results appear to support that our method is able to efficiently and effectively detect similar articles across Wikipedia.
+In this paper, we describe a similarity detection algorithm for Wikipedia articles that utilizes a locality sensitive hashing (LSH) technique on the MapReduce framework.
+The algorithm has been designed and implemented to detect similar content at the sentence level using large Wikipedia dumps.
+We also describe a heuristic method for classifying types of duplications on Wikipedia, which could be used for selecting and prioritizing editing efforts.
 \end{abstract}
@@
 \section{Introduction}
-The online encyclopedia Wikipedia is a multilingual, free resource with its 26 million articles.
-All these articles, with over 4.2 million in English alone, are written collaboratively by volunteer contributors around the world.
-Most articles can be edited by anyone with internet access, thus there are currently approximately 100,000 active contributors.
-In light of these facts, it is clear that the unprecedented example of such a large-scale collaboration effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity \cite{wiki:weblink}
+The online encyclopedia Wikipedia is a collaboratively edited, multilingual, free resource.
+As of xxx date, it contains 26 million articles, over 4.2 million in English alone.
+These articles are written and edited by volunteer contributors around the world.
+Most articles can be edited by anyone with internet access, and there are currently approximately 100,000 active contributors.
 
-Furthermore, Wikipedia has a history of generating controversy over editorial quality and factual correctness.
-Although some studies have found Wikipedia's accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.
-Since Wikipedia may be edited anonymously, information is often freely copied between web sources and even between Wikipedia articles.
+Because of its open nature, Wikipedia has a history of generating controversy over editorial quality and factual correctness.
+Although some studies have found Wikipedia's accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.[References??] Since Wikipedia may be edited anonymously, information may freely copied between web sources and even between Wikipedia articles without verification.
 Additionally, many articles in Wikipedia lack citations.
-There is little mechanism for detecting and correcting such errors.
-One potential source of error on Wikipedia is factual information that varies over time and is not updated.
-Wilkinson found that the distribution of article edits has a long tail, meaning that a small number of articles have many edits while most articles have few, and that the number of edits is directly related to article quality.
+Although there are active communities of editors who contribute to the upkeep of various articles, often focusing on a partiular subject area and expanding and improving the related content, still much of Wikipedia content is created in an unsupervised manner.
+Wilkinson found the distribution of article edits on Wikipedia to have a long tail, meaning that a small number of articles have many edits while most articles have few, and that the number of edits is directly related to article quality.
 Articles with low edits and low editorial attention, are less likely to be updated when new information is available \cite{wilkinson:wiki}.
 
-As a step toward identifying factual errors, we investigated the problem of finding near duplicate sentences on Wikipedia.
-Such near duplicate sentences may reflect factual information that has been updated in one article and not another, or merely inconsistencies that should be flagged and addressed.
+Under such conditions, this type of large-scale collaborative effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity \cite{wiki:weblink} [??].
+For our purposes, we focus primarily on the sentence level.
+Near duplicate sentences may reflect factual information that has been updated in one article and not another (for example, information that varies over time, like populations or a country's GDP), or merely inconsistencies that should be flagged and addressed.
 
-In order to come up with a novel algorithm that would allow us to detect near-duplicate sentences within Wikipedia articles, we decided that we needed to answer the following questions, first:
+Our approach applies minhashin, a well known, scalable, locality sensitive hashing (LSH) technique for near duplicate document detection.
+Since we are assuming the content we are looking for is not just similar, but has diverged due to an editorial process, as part of this work we investigate how well minhash approximates edit distance.
+We investigate the following questions:
 \begin{itemize}[noitemsep,nolistsep]
-\item How effectively does Minhashing approximate edit distance?
+\item How effectively does minhashing approximate edit distance?
 Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
-\item What is the appropriate granularity for analysis? Is comparing multiple consecutive sentences more effective than comparing single sentences? Similarly, what is the best shingle size?
 \item How well do techniques for detecting near duplicate documents work when applied at the sentence level?
-\item Do near duplicate sentences correspond to factual errors? Can these errors be automatically detected and/or corrections suggested?
+\item Do near duplicate sentences correspond to factual errors?
 \end{itemize}
@@
 Along with these questions, we also considered the scalability and efficiency issues due to the large size of Wikipedia.
-To address these issues, we used the MapReduce computing framework and LSH techniques to group sentences with the same signatures and identify near duplicates.
+To address these issues, we implemented our algorithm on the MapReduce computing framework.
 
@@
 A number of techniques have been implemented to identify similarity between documents in the literature.
-These techniques usually differ in terms of corpus of interest, signature representing the document, feature-set determined by the system, and the end goal.
-In addition to these differences, one can also consider the efficiency and scalability of the system, overall.
-
-In this section, we will go over some of theses techniques offered in the literature. Additionally, we will highlight our novel contribution.
+These techniques usually differ in terms of corpus of interest, signature representing the document, feature-set determined by the system, and the end goal of the analysis.
 
@@
 In order to handle large Wikipedia dumps with the order of tens or hundreds of gigabytes and even a few terabytes, we used MapReduce framework in this work, that was introduced by Dean and Ghemawat \cite{dean:mapreduce}.
-The implementation is able to stream the compressed bz2 dumps and feed into mappers and reducers for further processing, which will be detailed in the following sections.
 
@@
 
-%In order to measure document similarity we use a common LSH technique known as minhashing \cite{}.
+In order to measure document similarity we use a common LSH technique known as MinHash (\cite{broder:resemblance}).
 A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
-In our case input documents are sentences.
-Each sentence is broken up into n-gram ``shingles''.
-For each shingle set $S$ we calculate $\{min_{s \in S}(F_i(s)\}$, the set of minimum hashes over the hash family.
-The signature on a document d is a vector of $K$ minhashes from the set of minimum hashes.
-In order to minimize false negatives we apply the technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.
-
-In order to measure document similarity we use a common LSH technique known as MinHash \cite{Broder97onthe}.
-A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
-In our case, we denote ''documents'' to mean sentences found within the content of Wikipedia articles.
-Each sentence is broken up into n-gram ``shingles''.
-For each shingle set $S$ we calculate the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family.
+(In our case, input ''documents'' are individual sentences found within the content of Wikipedia articles.) Each document is broken up into n-gram ``shingles'' and for each shingle set $S$ a set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family is produced.
 The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes.
@@
 
-Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 library (\url{https://github.com/lintool/Cloud9}) for parsing Wikipedia page text from the Wikipedia XML dump format.
-Sentences are parsed out over each document using a regular expression.
+Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 (\url{https://github.com/lintool/Cloud9}) and WikiClean (\url{https://github.com/lintool/wikiclean/}) libraries for parsing Wikipedia page text from the Wikipedia XML dump format.
+An open source implementationis available on Github (\url{https://github.com/seweissman/wikiduper}).
+
+%Sentences are parsed out over each document using a regular expression.
 Sentences that are too large or too small are discarded.
-The family of hash functions is implemented using a ``Multiply Shift'' (http://en.wikipedia.org/wiki/Universal_hashing) hashing scheme and is generated from a random seed using the Java Random class.
+The family of hash functions is implemented using a ``Multiply Shift'' (\url{http://en.wikipedia.org/wiki/Universal_hashing}) hashing scheme and is generated from a random seed using the Java Random class.
 The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
@@
 
-Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
-A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \citw{Kirsch06distance-sensitivebloom}.
+%Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
+A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \cite{Kirsch06distance-sensitivebloom}.
 
@@
 In order to estimate the affect of shingle length on false positive rate we ran a number of experiments for a 1 G collection of wikipedia documents.
-For fixed $N=10$ we ran experiments for three values of $K=\{8,9,10\}$ and $5 \le L \le 15$.
+For fixed $N=10$ we ran experiments for three values of $K=\{8,9,10\}$ and $8 \le L \le 16$.
 Setting a normalized edit distance threshold of $e = .25$, we calculated the total number of ''good'' ($e <= .25$) and ''bad'' ($e > .25$) (unique) sentence pairs as well as the false positive rate (\# bad pairs divided by the total number of sentences).
@@
 
-We can see from the graphs in Figure \ref{ed-grid} that all three statistics hit a low at shingle length 12 or 13.
-This means that in order to achieve the lowest false positive rate we should use parameter settings around $N=10, K=10$ and $L=12$ or $L=13$.
-However the number of \emph{good} pairs also hits a minimum at $L = 12$, which means that while overall the output is more precise, we are also missing output pairs.
-
-Another feature of the graphs in Figure \ref{ed-grid} that stands out is that while the false positive rate and total number of bad pairs bottoms out at around $L=12$, for $L > 12$ the output quality actually decreases.
-This is counter to our intuition that output quality increases as the length of the shingle increases.
-One would expect larger shingles to correspond to closer edit distance scores, since larger shingles correspond to longer consecutive sequences of identical text.
-One explanation for these counter-intuitive results could be limitations of the underlying hash family.
-If longer shingle lengths lead to greater hash collisions this could explain the increased numbers of bad pairs.
-Improving the hash function to reduce collisions could improve results.
-
-Since minimizing the false positive rate also means minimizing reducing good pairs, another option is to let parameters to maximize good output and use edit distance as a secondary filter.
-With this approach our experimental results suggest that the best parameter combination would be $N=10, K=8, L=10$.
+As we might expect, as shingle length increases, the false positive rate decreases.
+However, the total number of good pairs also decreases, implying that our false negative rate is also increasing.
+When applying these techniques, increased recall will come at the price of decreased precision.
+Because of this, in a real implementation, it would likely be desirable to set requirements for recall, then use secondary filtering to increase precision.
+For example, actual edit distance could be applied as a secondary filter.
 
@@
 \centering
-\epsfig{file=edgrid.eps,width=3.5in}
+\epsfig{file=edgridl.eps,width=3.5in}
 \caption{False Positive Rate, Good Count, Bad Count for $N=10, K \in \{8,9,10\}, 5 \le L \le 15$}
@@
 
-\section{Working Application}
-
-While the Minhash signature code provides the raw similarity scores, it is one part of a larger framework composed of several pieces, described below.
-The input to the process is an XML dump format.
-(See \url{http://en.wikipedia.org/wiki/Wikipedia:Database_download} for details.) The output of the process is a list of sentence clusters containing the original article title and sentence text.
-Decomposing the sentence clustering into several pieces allows us to minimize the amount of raw text that gets passed between mappers and reducers, thus improving scalability.
-
-The process can be summarized as follows:
-
-\begin{enumerate}
-\item \textbf{Preprocess Wikipedia Pages} - Using a utility from the Cloud9 library, preprocess the raw Wikipedia dump into a SequenceFile format.
-Working with SequenceFiles gives the option to use block or record compressed input compatible with the MapReduce framework.
-\item \textbf{Minhash Wikipedia Sentences} - Reads processed Wikipedia input, and uses a regular expression to match sentences in the article text.
-Outputs a file of signature ``buckets'' organized by signature.
-Each output sentence is represented by a (docid,sentenceid) pair.
-\item \textbf{Dedup Sentence Buckets} - Because multiple sentences may occur in each bucket, a second MapReduce job is used to map from buckets to raw sentence pairs, removing duplicates.
-\item \textbf{Compute Sentence Clusters} - Performs a local (i.e., non-MapReduce) connected component analysis on the dedup-ed pairs to form sentence clusters.
-\item \textbf{Get Sentence Text} - Maps clustered sentences (represented by (docid,sentenceid) pairs) back to sentence text by streaming over the Wikipedia input a second time and recovering the corresponding sentences by ID.
-\item \textbf{Edit Distance Filter} - \emph{(optional)} For each output cluster and filter all pairs within the cluster by desired edit distance threshold.
-\end{enumerate}
-
-\subsection{Limitations to Our Approach}
-
-In addition to the aforementioned hash issue there are other limitations in our implementation and improvements that could be made.
-
-\emph{Data cleanliness} - The Cloud9 utilities that process Wikipedia code do some preprocessing of non-text elements from Wikipedia pages.
-However there is still improvements that could be made.
-Section headings can confuse our regular expression mapping, causing pieces of extraneous text to be appended to sentences.
-Parsing page text with a better understanding of how Wikipedia articles are structured could improve our input data.
-Additionally, keeping track of the order in which sentences occur on a page could improve analysis.
-For example, references and external links are typically found at the bottom of a Wikipeda page.
-More carefully filtering text based on sentence depth could improve results.
-
-\emph{Sentence matching} - Since Wikipedia data is not chunked by sentence, we rely on regular expression matching to break up input text into sentences.
-Since sentences have recursive structure, our regular expression can lead to stack overflow exceptions from the underlying recursive pattern match search.
-Setting bounds on the sentence structure nesting could provide more reliable results.
-The encyclopedic style of Wikipedia may lend itself to simpler sentence structures that don't require a general purpose sentence matching algorithm.
-
-\emph{Large clusters} - Since we rely on a connected component analysis to compute the final sentence clusters, our large clusters can be a bottleneck.
-Unfortunately, the Wikipedia data does contain large clusters of similar sentences (see the discussion of templatification below).
-Since our initial experimental results suggest that more interesting clusters (for example, sentence clusters representing copied data with factual errors) are much smaller (on the order of 2 or 3 sentences per cluster), we set a limit on maximum bucket size and only consider the first $n$ sentences in any bucket up to that limit.
-Setting a limit on cluster size helps ensure more predictable runtime and discards large portions of relatively uninteresting clusters, making output data more manageable.
-
-\emph{Non-determinism} - Our current implementation of Minhash suffers from a yet unidentified source of non-determinism.
-This affects the number of output records produced from the Minhashing stage of our implementation from one run to the next and has unknown effects on output quality.
-
 \section{Experiments and Discussion}
 
-We performed several analyses to provide more insight into the occurence of duplicate sentences.
+%We performed several analyses to provide more insight into the occurence of duplicate sentences.
 In particular, we were interested in detecting similar sentences that arose from copying text from one article to another since such instances would represent content that is either redundant, or content that has diverged in the sense that either the original or the copy was edited for clarification of factual correctness and the other was not.
@@
 
+\section{Limitations of Our Approach}
+
+In addition to the aforementioned hash issue there are other limitations in our implementation and improvements that could be made.
+
+\emph{Data cleanliness} - The Cloud9 utilities that process Wikipedia code do some preprocessing of non-text elements from Wikipedia pages.
+However there is still improvements that could be made.
+Section headings can confuse our regular expression mapping, causing pieces of extraneous text to be appended to sentences.
+Parsing page text with a better understanding of how Wikipedia articles are structured could improve our input data.
+Additionally, keeping track of the order in which sentences occur on a page could improve analysis.
+For example, references and external links are typically found at the bottom of a Wikipeda page.
+More carefully filtering text based on sentence depth could improve results.
+
+\emph{Sentence matching} - Since Wikipedia data is not chunked by sentence, we rely on regular expression matching to break up input text into sentences.
+Since sentences have recursive structure, our regular expression can lead to stack overflow exceptions from the underlying recursive pattern match search.
+Setting bounds on the sentence structure nesting could provide more reliable results.
+The encyclopedic style of Wikipedia may lend itself to simpler sentence structures that don't require a general purpose sentence matching algorithm.
+
+\emph{Large clusters} - Since we rely on a connected component analysis to compute the final sentence clusters, our large clusters can be a bottleneck.
+Unfortunately, the Wikipedia data does contain large clusters of similar sentences (see the discussion of templatification below).
+Since our initial experimental results suggest that more interesting clusters (for example, sentence clusters representing copied data with factual errors) are much smaller (on the order of 2 or 3 sentences per cluster), we set a limit on maximum bucket size and only consider the first $n$ sentences in any bucket up to that limit.
+Setting a limit on cluster size helps ensure more predictable runtime and discards large portions of relatively uninteresting clusters, making output data more manageable.
+
+\emph{Non-determinism} - Our current implementation of Minhash suffers from a yet unidentified source of non-determinism.
+This affects the number of output records produced from the Minhashing stage of our implementation from one run to the next and has unknown effects on output quality.
+
 \section{Conclusion and Future Work}

### 2013-11-02 article/article-draft.tex
Added unique title count back in to histogram code

@@
 
-All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 4/2013) obtained from dumps.wikimedia.org.
-The enwiki dump is approximately 40G in size and contains 4,113,785 articles (after excluding certain non-article page types).
-Running the first four steps of our application (up to but not including the final edit distance filtering pass) against the enwiki dump on a shared cluster of 16 nodes with (15 GB RAM and 4 cores each) took $\approx 2$ hours.
+All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 7/2013) obtained from dumps.wikimedia.org.
+The enwiki dump is approximately 42G in size and contains 10,218,778 articles (after excluding certain non-article page types).
+Running our application on the enwiki dump on a shared cluster of 16 nodes (20 GB RAM and 4?
+cores each) took $\approx$ 25 minutes.
 
-After minhashing and deduplification, we found a total of 9,465,881 similar article/sentence pairs.
-After clustering these pairs, the total number of similar sentence clusters was 415,936, including 1,792,748 unique article/sentence pairs over 759,297 article titles.
-The total number of unique sentences over all cluster was 1,305,359.
+The total number of similar sentence clusters was 1,151,640, including 3,496,074 article/sentence pairs over  article titles. The total number of unique sentences over all cluster was 1,305,359.
 

### 2013-11-02 src/main/wikiduper/analysis/HistogramClusters.java

@@ -111,7 +111,7 @@ public class HistogramClusters extends Configured implements Tool {
         TreeMap<Integer,Integer> sentencehistogram = new TreeMap<Integer,Integer>();
         
         // Sets to keep track of overall unique title and sentences
-        //HashSet<String> titleset = new HashSet<String>();
+        HashSet<String> titleset = new HashSet<String>();
         //HashSet<String> sentenceset = new HashSet<String>();
         
         // Per cluster data structures
@@ -214,7 +214,7 @@ public class HistogramClusters extends Configured implements Tool {
                     clustersentences.add(sentence);
                     clustertitles.add(title);
                     
-                    //titleset.add(title);
+                    titleset.add(title);
                     //sentenceset.add(sentence);
                 }else{
                     //System.err.println("Bad line " + linect + " : " + articlesentence.toString());
@@ -286,7 +286,7 @@ public class HistogramClusters extends Configured implements Tool {
         
         System.out.println("N lines: " + linect);
         System.out.println("N clusters: " + clusterct);            
-        //System.out.println("N unique titles: " + titleset.size());
+        System.out.println("N unique titles: " + titleset.size());
         //System.out.println("N unique sentences: " + sentenceset.size());
         
         

### 2013-11-02 src/main/wikiduper/analysis/HistogramClusters.java
Added unique sentence count back in to histogram code

@@ -111,8 +111,8 @@ public class HistogramClusters extends Configured implements Tool {
         TreeMap<Integer,Integer> sentencehistogram = new TreeMap<Integer,Integer>();
         
         // Sets to keep track of overall unique title and sentences
-        HashSet<String> titleset = new HashSet<String>();
-        //HashSet<String> sentenceset = new HashSet<String>();
+        //HashSet<String> titleset = new HashSet<String>();
+        HashSet<String> sentenceset = new HashSet<String>();
         
         // Per cluster data structures
         ArrayList<String> cluster = new ArrayList<String>();
@@ -214,8 +214,8 @@ public class HistogramClusters extends Configured implements Tool {
                     clustersentences.add(sentence);
                     clustertitles.add(title);
                     
-                    titleset.add(title);
-                    //sentenceset.add(sentence);
+                    //titleset.add(title);
+                    sentenceset.add(sentence);
                 }else{
                     //System.err.println("Bad line " + linect + " : " + articlesentence.toString());
                     System.err.println("Bad line " + linect + " : " + linetext);
@@ -286,8 +286,8 @@ public class HistogramClusters extends Configured implements Tool {
         
         System.out.println("N lines: " + linect);
         System.out.println("N clusters: " + clusterct);            
-        System.out.println("N unique titles: " + titleset.size());
-        //System.out.println("N unique sentences: " + sentenceset.size());
+        //System.out.println("N unique titles: " + titleset.size());
+        System.out.println("N unique sentences: " + sentenceset.size());
         
         
         StringBuffer histvals = new StringBuffer();

### 2013-11-03 article/article-draft.tex
Added count of template sentences to template scoring code

@@
 
-The total number of similar sentence clusters was 1,151,640, including 3,496,074 article/sentence pairs over  article titles. The total number of unique sentences over all cluster was 1,305,359.
+The total number of similar sentence clusters was 1,151,640, including 3,496,074 article/sentence pairs over 1,091,804 article titles.
+The total number of unique sentences over all clusters was 2,361,886.
 
-Cluster sizes ranged from 2 to 28,008.
-(See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, but the distribution of cluster sizes exhibits a long tail.
-As a result, while 99\% of our clusters have size below or equal to 30, about 1/3 of the output sentence/article pairs fall into clusters with size greater than 30.
+Cluster sizes ranged from 2 to 42,901.
+(See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, about 99\% of our clusters have size below or equal to 10, but about 1/4 of the output sentence/article pairs fall into clusters with size greater than 10.
 One explanation for this distribution of sentences is the phenomenon we call ''templatification,'' which we describe in more detail below.
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Bush had an approval rating of 22\% by the end of his term in 2008.
-\item Obama had an approval rating of 56\% by the end of his term in 2012.
+
+\item Of the agricultural land 40.4\% is used for growing crops and 26.6\% is pastures while 2.2\% is used for orchards or vine crops. [Gondiswil]
+\item Of the agricultural land 26.1\% is used for growing crops and 30.2\% is pastures while 3.0\% is used for orchards or vine crops. [Kleindietwil]
+\item Of the agricultural land 37.8\% is used for growing crops and 35.5\% is pastures while 2.2\% is used for orchards or vine crops. [Leimiswil]
 
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Bush had an approval rating of 22\% by the end of his term in 2008.
-\item Bush, a US President, had an approval rating of 22\% by the end of his term in 2008.
+\item In dry areas it may only emerge from its burrow for a few weeks when conditions are right and usually at night but in areas with permanent water bodies and abundant rain it may be active all day.
+[Great Plains toad]
+\item In dry areas it may only emerge from its burrow for a few weeks when conditions are right and only at night but in areas with permanent water bodies and abundant rain it may be active all day.
+[List of amphibians and reptiles of Montana]
 \end{itemize}
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Obama had an approval rating of 56\% by the end of his term in 2012.
-\item Obama had an approval rating of 46\% by the end of his term in 2012.
+\item The color of the upper rim of an astronomical object could go from green to blue to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
+[Green flash]
+\item The color of the upper limb of an astronomical object could go from blue to green to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
+[Mirage of astronomical objects]
 \end{itemize}
@@
 
-By manually counting a small sample of 824 output clusters, we came up with a breakdown of sentence types in Table 1.
+By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table 1.
 
@@
 \caption{Sentence Breakdown Counts}
-\begin{tabular}{| l | c |}
+\begin{tabular}{| l | c | c |}
 \hline
-Not Similar & 3 \\ \hline
-Factual Drift & 65 \\ \hline
-Template & 52 \\ \hline
-Reference & 23 \\ \hline
-Copy Edit & 214 \\ \hline
-Other & 12 \\ \hline
-Identical & 455 \\
+Factual Drift & 121 & 5.78\% \\ \hline
+Template & 632 & 30.18\% \\ \hline
+Reference & 7 & 0.33\% \\ \hline      
+Copy Edit & 283 & 13.51\% \\ \hline
+Identical & 948 & 45.27\% \\ \hline
+Other & 103 & 2.92\% \\ \hline
 \hline
@@
 \end{table}
+
+To get a rough estimate of the number of template clusters, we develop a heuristic score on low frequency words in the cluster word set to identify templates.
+For our purposes a low-frequency word is one that occurs in less than half of the cluster sentences.
+The score we use is:
+\[(\#numeric + \#proper)/(\#numeric + \#proper + \#other)\]
+Where \#numeric is the number of numeric terms in the cluster word set (all unique words occuring in the cluster), \#proper is the number of proper nouns in the cluster word set (i.e.
+capitalized words), and \#other is the number of other words.
+
+Applying the score to our hand-classified clusters shows us that this score does separate between template and non-template word.
+(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.)
+
+After applying the score to the entire set of wiki clusters (with a score threshold of .6), I get 122,698 template clusters and 268,433 non-template clusters.
+The template clusters contain 777,940 sentences (689743 unique) and the non-template 698,628 (400,458 unique).
+
+\begin{figure}
+\centering
+\includegraphics[width=3.5in, keepaspectratio = true]{classifyscoreswiki.pdf}
+\caption{Histogram of Hand Labeled Clusters by Template Heuristic Score.}
+\label{heuristic}
+\end{figure}
 

### 2013-11-03 src/main/wikiduper/analysis/TemplateClusters.java

@@ -169,6 +169,7 @@ public class TemplateClusters extends Configured implements Tool {
         Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
         
         int templateCt = 0;
+        int templateSentencesCt = 0;
         int identicalCt = 0;
         int otherCt = 0;
         int speciesCt = 0;
@@ -269,6 +270,7 @@ public class TemplateClusters extends Configured implements Tool {
                             }
                         }else if(clustersentences.size() >= count_threshold && score >= score_threshold){
                             templateCt++;
+                            templateSentencesCt += clustersentences.size();
                             for(String s : cluster){
                                 Text textout = new Text();
                                 textout.set(s);
@@ -385,6 +387,7 @@ public class TemplateClusters extends Configured implements Tool {
                 }
             }else if(clustersentences.size() >= count_threshold && score >= score_threshold){
                 templateCt++;
+                templateSentencesCt += clustersentences.size();
                 for(String s : cluster){
                     Text textout = new Text();
                     textout.set(s);
@@ -449,6 +452,7 @@ public class TemplateClusters extends Configured implements Tool {
         
         System.out.println("N identical clusters: " + identicalCt);
         System.out.println("N template clusters: " + templateCt);
+        System.out.println("N template sentences: " + templateSentencesCt);
         System.out.println("N other clusters: " + otherCt);
         System.out.println("N other pair clusters: " + otherCt2);
         System.out.println("N species clusters: " + speciesCt);

### 2013-11-03 article/article-draft.tex
Added count of non-template sentences to template scoring code

@@
 
-After applying the score to the entire set of wiki clusters (with a score threshold of .6), I get 122,698 template clusters and 268,433 non-template clusters.
-The template clusters contain 777,940 sentences (689743 unique) and the non-template 698,628 (400,458 unique).
+N lines: 3496074
+N clusters: 1151620
+N identical clusters: 666212
+N template clusters: 55430
+N other clusters: 20745
+N other pair clusters: 407963
+N species clusters: 1270
+
+N lines: 3496074
+N clusters: 1151620
+N identical clusters: 666212
+N template clusters: 244660
+N template sentences: 1116932
+N other clusters: 20745
+N other pair clusters: 218840
+N species clusters: 1163
+^C
+
+After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
+The template clusters contain 1,116,932, and the non-template
 
@@
 \centering
-\includegraphics[width=3.5in, keepaspectratio = true]{classifyscoreswiki.pdf}
+\includegraphics[width=3.5in, keepaspectratio = true]{classifyscoreswikinew.pdf}
 \caption{Histogram of Hand Labeled Clusters by Template Heuristic Score.}

### 2013-11-03 src/main/wikiduper/analysis/TemplateClusters.java

@@ -170,6 +170,7 @@ public class TemplateClusters extends Configured implements Tool {
         
         int templateCt = 0;
         int templateSentencesCt = 0;
+        int nontemplateSentencesCt = 0;
         int identicalCt = 0;
         int otherCt = 0;
         int speciesCt = 0;
@@ -263,6 +264,7 @@ public class TemplateClusters extends Configured implements Tool {
                         // identical case
                         if(clustersentences.size() == 1){
                             identicalCt++;
+                            nontemplateSentencesCt += clustersentences.size();
                             for(String s : cluster){
                                 Text textout = new Text();
                                 textout.set(s);
@@ -278,6 +280,7 @@ public class TemplateClusters extends Configured implements Tool {
                             }
                         }else if(isSpecies == 1){
                             speciesCt++;
+                            nontemplateSentencesCt += clustersentences.size();
                             for(String s : cluster){
                                 Text textout = new Text();
                                 textout.set(s);
@@ -285,6 +288,7 @@ public class TemplateClusters extends Configured implements Tool {
                             }
                         }else if(clustersentences.size() == 2){
                             otherCt2++;
+                            nontemplateSentencesCt += clustersentences.size();
                             for(String s : cluster){
                                 Text textout = new Text();
                                 textout.set(s);
@@ -292,6 +296,7 @@ public class TemplateClusters extends Configured implements Tool {
                             }
                         }else{
                             otherCt++;
+                            nontemplateSentencesCt += clustersentences.size();
                             for(String s : cluster){
                                 Text textout = new Text();
                                 textout.set(s);
@@ -380,6 +385,7 @@ public class TemplateClusters extends Configured implements Tool {
             // identical case
             if(clustersentences.size() == 1){
                 identicalCt++;
+                nontemplateSentencesCt += clustersentences.size();
                 for(String s : cluster){
                     Text textout = new Text();
                     textout.set(s);
@@ -395,6 +401,7 @@ public class TemplateClusters extends Configured implements Tool {
                 }
             }else if(isSpecies == 1){
                 speciesCt++;
+                nontemplateSentencesCt += clustersentences.size();
                 for(String s : cluster){
                     Text textout = new Text();
                     textout.set(s);
@@ -402,6 +409,7 @@ public class TemplateClusters extends Configured implements Tool {
                 }
             }else if(clustersentences.size() == 2){
                 otherCt2++;
[…]

### 2013-11-03 article/article-draft.tex
Added a more generic cluster scoring method to TemplateCluster class

@@
 
-By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table 1.
+By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table \ref{counts}.
 
@@
 \end{tabular}
+\label{counts}
 \end{table}
@@
 
-Applying the score to our hand-classified clusters shows us that this score does separate between template and non-template word.
-(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.)
-
-N lines: 3496074
-N clusters: 1151620
-N identical clusters: 666212
-N template clusters: 55430
-N other clusters: 20745
-N other pair clusters: 407963
-N species clusters: 1270
-
-N lines: 3496074
-N clusters: 1151620
-N identical clusters: 666212
-N template clusters: 244660
-N template sentences: 1116932
-N other clusters: 20745
-N other pair clusters: 218840
-N species clusters: 1163
-^C
+Applying the score to our hand-classified clusters shows us that this score does separate between template and non-template clusters.
+(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.) See Figure \ref{heuristic}.
 
 After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
-The template clusters contain 1,116,932, and the non-template
+The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196.
 

### 2013-11-03 src/main/wikiduper/analysis/TemplateClusters.java

@@ -8,6 +8,7 @@ import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.HashSet;
 import java.util.Iterator;
+import java.util.Set;
 import java.util.TreeSet;
 import java.util.regex.Matcher;
 import java.util.regex.Pattern;
@@ -516,7 +517,7 @@ public class TemplateClusters extends Configured implements Tool {
         return true;
     }
 
-    private void getClusterWordCounts(TreeSet<String> clustersentences,
+    private static void getClusterWordCounts(Set<String> clustersentences,
             HashMap<String, Integer> clusterwordct, ArrayList<HashSet<String>> sentencewordmap) {
         
         Iterator<String> clusterit = clustersentences.iterator();
@@ -543,10 +544,20 @@ public class TemplateClusters extends Configured implements Tool {
             sentencewordmap.add(sentencewordset);
         }
         
+        
     }
 
+    public static double scoreCluster(Set<String> clustersentences){
+        double score = 0;
+        HashMap<String,Integer> clusterwordct = new HashMap<String,Integer>();
+        ArrayList<HashSet<String>> sentencewordmap = new ArrayList<HashSet<String>>();
+        getClusterWordCounts(clustersentences, clusterwordct, sentencewordmap);
+        score = scoreClusterWords(clusterwordct,sentencewordmap,clustersentences.size());
+        return score;
+    }
+    
     // Some Java 6 -> 7 incompatibility issues here
-    Pattern propernoun = Pattern.compile("\\p{Lu}(\\w|\\p{Lu}|-|—)+('s)?"); //, Pattern.UNICODE_CHARACTER_CLASS);
+    static Pattern propernoun = Pattern.compile("\\p{Lu}(\\w|\\p{Lu}|-|—)+('s)?"); //, Pattern.UNICODE_CHARACTER_CLASS);
     private double scoreClusterWordsAlt(HashMap<String, Integer> clusterwordct, ArrayList<HashSet<String>> sentencewordmap, int nSentenceUnique, int nTitleSentenceUnique, 
             int clusterid, SequenceFile.Writer scoresWriter, int isTemplate, int isSpecies) throws IOException{
         // TODO Auto-generated method stub
@@ -630,7 +641,7 @@ public class TemplateClusters extends Configured implements Tool {
     }
 
     
-    private double scoreClusterWords(HashMap<String, Integer> clusterwordct, ArrayList<HashSet<String>> sentencewordmap, int nSentenceUnique, int nTitleSentenceUnique, 
[…]

### 2013-11-03 src/main/wikiduper/analysis/HistogramClusters.java
Updated classes to represent article/sentence as PairOfStrings

@@ -31,6 +31,8 @@ import org.apache.hadoop.util.Tool;
 import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
 
+import edu.umd.cloud9.io.pair.PairOfStrings;
+
 
 import wikiduper.application.MergeClusters;
 
@@ -125,7 +127,7 @@ public class HistogramClusters extends Configured implements Tool {
         long clustcurr = -1;
         int maxclustersize = 0;
         //Pattern linepat = Pattern.compile("^([^\t]+)\t(.*)$");
-        Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
+        //Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
 
         try {
         FileSystem fs = FileSystem.get(conf);
@@ -139,52 +141,51 @@ public class HistogramClusters extends Configured implements Tool {
             SequenceFile.Reader reader;
             reader = new SequenceFile.Reader(conf, SequenceFile.Reader.stream(in));
             LongWritable clusterid = new LongWritable();
-            Text articlesentence = new Text();
+            PairOfStrings articlesentence = new PairOfStrings();
             while(reader.next(clusterid, articlesentence)){
                 String linetext = articlesentence.toString().replace("\n", " ");
-                Matcher m = linepat.matcher(linetext);
+                //Matcher m = linepat.matcher(linetext);
                 String title = "";
                 String sentence = "";
-                if(m.matches()){
-                    title = m.group(1);
-                    sentence = m.group(2);
+                title = articlesentence.getLeftElement();
+                sentence = articlesentence.getRightElement();
 
-                    if(clustcurr == -1){
-                        clustcurr = clusterid.get();  
-                    }
+                if(clustcurr == -1){
+                    clustcurr = clusterid.get();  
+                }
                 
-                    if(!(clustcurr == clusterid.get())){
-                        if(clusterct % 10000 == 0) System.err.println("clusterct = " + clusterct);
+                if(!(clustcurr == clusterid.get())){
+                    if(clusterct % 10000 == 0) System.err.println("clusterct = " + clusterct);
 
-                        // Once we've found a new cluster Update each histogram
-                        int size = cluster.size();
-                        if(size > maxclustersize){
-                            maxclustersize = size;
-                        }
-                        if(size > thresh){
-                            bigclusterlinect+=size;
-                        }else{
-                            smallclusterlinect+=size;
[…]

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -6,6 +6,7 @@ import java.util.Collection;
 import java.util.HashMap;
 import java.util.Iterator;
 import java.util.Map;
+import java.util.regex.Pattern;
 
 import org.apache.commons.cli.CommandLine;
 import org.apache.commons.cli.CommandLineParser;
@@ -36,6 +37,9 @@ import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
 import org.apache.pig.parser.AliasMasker.keyvalue_return;
 
+import wikiduper.utils.DocSentence;
+import wikiduper.utils.Signature;
+
 import cern.colt.Arrays;
 import edu.umd.cloud9.io.array.ArrayListOfLongsWritable;
 import edu.umd.cloud9.io.array.ArrayListWritable;
@@ -48,13 +52,13 @@ import edu.umd.cloud9.util.fd.Object2IntFrequencyDistributionEntry;
 public class SentenceSimilarityCount extends Configured implements Tool {
     private static final Logger LOG = Logger.getLogger(SentenceSimilarityCount.class);
 
-
-    private static class MyMapper extends Mapper<ArrayListOfLongsWritable, ArrayListWritable<PairOfStringInt>, IntWritable, PairOfInts> {
+    Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
+    private static class MyMapper extends Mapper<Signature, DocSentence, IntWritable, PairOfInts> {
         private static final IntWritable KEY = new IntWritable();
         private static final PairOfInts VALUE = new PairOfInts();
 
         @Override
-        public void map(ArrayListOfLongsWritable key, ArrayListWritable<PairOfStringInt> sentences, Context context)
+        public void map(Signature key, DocSentence docsentence, Context context)
                 throws IOException, InterruptedException {
 
             //System.out.println(sentences.toString());

### 2013-11-03 src/main/wikiduper/analysis/TemplateClusters.java

@@ -36,6 +36,7 @@ import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
 
 import edu.umd.cloud9.io.array.ArrayListOfIntsWritable;
+import edu.umd.cloud9.io.pair.PairOfStrings;
 
 
 import wikiduper.application.MergeClusters;
@@ -167,7 +168,7 @@ public class TemplateClusters extends Configured implements Tool {
         long clustcurr = -1;
         int maxclustersize = 0;
         //Pattern linepat = Pattern.compile("^([^\t]+)\t(.*)$");
-        Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
+        //Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
         
         int templateCt = 0;
         int templateSentencesCt = 0;
@@ -210,106 +211,99 @@ public class TemplateClusters extends Configured implements Tool {
                 FSDataInputStream in = fs.open(filestatus.getPath());
                 SequenceFile.Reader reader = new SequenceFile.Reader(conf, SequenceFile.Reader.stream(in));
                 clusterid = new LongWritable();
-                Text articlesentence = new Text();
+                PairOfStrings articlesentence = new PairOfStrings();
             
             while(reader.next(clusterid, articlesentence)){
                 String linetext = articlesentence.toString()
                         .replace("\n", " ")
                         .replaceAll(" ?\\[?http\\S+", "");
-                Matcher m = linepat.matcher(linetext);
                 String title = "";
                 String sentence = "";
-                if(m.matches()){
-                    title = m.group(1);
-                    sentence = m.group(2);
+                title = articlesentence.getLeftElement();
+                sentence = articlesentence.getRightElement();
 
-                    if(clustcurr == -1){
-                        clustcurr = clusterid.get();  
-                    }
-                    //if(clusterct > 197000){
-                      //  System.out.println("articlesentence " + articlesentence.toString());
-                        //System.out.println("sentence = " + title + " " + sentence);
-                    //}
+                if(clustcurr == -1){
+                    clustcurr = clusterid.get();  
+                }
                     
-                    if(!(clustcurr == clusterid.get())){
-                        if(clusterct % 10000 == 0) System.err.println("clusterct = " + clusterct);
-                        // Once we've found a new cluster Update each histogram
-                        int size = cluster.size();
-                        if(size > maxclustersize){
[…]

### 2013-11-03 src/main/wikiduper/application/GetSentenceClusters.java

@@ -59,6 +59,7 @@ import wikiduper.wikipedia.WikipediaPage;
 import edu.umd.cloud9.io.array.ArrayListWritable;
 import edu.umd.cloud9.io.pair.PairOfLongString;
 import edu.umd.cloud9.io.pair.PairOfLongs;
+import edu.umd.cloud9.io.pair.PairOfStrings;
 
 public class GetSentenceClusters extends Configured implements Tool {
     private static final Logger LOG = Logger.getLogger(GetSentenceClusters.class);
@@ -74,7 +75,7 @@ public class GetSentenceClusters extends Configured implements Tool {
      *
      */
     private static class ClusterMapper extends MapReduceBase implements
-    Mapper<IntWritable, WikipediaPage, LongWritable, Text> {
+    Mapper<IntWritable, WikipediaPage, LongWritable, PairOfStrings> {
     //Mapper<LongWritable, WikipediaPage, IntWritable, Text> {
         
         // Map from docid -> sentence number -> cluster number
@@ -82,7 +83,7 @@ public class GetSentenceClusters extends Configured implements Tool {
         
         // The document-sentence identifier
         static final LongWritable CLUSTER = new LongWritable();
-        static final Text TITLESENTENCE = new Text();
+        static final PairOfStrings TITLESENTENCE = new PairOfStrings();
         
         //Adapted from http://stackoverflow.com/questions/5553410/regular-expression-match-a-sentence
         static final Pattern sentenceregex = Pattern.compile(
@@ -102,7 +103,7 @@ public class GetSentenceClusters extends Configured implements Tool {
 
         public static WikiClean cleaner;
 
-        public void map(IntWritable key, WikipediaPage p, OutputCollector<LongWritable, Text> output,
+        public void map(IntWritable key, WikipediaPage p, OutputCollector<LongWritable, PairOfStrings> output,
                 Reporter reporter) throws IOException {
           //public void map(LongWritable key, WikipediaPage p, OutputCollector<IntWritable, Text> output,
             //        Reporter reporter) throws IOException {
@@ -135,7 +136,7 @@ public class GetSentenceClusters extends Configured implements Tool {
                 String sentence = m.group(1);
                 if(sentMap.containsKey(sentencect)){
                     long clust = sentMap.get(sentencect);
-                    TITLESENTENCE.set(p.getTitle() + "\t" + sentence);
+                    TITLESENTENCE.set(p.getTitle(),sentence);
[…]

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
undo changes to sentencesimilaritycount

@@ -6,7 +6,6 @@ import java.util.Collection;
 import java.util.HashMap;
 import java.util.Iterator;
 import java.util.Map;
-import java.util.regex.Pattern;
 
 import org.apache.commons.cli.CommandLine;
 import org.apache.commons.cli.CommandLineParser;
@@ -37,9 +36,6 @@ import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
 import org.apache.pig.parser.AliasMasker.keyvalue_return;
 
-import wikiduper.utils.DocSentence;
-import wikiduper.utils.Signature;
-
 import cern.colt.Arrays;
 import edu.umd.cloud9.io.array.ArrayListOfLongsWritable;
 import edu.umd.cloud9.io.array.ArrayListWritable;
@@ -52,13 +48,13 @@ import edu.umd.cloud9.util.fd.Object2IntFrequencyDistributionEntry;
 public class SentenceSimilarityCount extends Configured implements Tool {
     private static final Logger LOG = Logger.getLogger(SentenceSimilarityCount.class);
 
-    Pattern linepat = Pattern.compile("^([^\t]+)\t((?>\\P{M}\\p{M}*)+)$");
-    private static class MyMapper extends Mapper<Signature, DocSentence, IntWritable, PairOfInts> {
+
+    private static class MyMapper extends Mapper<ArrayListOfLongsWritable, ArrayListWritable<PairOfStringInt>, IntWritable, PairOfInts> {
         private static final IntWritable KEY = new IntWritable();
         private static final PairOfInts VALUE = new PairOfInts();
 
         @Override
-        public void map(Signature key, DocSentence docsentence, Context context)
+        public void map(ArrayListOfLongsWritable key, ArrayListWritable<PairOfStringInt> sentences, Context context)
                 throws IOException, InterruptedException {
 
             //System.out.println(sentences.toString());

### 2013-11-03 src/main/wikiduper/analysis/TemplateClusters.java
Fixed bad initialization

@@ -341,7 +341,7 @@ public class TemplateClusters extends Configured implements Tool {
                 
                 linect++;
                 clusterid = new LongWritable();
-                articlesentence = new Text();
+                articlesentence = new PairOfStrings();
 
             }
             reader.close();

### 2013-11-03 article/article-draft.tex
Changed SentenceSimilarityCount to work with updated workflow and to remove templates using heuristic score

@@
 
-\section{Limitations of Our Approach}
-
-In addition to the aforementioned hash issue there are other limitations in our implementation and improvements that could be made.
-
-\emph{Data cleanliness} - The Cloud9 utilities that process Wikipedia code do some preprocessing of non-text elements from Wikipedia pages.
-However there is still improvements that could be made.
-Section headings can confuse our regular expression mapping, causing pieces of extraneous text to be appended to sentences.
-Parsing page text with a better understanding of how Wikipedia articles are structured could improve our input data.
-Additionally, keeping track of the order in which sentences occur on a page could improve analysis.
-For example, references and external links are typically found at the bottom of a Wikipeda page.
-More carefully filtering text based on sentence depth could improve results.
-
-\emph{Sentence matching} - Since Wikipedia data is not chunked by sentence, we rely on regular expression matching to break up input text into sentences.
-Since sentences have recursive structure, our regular expression can lead to stack overflow exceptions from the underlying recursive pattern match search.
-Setting bounds on the sentence structure nesting could provide more reliable results.
-The encyclopedic style of Wikipedia may lend itself to simpler sentence structures that don't require a general purpose sentence matching algorithm.
-
-\emph{Large clusters} - Since we rely on a connected component analysis to compute the final sentence clusters, our large clusters can be a bottleneck.
-Unfortunately, the Wikipedia data does contain large clusters of similar sentences (see the discussion of templatification below).
-Since our initial experimental results suggest that more interesting clusters (for example, sentence clusters representing copied data with factual errors) are much smaller (on the order of 2 or 3 sentences per cluster), we set a limit on maximum bucket size and only consider the first $n$ sentences in any bucket up to that limit.
-Setting a limit on cluster size helps ensure more predictable runtime and discards large portions of relatively uninteresting clusters, making output data more manageable.
-
-\emph{Non-determinism} - Our current implementation of Minhash suffers from a yet unidentified source of non-determinism.
-This affects the number of output records produced from the Minhashing stage of our implementation from one run to the next and has unknown effects on output quality.
-
 \section{Conclusion and Future Work}

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -1,11 +1,8 @@
 package wikiduper.analysis;
 
 import java.io.IOException;
-import java.util.ArrayList;
-import java.util.Collection;
-import java.util.HashMap;
+import java.util.HashSet;
 import java.util.Iterator;
-import java.util.Map;
 
 import org.apache.commons.cli.CommandLine;
 import org.apache.commons.cli.CommandLineParser;
@@ -18,7 +15,6 @@ import org.apache.hadoop.conf.Configuration;
 import org.apache.hadoop.conf.Configured;
 import org.apache.hadoop.fs.FileSystem;
 import org.apache.hadoop.fs.Path;
-import org.apache.hadoop.io.BytesWritable;
 import org.apache.hadoop.io.IntWritable;
 import org.apache.hadoop.io.LongWritable;
 import org.apache.hadoop.io.Text;
@@ -27,114 +23,93 @@ import org.apache.hadoop.mapreduce.Mapper;
 import org.apache.hadoop.mapreduce.Reducer;
 import org.apache.hadoop.mapreduce.lib.input.FileInputFormat;
 import org.apache.hadoop.mapreduce.lib.input.SequenceFileInputFormat;
-import org.apache.hadoop.mapreduce.lib.input.TextInputFormat;
 import org.apache.hadoop.mapreduce.lib.output.FileOutputFormat;
 import org.apache.hadoop.mapreduce.lib.output.SequenceFileOutputFormat;
-import org.apache.hadoop.mapreduce.lib.output.TextOutputFormat;
 import org.apache.hadoop.util.Tool;
 import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
-import org.apache.pig.parser.AliasMasker.keyvalue_return;
 
 import cern.colt.Arrays;
-import edu.umd.cloud9.io.array.ArrayListOfLongsWritable;
 import edu.umd.cloud9.io.array.ArrayListWritable;
-import edu.umd.cloud9.io.pair.PairOfInts;
-import edu.umd.cloud9.io.pair.PairOfStringInt;
-import edu.umd.cloud9.util.fd.Object2IntFrequencyDistribution;
-import edu.umd.cloud9.util.fd.Object2IntFrequencyDistributionEntry;
-
+import edu.umd.cloud9.io.pair.PairOfStrings;
 
 public class SentenceSimilarityCount extends Configured implements Tool {
     private static final Logger LOG = Logger.getLogger(SentenceSimilarityCount.class);
 
 
[…]

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Debugging job chaining errors

@@ -220,6 +220,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         LOG.info("Job Finished in " + (System.currentTimeMillis() - startTime) / 1000.0 + " seconds");
         
         // Job 2 
+        job = Job.getInstance(conf);
         FileOutputFormat.setOutputPath(job, new Path(inputPath));
         FileOutputFormat.setOutputPath(job, new Path(outputPath));
 

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Debugging job chaining errors

@@ -221,6 +221,10 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         
         // Job 2 
         job = Job.getInstance(conf);
+        job.setJobName("SentenceSimilarityCount");
+        job.setJarByClass(SentenceSimilarityCount.class);
+        job.setNumReduceTasks(reduceTasks);
+
         FileOutputFormat.setOutputPath(job, new Path(inputPath));
         FileOutputFormat.setOutputPath(job, new Path(outputPath));
 

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Debugging job chaining errors

@@ -221,11 +221,12 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         
         // Job 2 
         job = Job.getInstance(conf);
+        
         job.setJobName("SentenceSimilarityCount");
         job.setJarByClass(SentenceSimilarityCount.class);
         job.setNumReduceTasks(reduceTasks);
 
-        FileOutputFormat.setOutputPath(job, new Path(inputPath));
+        FileInputFormat.setInputPaths(job, new Path(tmpPath));
         FileOutputFormat.setOutputPath(job, new Path(outputPath));
 
         // set input/output format of the job

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Increasing default number of reducers

@@ -171,7 +171,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         String inputPath = cmdline.getOptionValue(INPUT);
         String outputPath = cmdline.getOptionValue(OUTPUT);
         String tmpPath = "tmppath";
-        int reduceTasks = cmdline.hasOption(NUM_REDUCERS) ? Integer.parseInt(cmdline.getOptionValue(NUM_REDUCERS)) : 6;
+        int reduceTasks = cmdline.hasOption(NUM_REDUCERS) ? Integer.parseInt(cmdline.getOptionValue(NUM_REDUCERS)) : 20;
         
 
         LOG.info("Tool: " + SentenceSimilarityCount.class.getSimpleName());

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Replaced threshold argument to sentence similarity counting code

@@ -18,6 +18,7 @@ import org.apache.hadoop.fs.Path;
 import org.apache.hadoop.io.IntWritable;
 import org.apache.hadoop.io.LongWritable;
 import org.apache.hadoop.io.Text;
+import org.apache.hadoop.mapred.JobConf;
 import org.apache.hadoop.mapreduce.Job;
 import org.apache.hadoop.mapreduce.Mapper;
 import org.apache.hadoop.mapreduce.Reducer;
@@ -71,7 +72,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static class MyMapper extends Mapper<LongWritable, ArrayListWritable<Text>, PairOfStrings, IntWritable> {
         private static final PairOfStrings KEY = new PairOfStrings();
         private static final IntWritable ONE = new IntWritable();
-
+        private static long threshold;
         @Override
         public void map(LongWritable key, ArrayListWritable<Text> doclist, Context context)
                 throws IOException, InterruptedException {
@@ -79,6 +80,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             //System.out.println(sentences.toString());
             Text doc1;
             Text doc2;
+            if(doclist.size() > threshold)
+                return;
             for (int i=0;i<doclist.size();i++){
                 doc1 = doclist.get(i);
                 for(int j=i+1;j<doclist.size();j++){
@@ -89,6 +92,11 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                     }
                 }
             }
+        }
+        
+        public void configure(JobConf job){
+            threshold = job.getLong("threshold",1000);            
+            
         }
     }
 
@@ -170,6 +178,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
 
         String inputPath = cmdline.getOptionValue(INPUT);
         String outputPath = cmdline.getOptionValue(OUTPUT);
+        long threshold = Long.valueOf(cmdline.getOptionValue(THRESHOLD));
         String tmpPath = "tmppath";
         int reduceTasks = cmdline.hasOption(NUM_REDUCERS) ? Integer.parseInt(cmdline.getOptionValue(NUM_REDUCERS)) : 20;
         
@@ -186,6 +195,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         job.setJarByClass(SentenceSimilarityCount.class);
         job.setNumReduceTasks(reduceTasks);
         
[…]

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Removed threshold argument to sentence similarity counting code

@@ -72,7 +72,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static class MyMapper extends Mapper<LongWritable, ArrayListWritable<Text>, PairOfStrings, IntWritable> {
         private static final PairOfStrings KEY = new PairOfStrings();
         private static final IntWritable ONE = new IntWritable();
-        private static long threshold;
+        //private static long threshold;
         @Override
         public void map(LongWritable key, ArrayListWritable<Text> doclist, Context context)
                 throws IOException, InterruptedException {
@@ -80,8 +80,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             //System.out.println(sentences.toString());
             Text doc1;
             Text doc2;
-            if(doclist.size() > threshold)
-                return;
+            //if(doclist.size() > threshold)
+              //  return;
             for (int i=0;i<doclist.size();i++){
                 doc1 = doclist.get(i);
                 for(int j=i+1;j<doclist.size();j++){
@@ -94,10 +94,10 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             }
         }
         
-        public void configure(JobConf job){
-            threshold = job.getLong("threshold",1000);            
+        //public void configure(JobConf job){
+          //  threshold = job.getLong("threshold",1000);            
             
-        }
+        //}
     }
 
     private static class MyReducer extends Reducer<PairOfStrings, IntWritable, PairOfStrings, IntWritable> {
@@ -113,7 +113,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             Iterator<IntWritable> iter = values.iterator();
             int sum = 0;
             while (iter.hasNext()) {
-                sum++;
+                sum+= iter.next().get();
             }
             SUM.set(sum);
             context.write(articlepair, SUM);
@@ -132,7 +132,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static final String INPUT = "input";
     private static final String OUTPUT = "output";
     private static final String NUM_REDUCERS = "numReducers";
-    private static final String THRESHOLD = "threshold";
+    //private static final String THRESHOLD = "threshold";
 
     /**
      * Runs this tool.
@@ -151,8 +151,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
[…]

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Removed threshold argument to sentence similarity counting code

@@ -41,6 +41,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static class ClusterReducer extends Reducer<LongWritable, PairOfStrings, LongWritable, ArrayListWritable<Text>> {
         private static final ArrayListWritable<Text> VALUE = new ArrayListWritable<Text>();
         private static final HashSet<String> clusterSentences = new HashSet<String>();
+        private static final HashSet<String> clusterDocs = new HashSet<String>();
         @Override
         public void reduce(LongWritable clusterID, Iterable<PairOfStrings> docs, Context context)
                 throws IOException, InterruptedException {
@@ -49,22 +50,28 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             // article denoted by wikiID
             VALUE.clear();
             clusterSentences.clear();
+            clusterDocs.clear();
             Iterator<PairOfStrings> iter = docs.iterator();
             PairOfStrings docsentence;
             while (iter.hasNext()) {
                 docsentence = iter.next();
                 String doc = docsentence.getLeftElement();
                 String sentence = docsentence.getRightElement();
-                Text docout = new Text();
                 clusterSentences.add(sentence);
-                docout.set(doc);
-                VALUE.add(docout);
-
+                clusterDocs.add(doc);
             }
             double score = TemplateClusters.scoreCluster(clusterSentences);
             if(score < .6){
+                for(String doc : clusterDocs){
+                    Text docout = new Text();
+                    docout.set(doc);
+                    VALUE.add(docout);
+                }
                 context.write(clusterID, VALUE);
             }
+
+
+
             
         }
     }
@@ -80,8 +87,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             //System.out.println(sentences.toString());
             Text doc1;
             Text doc2;
-            //if(doclist.size() > threshold)
-              //  return;
+            if(doclist.size() > 10000)
+                return;
             for (int i=0;i<doclist.size();i++){
                 doc1 = doclist.get(i);
                 for(int j=i+1;j<doclist.size();j++){

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Fixed missing value for summing

@@ -78,7 +78,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
    
     private static class MyMapper extends Mapper<LongWritable, ArrayListWritable<Text>, PairOfStrings, IntWritable> {
         private static final PairOfStrings KEY = new PairOfStrings();
-        private static final IntWritable ONE = new IntWritable();
+        private static final IntWritable ONE = new IntWritable(1);
         //private static long threshold;
         @Override
         public void map(LongWritable key, ArrayListWritable<Text> doclist, Context context)

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Added an extra job to sort by count

@@ -128,7 +128,16 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         }
    }
 
+    private static class FlipMapper extends Mapper<PairOfStrings, IntWritable, IntWritable, PairOfStrings> {
+        @Override
+        public void map(PairOfStrings docpair, IntWritable sum, Context context)
+                throws IOException, InterruptedException {
 
+            context.write(sum,  docpair);
+
+        }
+        
+    }
 
 
     /**
@@ -187,6 +196,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         String outputPath = cmdline.getOptionValue(OUTPUT);
         //long threshold = Long.valueOf(cmdline.getOptionValue(THRESHOLD));
         String tmpPath = "tmppath";
+        String tmpPath2 = "tmppath2";
         int reduceTasks = cmdline.hasOption(NUM_REDUCERS) ? Integer.parseInt(cmdline.getOptionValue(NUM_REDUCERS)) : 20;
         
 
@@ -239,12 +249,12 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         // Job 2 
         job = Job.getInstance(conf);
         
-        job.setJobName("SentenceSimilarityCount");
+        job.setJobName("SentenceSimilarityCount-2");
         job.setJarByClass(SentenceSimilarityCount.class);
         job.setNumReduceTasks(reduceTasks);
 
         FileInputFormat.setInputPaths(job, new Path(tmpPath));
-        FileOutputFormat.setOutputPath(job, new Path(outputPath));
+        FileOutputFormat.setOutputPath(job, new Path(tmpPath2));
 
         // set input/output format of the job
         job.setInputFormatClass(SequenceFileInputFormat.class);
@@ -263,13 +273,45 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         job.setCombinerClass(MyReducer.class);
         
         // Delete the output directory if it exists already.
-        outputDir = new Path(outputPath);
+        outputDir = new Path(tmpPath2);
         FileSystem.get(conf).delete(outputDir, true);
 
         startTime = System.currentTimeMillis();
         job.waitForCompletion(true);
         LOG.info("Job Finished in " + (System.currentTimeMillis() - startTime) / 1000.0 + " seconds");
         
+        // Job 3
+        job = Job.getInstance(conf);
+        
+        job.setJobName("SentenceSimilarityCount-3");
[…]

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Fixed key value config

@@ -296,8 +296,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         //job.setOutputFormatClass(TextOutputFormat.class);
 
         // set output key/value data types
-        job.setMapOutputKeyClass(PairOfStrings.class);
-        job.setMapOutputValueClass(IntWritable.class);
+        job.setMapOutputKeyClass(IntWritable.class);
+        job.setMapOutputValueClass(PairOfStrings.class);
         job.setOutputKeyClass(IntWritable.class);
         job.setOutputValueClass(PairOfStrings.class);
 

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Fixed key value config

@@ -303,7 +303,6 @@ public class SentenceSimilarityCount extends Configured implements Tool {
 
         // define Mapper and Reducer
         job.setMapperClass(MyMapper.class);
-        job.setReducerClass(null);
         
         // Delete the output directory if it exists already.
         outputDir = new Path(outputPath);

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Corrected mapper class

@@ -302,7 +302,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         job.setOutputValueClass(PairOfStrings.class);
 
         // define Mapper and Reducer
-        job.setMapperClass(MyMapper.class);
+        job.setMapperClass(FlipMapper.class);
         
         // Delete the output directory if it exists already.
         outputDir = new Path(outputPath);

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Filtering out one counts

@@ -122,8 +122,10 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             while (iter.hasNext()) {
                 sum+= iter.next().get();
             }
-            SUM.set(sum);
-            context.write(articlepair, SUM);
+            if(sum > 1){
+                SUM.set(sum);
+                context.write(articlepair, SUM);
+            }
 
         }
    }
@@ -285,7 +287,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         
         job.setJobName("SentenceSimilarityCount-3");
         job.setJarByClass(SentenceSimilarityCount.class);
-        job.setNumReduceTasks(reduceTasks);
+        job.setNumReduceTasks(1);
 
         FileInputFormat.setInputPaths(job, new Path(tmpPath2));
         FileOutputFormat.setOutputPath(job, new Path(outputPath));

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Filtering out one counts

@@ -122,10 +122,9 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             while (iter.hasNext()) {
                 sum+= iter.next().get();
             }
-            if(sum > 1){
-                SUM.set(sum);
-                context.write(articlepair, SUM);
-            }
+            
+            SUM.set(sum);
+            context.write(articlepair, SUM);
 
         }
    }
@@ -134,8 +133,9 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         @Override
         public void map(PairOfStrings docpair, IntWritable sum, Context context)
                 throws IOException, InterruptedException {
-
-            context.write(sum,  docpair);
+            if(sum.get() > 1){
+                context.write(sum,  docpair);
+            }
 
         }
         

### 2013-11-03 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Filtering out identical clusters

@@ -60,6 +60,9 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 clusterSentences.add(sentence);
                 clusterDocs.add(doc);
             }
+            if(clusterSentences.size() == 1){
+                return;
+            }
             double score = TemplateClusters.scoreCluster(clusterSentences);
             if(score < .6){
                 for(String doc : clusterDocs){

### 2013-11-04 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Debugging sentence similarity code

@@ -64,6 +64,9 @@ public class SentenceSimilarityCount extends Configured implements Tool {
               //  return;
             //}
             double score = TemplateClusters.scoreCluster(clusterSentences);
+            if(clusterID.get() == 22040){
+                System.out.println(score + "\t" + clusterSentences);
+            }
             //if(score < .6){
                 for(String doc : clusterDocs){
                     Text docout = new Text();

### 2013-11-04 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Debugging sentence similarity code

@@ -40,7 +40,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
 
     private static class ClusterReducer extends Reducer<LongWritable, PairOfStrings, LongWritable, ArrayListWritable<Text>> {
         private static final ArrayListWritable<Text> VALUE = new ArrayListWritable<Text>();
-        private static final HashSet<String> clusterSentences = new HashSet<String>();
+        private static final HashSet<String> clusterTitleSentences = new HashSet<String>();
         private static final HashSet<String> clusterDocs = new HashSet<String>();
         @Override
         public void reduce(LongWritable clusterID, Iterable<PairOfStrings> docs, Context context)
@@ -49,7 +49,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             // iterate through all sentences from other wiki articles that have hashed to the same value as one of the sentences in the wiki
             // article denoted by wikiID
             VALUE.clear();
-            clusterSentences.clear();
+            clusterTitleSentences.clear();
             clusterDocs.clear();
             Iterator<PairOfStrings> iter = docs.iterator();
             PairOfStrings docsentence;
@@ -57,15 +57,15 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 docsentence = iter.next();
                 String doc = docsentence.getLeftElement();
                 String sentence = docsentence.getRightElement();
-                clusterSentences.add(sentence);
+                clusterTitleSentences.add(doc + "\t" + sentence);
                 clusterDocs.add(doc);
             }
             //if(clusterSentences.size() == 1){
               //  return;
             //}
-            double score = TemplateClusters.scoreCluster(clusterSentences);
+            double score = TemplateClusters.scoreCluster(clusterTitleSentences);
             if(clusterID.get() == 22040){
-                System.out.println(score + "\t" + clusterSentences);
+                System.out.println(score + "\t" + clusterTitleSentences);
             }
             //if(score < .6){
                 for(String doc : clusterDocs){

### 2013-11-04 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Fixed template scoring and added back in filtering to article similarity code

@@ -64,17 +64,15 @@ public class SentenceSimilarityCount extends Configured implements Tool {
               //  return;
             //}
             double score = TemplateClusters.scoreCluster(clusterTitleSentences);
-            if(clusterID.get() == 22040){
-                System.out.println(score + "\t" + clusterTitleSentences);
-            }
-            //if(score < .6){
+
+            if(score < .6){
                 for(String doc : clusterDocs){
                     Text docout = new Text();
                     docout.set(doc);
                     VALUE.add(docout);
                 }
                 context.write(clusterID, VALUE);
-            //}
+            }
 
 
 

### 2013-11-04 article/article-draft.tex
Added back in code to filter identical clusters

@@
     \textbf{Article ID} & \textbf{Title} \\ \hline
-    21986867 & 2000 New Year Honours \\ \hline
-    21986897 & 1999 New Year Honours \\ \hline
-    3951586 & Instruments of the United Kingdom, 1994 \\ \hline
-    3951664 & Instruments of the United Kingdom, 1995 \\ \hline
-    1903966 & Management of baldness \\ \hline
-    38088660 & Management of androgenic alopecia \\ \hline
-    1503105 & Jayne Torvill \\ \hline
-    1503115 & Christopher Dean \\ \hline
-    184843 & Henry VI, Part 1 \\ \hline
-    184846 & Henry VI, Part 2 \\ \hline
-    184847 & Henry VI, Part 3 \\ \hline
-    10701462 & List of birds of Zambia \\ \hline
-    10930255 & List of birds of Zimbabwe \\ \hline
-    10930111 & List of birds of Mozambique \\ \hline
-    48711 & Oregon Trail \\ \hline
-    31518964 & History of the Oregon Trail \\
+[Early life and career of Marcus Aurelius, Marcus Aurelius]
+[Private equity in the 2000s, History of private equity and venture capital]
+[List of ethnic cleansings, Ethnic cleansing]
+[Route of the Oregon Trail, Oregon Trail]
+[English literature, British literature]
+[Culture of the United States, Society of the United States]
+[18th-century history of Germany, History of Germany]
+[Insect morphology, Insect wing]
+[Nutritional neuroscience, Nutrition and cognition]
+[Philippine general election, 2004, Philippine presidential election, 2004]
+[History of the Dallas Mavericks, Dallas Mavericks]
+[May Bukas Pa, List of May Bukas Pa episodes]
+[Individualist anarchism in the United States, Anarchism in the United States]
+[Native Americans in the United States, Native American cultures in the United States]
+[Hockey stick controversy, Hockey stick graph]
+[Filioque, History of the Filioque controversy]
+[Vancouver Canucks, History of the Vancouver Canucks]
+[Silvio Berlusconi, Controversies surrounding Silvio Berlusconi]
+[2007 suicide bombings in Iraq, List of terrorist incidents in Iraq in 2007]
+[List of Canadian tornadoes and tornado outbreaks, List of 21st-century Canadian tornadoes and tornado outbreaks]
+[Scotland in the modern era, History of Scotland]
+[Reliability of Wikipedia, Criticism of Wikipedia]
+[Imperial Roman army, Auxiliaries (Roman military)]
+[Libertarian socialism, Libertarian Marxism]
+[Arts in Australia, Culture of Australia]
+[Canti (Leopardi), Giacomo Leopardi]
+[Culture of England, Religion in England]
+[Government of Mahmoud Ahmadinejad (2005–present), Foreign policy of Mahmoud Ahmadinejad]
+[Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages]
+[Go Nagai bibliography, Go Nagai]
+[Galvatron, Megatron]
+[Wakfu (TV series), Wakfu]
+[Isabela, Basilan, History of Basilan]
+[List of Prison Break recurring characters, List of Prison Break minor characters]
+[Interracial marriage, Miscegenation]
+[List of Shakespearean characters (L–Z), List of Shakespearean characters (A–K)]
+[Fascism and ideology, Fascism]
+[Anarchism, History of anarchism]
+[Ethnic groups in Ecuador, Ecuadorian people]
+[History of painting, Western painting, 20th-century Western painting]
+[Precipitation, Rain]
+[Megaupload legal case, Megaupload]
+[Anti-spam techniques, Anti-spam techniques (users)]
+[History of the Detroit Tigers, Detroit Tigers]
+[Yuko Kavaguti, Alexander Smirnov (figure skater)]
+[San Francisco Giants, History of the San Francisco Giants]
+[List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)]
+[List of Reaper characters, Reaper (TV series)]
+[Port of Tianjin operations and logistics, Port of Tianjin]
+[Management of androgenic alopecia, Management of baldness]
+[Legion of Super-Heroes, Legion of Super-Heroes (1958 team)]
+[American rock, Rock music]
+[One-Day Internationals in England in 2005, Test matches in England in 2005, Australian cricket team in England in 2005]
+[Swedes, Sweden]
+[Controversies surrounding the European sovereign-debt crisis, Policy reactions to the European sovereign-debt crisis, European sovereign-debt crisis, Economic reforms and recovery proposals regarding the European sovereign-debt crisis]
+[List of Irish Americans, List of Americans of Irish descent]
+[CIA leak scandal criminal investigation, Plame affair grand jury investigation]
+[Medway watermills (lower tributaries), River Len]
+[2000 New Year Honours, 1999 New Year Honours]
+[Kingdom of Greece, History of modern Greece]
+[List of Russian people, List of Russian scientists]
+
+    %% 21986867 & 2000 New Year Honours \\ \hline
+    %% 21986897 & 1999 New Year Honours \\ \hline
+    %% 3951586 & Instruments of the United Kingdom, 1994 \\ \hline
+    %% 3951664 & Instruments of the United Kingdom, 1995 \\ \hline
+    %% 1903966 & Management of baldness \\ \hline
+    %% 38088660 & Management of androgenic alopecia \\ \hline
+    %% 1503105 & Jayne Torvill \\ \hline
+    %% 1503115 & Christopher Dean \\ \hline
+    %% 184843 & Henry VI, Part 1 \\ \hline
+    %% 184846 & Henry VI, Part 2 \\ \hline
+    %% 184847 & Henry VI, Part 3 \\ \hline
+    %% 10701462 & List of birds of Zambia \\ \hline
+    %% 10930255 & List of birds of Zimbabwe \\ \hline
+    %% 10930111 & List of birds of Mozambique \\ \hline
+    %% 48711 & Oregon Trail \\ \hline
+    %% 31518964 & History of the Oregon Trail \\
     \hline

### 2013-11-04 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -41,6 +41,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static class ClusterReducer extends Reducer<LongWritable, PairOfStrings, LongWritable, ArrayListWritable<Text>> {
         private static final ArrayListWritable<Text> VALUE = new ArrayListWritable<Text>();
         private static final HashSet<String> clusterTitleSentences = new HashSet<String>();
+        private static final HashSet<String> clusterSentences = new HashSet<String>();
         private static final HashSet<String> clusterDocs = new HashSet<String>();
         @Override
         public void reduce(LongWritable clusterID, Iterable<PairOfStrings> docs, Context context)
@@ -50,6 +51,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             // article denoted by wikiID
             VALUE.clear();
             clusterTitleSentences.clear();
+            clusterSentences.clear();
             clusterDocs.clear();
             Iterator<PairOfStrings> iter = docs.iterator();
             PairOfStrings docsentence;
@@ -57,12 +59,13 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 docsentence = iter.next();
                 String doc = docsentence.getLeftElement();
                 String sentence = docsentence.getRightElement();
+                clusterSentences.add(sentence);
                 clusterTitleSentences.add(doc + "\t" + sentence);
                 clusterDocs.add(doc);
             }
-            //if(clusterSentences.size() == 1){
-              //  return;
-            //}
+            if(clusterSentences.size() == 1){
+                return;
+            }
             double score = TemplateClusters.scoreCluster(clusterTitleSentences);
 
             if(score < .6){

### 2013-11-04 article/article-draft.tex
Removing cluster size limit

--- 2013-11-03 article/article-draft.tex
@@
 \usepackage{natbib}
-
+\usepackage[utf8]{inputenc}
 \begin{document}
@@
 Based on our preliminary analysis, templatification tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics.
-For example, of the top 10 pairs of articles with the highest similarity count, one article pair was the articles titled ''List of birds of Zambia'' and ''List of birds of Tanzania''.
-With both countries sharing the same geographic region, it is not unexpected that their respective wikipedia articles on the countrys' bird species would be highly comparable.
+For example, the articles ''List of birds of Zambia'' and ''List of birds of Tanzania'' share a large number of templated sentences.
+With both countries sharing the same geographic region, it is not unexpected that their respective Wikipedia articles on the countrys' bird species would be highly comparable.
 For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature.
 Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences.
-Overall, we found $\approx 6500$ wikipedia article pairs that had a similarity count greater than $50$.
+Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.
 
@@
 \caption{Top 10 Article Pair Titles}
-\begin{tabular}{| l | c |}
+{\small
+\begin{tabular}{| l |}
     \hline
-    \textbf{Article ID} & \textbf{Title} \\ \hline
-    21986867 & 2000 New Year Honours \\ \hline
-    21986897 & 1999 New Year Honours \\ \hline
-    3951586 & Instruments of the United Kingdom, 1994 \\ \hline
-    3951664 & Instruments of the United Kingdom, 1995 \\ \hline
-    1903966 & Management of baldness \\ \hline
-    38088660 & Management of androgenic alopecia \\ \hline
-    1503105 & Jayne Torvill \\ \hline
-    1503115 & Christopher Dean \\ \hline
-    184843 & Henry VI, Part 1 \\ \hline
-    184846 & Henry VI, Part 2 \\ \hline
-    184847 & Henry VI, Part 3 \\ \hline
-    10701462 & List of birds of Zambia \\ \hline
-    10930255 & List of birds of Zimbabwe \\ \hline
-    10930111 & List of birds of Mozambique \\ \hline
-    48711 & Oregon Trail \\ \hline
-    31518964 & History of the Oregon Trail \\
+\{Private equity in the 2000s, History of private equity and venture capital, Private equity in the 1980s\} \\
+\{List of ethnic cleansings, Ethnic cleansing\} \\
+\{Route of the Oregon Trail, Oregon Trail\} \\
+\{English literature, British literature\} \\
+\{Portia schultzi, Portia labiata, Portia fimbriata\} \\
+\{Lesbian American history, List of lesbian, gay, bisexual, or transgender firsts by year\} \\
+\{Lists of British inventions, List of English inventions and discoveries\} \\
+\{1981 in baseball, 1981 Major League Baseball season\} \\
+\{Minority Report (film), Themes in Minority Report\} \\
+\{What Is History?, E. H. Carr\} \\
+\{Individualist anarchism in Europe, Individualist anarchism in the United States, Individualist anarchism, Anarchism in the United States\} \\
+\{Kingdom of Scotland, Scotland in the Early Modern Era\} \\
+\{Decline of Greco-Roman polytheism, Christian persecution of paganism after Theodosius I until the fall of the Roman Empire\} \\
+\{Anarchist schools of thought, Libertarian socialism, Anarchist communism, Anarchism, History of anarchism, Libertarian Marxism\} \\
+\{Brill Tramway, Quainton Road railway station\} \\
+\{History of the Roman Empire, Byzantine Empire, History of the Byzantine Empire\} \\
+\{List of American state and local politicians convicted of crimes, List of state and local political scandals in the United States\} \\
+\{Filioque, History of the Filioque controversy\} \\
+\{1960 Major League Baseball season, 1960 in baseball\} \\
+\{Domitian, Flavian dynasty\} \\
+\{Military history of Australia during World War II, Australian Army during World War II\} \\
+\{Kuomintang, History of the Kuomintang\} \\
+\{Interracial marriage, Miscegenation, Eurasian (mixed ancestry)\} \\
+\{Scotland in the modern era, History of Scotland\} \\
+\{History of California, Maritime history of California\} \\
+\{Outline of project management, Glossary of project management\} \\
+\{Wigan Warriors, History of Wigan Warriors\} \\
+\{List of American federal politicians convicted of crimes, List of federal political scandals in the United States\} \\
+\{Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages\} \\
+\{Galvatron, Megatron\} \\
+\{Metropolitan Police role in the news media phone hacking scandal, News media phone hacking scandal\} \\
+\{List of Shakespearean characters (L-Z), List of Shakespearean characters (A-K), List of historical figures dramatised by Shakespeare\} \\
+\{Fetal alcohol spectrum disorder, Fetal alcohol syndrome\} \\
+\{List of marine bony fishes of South Africa, List of marine animals of the Cape Peninsula and False Bay\} \\
+\{History of painting, Western painting, 20th-century Western painting\} \\
+\{Timeline of the 2007 Burmese anti-government protests, 2007 Burmese anti-government protests\} \\
+\{Precipitation, Rain\} \\
+\{List of Puerto Ricans, List of Puerto Rican military personnel\} \\
+\{Glossary of basketball terms, Outline of basketball\} \\
+\{Hannibal, Conquests of Hannibal\} \\
+\{Bogotá, History of Bogotá\} \\
+\{Pseudotsuga menziesii var. menziesii, Douglas fir\} \\
+\{History of the East-West Schism, East-West Schism\} \\
+\{List of attacks in Lebanon, Lebanon bombings and assassinations (2004-present)\} \\
+\{Zen, Chinese Chán\} \\
+\{List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)\} \\
+\{1991 Major League Baseball season, 1991 in baseball\} \\
+\{American rock, Rock music\} \\
+\{Test matches in England in 2005, Australian cricket team in England in 2005\} \\
+\{Swedes, Sweden\} \\
+\{Glossary of robotics, Outline of robotics\} \\
+\{CIA leak scandal criminal investigation, Plame affair grand jury investigation\} \\
+\{History of Australia since 1945, History of Australia\} \\
+\{List of Russian people, List of Russian scientists\} \\
+    %% 21986867 & 2000 New Year Honours \\ \hline
+    %% 21986897 & 1999 New Year Honours \\ \hline
+    %% 3951586 & Instruments of the United Kingdom, 1994 \\ \hline
+    %% 3951664 & Instruments of the United Kingdom, 1995 \\ \hline
+    %% 1903966 & Management of baldness \\ \hline
+    %% 38088660 & Management of androgenic alopecia \\ \hline
+    %% 1503105 & Jayne Torvill \\ \hline
+    %% 1503115 & Christopher Dean \\ \hline
+    %% 184843 & Henry VI, Part 1 \\ \hline
+    %% 184846 & Henry VI, Part 2 \\ \hline
+    %% 184847 & Henry VI, Part 3 \\ \hline
+    %% 10701462 & List of birds of Zambia \\ \hline
+    %% 10930255 & List of birds of Zimbabwe \\ \hline
+    %% 10930111 & List of birds of Mozambique \\ \hline
+    %% 48711 & Oregon Trail \\ \hline
+    %% 31518964 & History of the Oregon Trail \\
     \hline
 \end{tabular}
+}
 \end{table}

### 2013-11-04 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -94,8 +94,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             //System.out.println(sentences.toString());
             Text doc1;
             Text doc2;
-            if(doclist.size() > 10000)
-                return;
+            //if(doclist.size() > 10000)
+              //  return;
             for (int i=0;i<doclist.size();i++){
                 doc1 = doclist.get(i);
                 for(int j=i+1;j<doclist.size();j++){

### 2013-11-11 article/article-draft.tex
Removed restrictions on sentence similarity counts

@@
 After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
-The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196.
+The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196 sentences.
 
@@
 
-Based on our preliminary analysis, templatification tends to occur most often between articles that maintain large lists of information related to the same general sub-theme of different topics.
-For example, the articles ''List of birds of Zambia'' and ''List of birds of Tanzania'' share a large number of templated sentences.
-With both countries sharing the same geographic region, it is not unexpected that their respective Wikipedia articles on the countrys' bird species would be highly comparable.
  For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature.

### 2013-11-11 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -63,19 +63,19 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 clusterTitleSentences.add(doc + "\t" + sentence);
                 clusterDocs.add(doc);
             }
-            if(clusterSentences.size() == 1){
-                return;
-            }
-            double score = TemplateClusters.scoreCluster(clusterTitleSentences);
+            //if(clusterSentences.size() == 1){
+              //  return;
+            //}
+    //        double score = TemplateClusters.scoreCluster(clusterTitleSentences);
 
-            if(score < .6){
+//            if(score < .6){
                 for(String doc : clusterDocs){
                     Text docout = new Text();
                     docout.set(doc);
                     VALUE.add(docout);
                 }
                 context.write(clusterID, VALUE);
-            }
+  //          }
 
 
 

### 2013-11-12 src/main/wikiduper/utils/junk/RemoveKeyLessThan.java
Adding utility for removing low key counts

@@ -1,0 +1,157 @@
+package wikiduper.utils.junk;
+
+import java.io.IOException;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.GnuParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.ParseException;
+import org.apache.hadoop.conf.Configuration;
+import org.apache.hadoop.conf.Configured;
+import org.apache.hadoop.fs.FileSystem;
+import org.apache.hadoop.fs.Path;
+import org.apache.hadoop.io.IntWritable;
+import org.apache.hadoop.mapreduce.Job;
+import org.apache.hadoop.mapreduce.Mapper;
+import org.apache.hadoop.mapreduce.lib.input.FileInputFormat;
+import org.apache.hadoop.mapreduce.lib.input.SequenceFileInputFormat;
+import org.apache.hadoop.mapreduce.lib.output.FileOutputFormat;
+import org.apache.hadoop.mapreduce.lib.output.SequenceFileOutputFormat;
+import org.apache.hadoop.util.Tool;
+import org.apache.hadoop.util.ToolRunner;
+import org.apache.log4j.Logger;
+
+import edu.umd.cloud9.io.pair.PairOfStrings;
+
+public class RemoveKeyLessThan extends Configured implements Tool {
+    private static final Logger LOG = Logger.getLogger(RemoveKeyLessThan.class);
+    public static int minsim = 2;
+    private static class MyMapper extends Mapper<IntWritable, PairOfStrings, IntWritable, PairOfStrings> {
+        @Override
+        public void map(IntWritable key, PairOfStrings value, Context context)
+                throws IOException, InterruptedException {
+            if(key.get() < minsim){
+                return;
+            }
+            context.write(key, value);
+        }
+        
+        @Override
+        public void setup(Context context){
+            minsim = context.getConfiguration().getInt("minsim", 2);
+        }
+    }
+
+    /**
+     * Creates an instance of this tool.
+     */
+    public RemoveKeyLessThan() {}
+
+    private static final String INPUT = "input";
+    private static final String OUTPUT = "output";
+    private static final String NUM_REDUCERS = "numReducers";
+    private static final String MINSIM = "minsim";
+    //private static final String THRESHOLD = "threshold";
+
+    /**
+     * Runs this tool.
+     */
[…]

### 2013-11-12 article/article-draft.tex
Fixed wrong argument type in context param

@@
  For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature.
-Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences.
+Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure.
 Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.

### 2013-11-12 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -63,6 +63,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 clusterTitleSentences.add(doc + "\t" + sentence);
                 clusterDocs.add(doc);
             }
+
             //if(clusterSentences.size() == 1){
               //  return;
             //}
@@ -77,10 +78,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 context.write(clusterID, VALUE);
   //          }
 
-
-
-            
         }
+
     }
    
     private static class MyMapper extends Mapper<LongWritable, ArrayListWritable<Text>, PairOfStrings, IntWritable> {
@@ -117,7 +116,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static class MyReducer extends Reducer<PairOfStrings, IntWritable, PairOfStrings, IntWritable> {
         private static final IntWritable SUM = new IntWritable();
 
-        
+        public static long minsim = 2;
+
         @Override
         public void reduce(PairOfStrings articlepair, Iterable<IntWritable> values, Context context)
                 throws IOException, InterruptedException {
@@ -129,11 +129,20 @@ public class SentenceSimilarityCount extends Configured implements Tool {
             while (iter.hasNext()) {
                 sum+= iter.next().get();
             }
-            
+            if(sum < minsim){
+                return;
+            }                    
             SUM.set(sum);
             context.write(articlepair, SUM);
 
         }
+
+        @Override
+        public void setup(Context context){
+            minsim = context.getConfiguration().getLong("minsim", 2);
+            
+        }
+        
    }
 
     private static class FlipMapper extends Mapper<PairOfStrings, IntWritable, IntWritable, PairOfStrings> {
@@ -157,6 +166,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
     private static final String INPUT = "input";
     private static final String OUTPUT = "output";
     private static final String NUM_REDUCERS = "numReducers";
+    private static final String MINSIM = "minsim";
     //private static final String THRESHOLD = "threshold";
 
     /**
@@ -176,8 +186,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         options.addOption(OptionBuilder.withArgName("num").hasArg()
[…]

### 2013-11-12 src/main/wikiduper/utils/junk/RemoveKeyLessThan.java

@@ -111,7 +111,7 @@ public class RemoveKeyLessThan extends Configured implements Tool {
         job.setJarByClass(RemoveKeyLessThan.class);
         job.setNumReduceTasks(0);
         
-        conf.setLong("minsim", minsim);
+        conf.setInt("minsim", minsim);
         conf.set("mapred.job.map.memory.mb", "6144");
         conf.set("mapred.map.child.java.opts", "-Xmx6144m");
         conf.set("mapred.job.reduce.memory.mb", "6144");

### 2013-11-12 src/main/wikiduper/utils/junk/RemoveKeyLessThan.java
Fixed wrong argument type in context param

@@ -33,15 +33,15 @@ public class RemoveKeyLessThan extends Configured implements Tool {
         @Override
         public void map(IntWritable key, PairOfStrings value, Context context)
                 throws IOException, InterruptedException {
-            if(key.get() < minsim){
-                return;
+            if(key.get() >= minsim){
+                context.write(key, value);
             }
-            context.write(key, value);
+            
         }
         
         @Override
         public void setup(Context context){
-            minsim = context.getConfiguration().getInt("minsim", 2);
+            minsim = context.getConfiguration().getInt("minsim", 20);
         }
     }
 

### 2013-11-12 src/main/wikiduper/utils/junk/RemoveKeyLessThan.java
changing ordering of conf to see if will recognize param

@@ -106,10 +106,6 @@ public class RemoveKeyLessThan extends Configured implements Tool {
 
         // set job configurations
         Configuration conf = getConf();
-        Job job = Job.getInstance(conf);
-        job.setJobName("SentenceSimilarityCount");
-        job.setJarByClass(RemoveKeyLessThan.class);
-        job.setNumReduceTasks(0);
         
         conf.setInt("minsim", minsim);
         conf.set("mapred.job.map.memory.mb", "6144");
@@ -117,6 +113,10 @@ public class RemoveKeyLessThan extends Configured implements Tool {
         conf.set("mapred.job.reduce.memory.mb", "6144");
         conf.set("mapred.reduce.child.java.opts", "-Xmx6144m");
 
+        Job job = Job.getInstance(conf);
+        job.setJobName("SentenceSimilarityCount");
+        job.setJarByClass(RemoveKeyLessThan.class);
+        job.setNumReduceTasks(0);
         
         //Job 1
         FileInputFormat.setInputPaths(job, new Path(inputPath));

### 2013-11-12 src/main/wikiduper/utils/junk/RemoveKeyLessThan.java
Added a reducer to group results

@@ -116,7 +116,7 @@ public class RemoveKeyLessThan extends Configured implements Tool {
         Job job = Job.getInstance(conf);
         job.setJobName("SentenceSimilarityCount");
         job.setJarByClass(RemoveKeyLessThan.class);
-        job.setNumReduceTasks(0);
+        job.setNumReduceTasks(1);
         
         //Job 1
         FileInputFormat.setInputPaths(job, new Path(inputPath));

### 2013-11-12 article/article-draft.tex
Removed threshold argument from connected component code

@@
 
- For clarity purposes, we define \emph{similarity count} as simply the total number of sentences between two articles that were found to share the same hash signature.
+ For clarity purposes, we define \emph{similarity count} as simply the total number of unique sentences between two articles that were found to share the same hash signature.
 Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure.
-Overall, we found $\approx 29580$ wikipedia article pairs that had a similarity count greater than $50$.
+Overall, we found $\approx 121000$ wikipedia article paris that had a similarity count greater than or equal to $20$ and $\approx 29580$ wikipedia article pairs that had a similarity count greater than or equal to $50$.
 
@@
 What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$.
-Based on the fact that we found $\approx 6500$ article pairs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common.
+2,361,886 unique sentences.
+Based on the number of airs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common.
 As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in Figure \ref{toparticles}).

### 2013-11-12 src/main/wikiduper/analysis/GetDocComponents.java

@@ -53,7 +53,6 @@ public class GetDocComponents extends Configured implements Tool {
 
     private static final String INPUT = "input";
     private static final String OUTPUT = "output";
-    private static final String THRESHOLD = "threshold";
 
     @SuppressWarnings("static-access")
     @Override
@@ -63,8 +62,6 @@ public class GetDocComponents extends Configured implements Tool {
                 .hasArg().withDescription("output path").create(OUTPUT));
         options.addOption(OptionBuilder.withArgName("path")
                 .hasArg().withDescription("minhash output buckets").create(INPUT));
-        options.addOption(OptionBuilder.withArgName("num")
-                .hasArg().withDescription("similarity threshold").create(THRESHOLD));
 
         CommandLine cmdline;
         CommandLineParser parser = new GnuParser();
@@ -75,7 +72,7 @@ public class GetDocComponents extends Configured implements Tool {
             return -1;
         }
 
-        if (!cmdline.hasOption(OUTPUT) || !cmdline.hasOption(INPUT) || !cmdline.hasOption(THRESHOLD)){
+        if (!cmdline.hasOption(OUTPUT) || !cmdline.hasOption(INPUT)){
             HelpFormatter formatter = new HelpFormatter();
             formatter.setWidth(120);
             formatter.printHelp(this.getClass().getName(), options);
@@ -85,7 +82,6 @@ public class GetDocComponents extends Configured implements Tool {
 
         String outputPath = cmdline.getOptionValue(OUTPUT);
         String inputPath = cmdline.getOptionValue(INPUT);
-        int threshold = Integer.parseInt(cmdline.getOptionValue(THRESHOLD));
         LOG.info("Tool name: " + this.getClass().getName());
         LOG.info(" - output file: " + outputPath);
         
@@ -93,7 +89,7 @@ public class GetDocComponents extends Configured implements Tool {
 
         /* Get Clusters from MinhashWikipediaPages pair output */
         
-        getClusters(inputPath,conf,outputPath,threshold);
+        getClusters(inputPath,conf,outputPath);
 
         return 0;
     }
@@ -120,11 +116,11 @@ public class GetDocComponents extends Configured implements Tool {
     // Creates a global cluster numbering and a map from doc numbers to sentences and their cluster numbers
     // Writes the docmap to docmapFile
     //static final Pattern sentencepattern = Pattern.compile(".*\\[(.+), (.+), (.+)\\].*");
[…]

### 2013-11-12 article/article-draft.tex
Fixed conf for minimum similarity argument in sentence similarity code. Added argument to toggle filtering.

@@
 Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure.
-Overall, we found $\approx 121000$ wikipedia article paris that had a similarity count greater than or equal to $20$ and $\approx 29580$ wikipedia article pairs that had a similarity count greater than or equal to $50$.
+Overall, we found $\approx 121,000$ wikipedia article paris that had a similarity count greater than or equal to $20$ and $\approx 29,580$ wikipedia article pairs that had a similarity count greater than or equal to $50$.
+If we performt the same similarity analysis, but filter clusters using the template heuristic described above,
 

### 2013-11-12 src/main/wikiduper/analysis/SentenceSimilarityCount.java

@@ -18,7 +18,6 @@ import org.apache.hadoop.fs.Path;
 import org.apache.hadoop.io.IntWritable;
 import org.apache.hadoop.io.LongWritable;
 import org.apache.hadoop.io.Text;
-import org.apache.hadoop.mapred.JobConf;
 import org.apache.hadoop.mapreduce.Job;
 import org.apache.hadoop.mapreduce.Mapper;
 import org.apache.hadoop.mapreduce.Reducer;
@@ -30,7 +29,6 @@ import org.apache.hadoop.util.Tool;
 import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
 
-import cern.colt.Arrays;
 import edu.umd.cloud9.io.array.ArrayListWritable;
 import edu.umd.cloud9.io.pair.PairOfStrings;
 
@@ -43,6 +41,8 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         private static final HashSet<String> clusterTitleSentences = new HashSet<String>();
         private static final HashSet<String> clusterSentences = new HashSet<String>();
         private static final HashSet<String> clusterDocs = new HashSet<String>();
+        private static boolean filter = false;
+        
         @Override
         public void reduce(LongWritable clusterID, Iterable<PairOfStrings> docs, Context context)
                 throws IOException, InterruptedException {
@@ -64,20 +64,23 @@ public class SentenceSimilarityCount extends Configured implements Tool {
                 clusterDocs.add(doc);
             }
 
-            //if(clusterSentences.size() == 1){
-              //  return;
-            //}
-    //        double score = TemplateClusters.scoreCluster(clusterTitleSentences);
+            if(filter){
+                if(clusterSentences.size() == 1) return;
+                double score = TemplateClusters.scoreCluster(clusterTitleSentences);
+                if(score >= .6) return;
+            }
+            for(String doc : clusterDocs){
+                Text docout = new Text();
+                docout.set(doc);
+                VALUE.add(docout);
+            }
+            context.write(clusterID, VALUE);
 
-//            if(score < .6){
-                for(String doc : clusterDocs){
-                    Text docout = new Text();
-                    docout.set(doc);
-                    VALUE.add(docout);
-                }
-                context.write(clusterID, VALUE);
-  //          }
-
+        }
+        
+        @Override
+        public void setup(Context context){
+            filter = context.getConfiguration().getBoolean("filter", false);
         }
 
[…]

### 2013-11-12 src/main/wikiduper/analysis/SentenceSimilarityCount.java
Added args to job name

@@ -233,8 +233,9 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         conf.set("mapred.job.reduce.memory.mb", "6144");
         conf.set("mapred.reduce.child.java.opts", "-Xmx6144m");
 
+        String jobargs = String.format("[%s: %s, %s: %s, %s: %d, %s: %b]", INPUT, inputPath, OUTPUT, outputPath, MINSIM, minsim, FILTER, filter);
         Job job = Job.getInstance(conf);
-        job.setJobName("SentenceSimilarityCount");
+        job.setJobName("SentenceSimilarityCount-2 " + jobargs);
         job.setJarByClass(SentenceSimilarityCount.class);
         job.setNumReduceTasks(reduceTasks);
         
@@ -267,8 +268,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         
         // Job 2 
         job = Job.getInstance(conf);
-        
-        job.setJobName("SentenceSimilarityCount-2");
+        job.setJobName("SentenceSimilarityCount-2 " + jobargs);
         job.setJarByClass(SentenceSimilarityCount.class);
         job.setNumReduceTasks(reduceTasks);
 
@@ -302,7 +302,7 @@ public class SentenceSimilarityCount extends Configured implements Tool {
         // Job 3
         job = Job.getInstance(conf);
         
-        job.setJobName("SentenceSimilarityCount-3");
+        job.setJobName("SentenceSimilarityCount-3 " + jobargs);
         job.setJarByClass(SentenceSimilarityCount.class);
         job.setNumReduceTasks(1);
 

### 2013-11-24 article/article-draft.tex
Updates to original article and new article draft

--- 2013-11-12 article/article-draft.tex
@@
 \begin{abstract}
-The growth of the Internet has enabled collaboration and cooperation on a large scale, resulting in an abundant number of near-duplicate web documents.
-Information is propagated on a large scale, which means that finding (and correcting) factual errors is made more difficult, since such errors may be duplicated many times over in different locations.
+On collaboratively authored sites like Wikipedia (\url{http://www.wikipedia.org}), where information is propagated on a large scale by a large number of authors, finding (and correcting) factual errors is difficult.
 Wikipedia articles, which are written and edited by an open community of mostly anonymous users are a prime candidate for copying of information.
-With few exceptions, the reader of any article can edit the text by copying from another article or an outside source without prior approval or confirmation of correctness.
-Although Wikipedia has its own policies and procedures for maintaining articles and improving quality, questions of the quality and accuracy of information on the website remain.
+With few exceptions, the reader of any article can edit the text by copying from another article or an outside source without prior approval or confirmation of correctness and such errors may be duplicated many times over in different locations.
+Although Wikipedia has its own policies and procedures for maintaining articles and monitoring article quality, questions of the accuracy of information on the website remain.
 Although we do not directy attempt to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
-Such near duplicate sentences may reflect factual information that has been updated in one article and not another, or merely inconsistencies that should be flagged and addressed.
+Such near duplicate sentences may reflect factual information that has been updated in one article and not another, redundant content that should be merged, or merely inconsistencies that should be flagged and addressed.
 
-In this paper, we describe a similarity detection algorithm for Wikipedia articles that utilizes a locality sensitive hashing (LSH) technique on the MapReduce framework.
+In this paper, we describe a similarity detection algorithm for Wikipedia articles that uses a locality sensitive hashing (LSH) technique implemened on the Hadoop MapReduce framework.
 The algorithm has been designed and implemented to detect similar content at the sentence level using large Wikipedia dumps.
@@
 The online encyclopedia Wikipedia is a collaboratively edited, multilingual, free resource.
-As of xxx date, it contains 26 million articles, over 4.2 million in English alone.
-These articles are written and edited by volunteer contributors around the world.
-Most articles can be edited by anyone with internet access, and there are currently approximately 100,000 active contributors.
+As of November 2013, there are over 31 million wiki pages with over 4 million articles in English and over 20,086,301 registered user accounts on the system \cite{wiki:weblink}.
+Most articles can be edited by anyone with internet access and an account is not required to edit.
 
@@
 
-Under such conditions, this type of large-scale collaborative effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity \cite{wiki:weblink} [??].
+Under such conditions, this type of large-scale collaborative effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity.
 For our purposes, we focus primarily on the sentence level.
@@
 
-Our approach applies minhashin, a well known, scalable, locality sensitive hashing (LSH) technique for near duplicate document detection.
+Our approach applies minhashing, a well known, scalable, locality sensitive hashing (LSH) technique for near duplicate document detection.
 Since we are assuming the content we are looking for is not just similar, but has diverged due to an editorial process, as part of this work we investigate how well minhash approximates edit distance.
@@
 \end{itemize}
-
-Along with these questions, we also considered the scalability and efficiency issues due to the large size of Wikipedia.
-To address these issues, we implemented our algorithm on the MapReduce computing framework.
 
@@
 
-\subsection{Design}
-Many signature techniques such as LSH are embarrassingly parallel. In our project, we designed our algorithm around the MapReduce framework.
+%% \subsection{Design}
+%% Many signature techniques such as LSH are embarrassingly parallel. In our project, we designed our algorithm around the MapReduce framework.
 
-Because the minhash technique is parametrized by several variables, including shingle length, signature size, and number of signatures to be calculated per document, these values can also be considered as inputs for the MapReduce algorithm.
+%% Because the minhash technique is parametrized by several variables, including shingle length, signature size, and number of signatures to be calculated per document, these values can also be considered as inputs for the MapReduce algorithm.
 
-\begin{table}
-\begin{algorithm}[H]
-\caption{Minhash MapReduce Pseudocode}
-\begin{algorithmic}
-\Function{initialize}{}
-%\Comment{configure and set up algorithm parameters}
- \State $F \gets $ hash family;
- \State $L \gets $ shingle length;
- \State $K \gets $ vector length;
- \State $N \gets $ number of signatures to emit;
-\EndFunction
+%% \begin{table}
+%% \begin{algorithm}[H]
+%% \caption{Minhash MapReduce Pseudocode}
+%% \begin{algorithmic}
+%% \Function{initialize}{}
+%% %\Comment{configure and set up algorithm parameters}
+%%  \State $F \gets $ hash family;
+%%  \State $L \gets $ shingle length;
+%%  \State $K \gets $ vector length;
+%%  \State $N \gets $ number of signatures to emit;
+%% \EndFunction
 
-\Function{map}{docid $d$, wikipage $p$}
- \State sentencect $\gets 0$
- %\Comment {Break up article text into sentence}
- \While{$s \gets$ nextSentence($p$)}
-  %\Comment{Break up sentence into shingles}
-  \State shingles $\gets$ shingleSet($s$,$L$);
-  \State minhashes = new List(|F|);
-   \For{$i \gets 1 \ldots |F|$}
-    \State minhashes[$i$] $\gets \infty$;
-   \EndFor
-   %\Comment{Calculate set of minhash signature for each sentence}
-   \For{$g \in$ shingles}
-    \For{$i \gets 1 \ldots |F|$}
-     \State minhashes[$i$] $\gets$ min($F_i(g)$,minhashes[$i$]);
-    \EndFor
-   \EndFor
-   %\Comment{Emit $N$ $K$-length signatures}
-  \For{$i \gets 1 \ldots N$}
-   \State sig = select($K$, minhahses);
-   \State emit(sig,(docid,sentencect));
-  \EndFor
-  \State  sentencect++;
- \EndWhile
-\EndFunction
+%% \Function{map}{docid $d$, wikipage $p$}
+%%  \State sentencect $\gets 0$
+%%  %\Comment {Break up article text into sentence}
+%%  \While{$s \gets$ nextSentence($p$)}
+%%   %\Comment{Break up sentence into shingles}
+%%   \State shingles $\gets$ shingleSet($s$,$L$);
+%%   \State minhashes = new List(|F|);
+%%    \For{$i \gets 1 \ldots |F|$}
+%%     \State minhashes[$i$] $\gets \infty$;
+%%    \EndFor
+%%    %\Comment{Calculate set of minhash signature for each sentence}
+%%    \For{$g \in$ shingles}
+%%     \For{$i \gets 1 \ldots |F|$}
+%%      \State minhashes[$i$] $\gets$ min($F_i(g)$,minhashes[$i$]);
+%%     \EndFor
+%%    \EndFor
+%%    %\Comment{Emit $N$ $K$-length signatures}
+%%   \For{$i \gets 1 \ldots N$}
+%%    \State sig = select($K$, minhahses);
+%%    \State emit(sig,(docid,sentencect));
+%%   \EndFor
+%%   \State  sentencect++;
+%%  \EndWhile
+%% \EndFunction
 
-\Function{reduce}{signature sig, sentenceids $S$}
-\If{$|S| > 1$}
-\State emit(sig, $S$);
-\EndIf
-\EndFunction
-\end{algorithmic}
-\end{algorithm}
-\end{table}
+%% \Function{reduce}{signature sig, sentenceids $S$}
+%% \If{$|S| > 1$}
+%% \State emit(sig, $S$);
+%% \EndIf
+%% \EndFunction
+%% \end{algorithmic}
+%% \end{algorithm}
+%% \end{table}
 
@@
 
-As mentioned above the minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
+The minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
 Each of these parameters has an impact on the error rates in the minhash output.
@@
 
-\subsubsection{Break down of sentence types}
+\subsubsection{Breakdown of Sentence Types and Filtering}
 
 By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table \ref{counts}.
+The manual analysis reveals that $\approx 75\%$ of the clusters identified are either in the \emph{identical} or the \emph{template} classes.
+We argue that these classes are less interesting, since they represent either large collections of identically formatted and very specific facts, or content that is exactly the same, and such content is at least internally consistent, if redundant, and less likely to contain errors.
+Thus they are candidates for filtering out of the result set.
 
@@
 
-To get a rough estimate of the number of template clusters, we develop a heuristic score on low frequency words in the cluster word set to identify templates.
+Identical clusters are easy to identify through exact hashing.
+In order to get a rough filter for template clusters, we develop a heuristic score on low frequency words in the cluster word set.
 For our purposes a low-frequency word is one that occurs in less than half of the cluster sentences.
@@
 \[(\#numeric + \#proper)/(\#numeric + \#proper + \#other)\]
-Where \#numeric is the number of numeric terms in the cluster word set (all unique words occuring in the cluster), \#proper is the number of proper nouns in the cluster word set (i.e.
+Where \#numeric is the number of numeric terms in the cluster word set (all unique low frequency words occuring in the cluster), \#proper is the number of proper nouns in the cluster word set (i.e.
 capitalized words), and \#other is the number of other words.
 
-Applying the score to our hand-classified clusters shows us that this score does separate between template and non-template clusters.
-(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.) See Figure \ref{heuristic}.
+Applying the score to our hand-classified clusters we see (Figure \ref{heuristic}) that this score does separate between template and non-template clusters.
+(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.)
 
-After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
+After applying the score to the entire set of wiki clusters (with a score threshold of .6), we identify 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
 The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196 sentences.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.43, keepaspectratio = true]{Top10ArticlePairs.jpg}
-\end{center}
-\caption{Top 10 Similarity Counts}
-\label{toparticles}
-\end{figure}
-
  For clarity purposes, we define \emph{similarity count} as simply the total number of unique sentences between two articles that were found to share the same hash signature.
 Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure.
-Overall, we found $\approx 121000$ wikipedia article paris that had a similarity count greater than or equal to $20$ and $\approx 29580$ wikipedia article pairs that had a similarity count greater than or equal to $50$.
+Overall, we found $91,591$ wikipedia article paris that had a similarity count greater than or equal to $25$ and $29,582$ wikipedia article pairs that had a similarity count greater than or equal to $50$, and $\approx 6331$ Wikipedia articles with similarity count greater than or equal to $75$.
+If we perform the same similarity analysis, but filter clusters using the template heuristic described above, we find $5950$ article pairs with similarity count greater than or equal to $25$, $472$ article pairs with similarity greater than or equal to $50$ and $159$ article pairs with similarity greater than or equal to $75$.
+Table \ref{toparticlegroups}) shows the top similar article groups with similarity count greater than 100 (where pairs sharing an element have been merged).
 
-Looking at the distribution of cluster sizes in Figure \ref{clust}, we can see the expected behavior of decreasing number of clusters of size $k$ as $k$ grows large.
-What is unusual though is the number of relatively large clusters in the size range of $[25, 65]$.
-2,361,886 unique sentences.
-Based on the number of airs with a similarity count greater than $50$, this would indicate that there are collections of articles that have a large number of near-duplicate sentences in common.
-As can be seen in the Top 10 similarity counts, there can even be chains of articles that share large portions of their content with each other (a chain of 3 is demonstrated in Figure \ref{toparticles}).
-
-\begin{table}
+\begin{figure*}[hp!]
 \centering
-\caption{Top 10 Article Pair Titles}
+\caption{Top Similar Article Groupings, Similarity Count $\ge$ 100}
 {\small
@@
     \hline
-\{Private equity in the 2000s, History of private equity and venture capital, Private equity in the 1980s\} \\
+\{Hindi Cinema, Bollywood\} \\
+\{Telecommunications in the People's Republic of China, Telecommunications in China\} \\
+\{Private equity in the 2000s, History of private equity and venture capital\} \\
 \{List of ethnic cleansings, Ethnic cleansing\} \\
@@
 \{English literature, British literature\} \\
-\{Portia schultzi, Portia labiata, Portia fimbriata\} \\
-\{Lesbian American history, List of lesbian, gay, bisexual, or transgender firsts by year\} \\
-\{Lists of British inventions, List of English inventions and discoveries\} \\
-\{1981 in baseball, 1981 Major League Baseball season\} \\
-\{Minority Report (film), Themes in Minority Report\} \\
-\{What Is History?, E. H. Carr\} \\
-\{Individualist anarchism in Europe, Individualist anarchism in the United States, Individualist anarchism, Anarchism in the United States\} \\
-\{Kingdom of Scotland, Scotland in the Early Modern Era\} \\
-\{Decline of Greco-Roman polytheism, Christian persecution of paganism after Theodosius I until the fall of the Roman Empire\} \\
-\{Anarchist schools of thought, Libertarian socialism, Anarchist communism, Anarchism, History of anarchism, Libertarian Marxism\} \\
-\{Brill Tramway, Quainton Road railway station\} \\
+\{Maritime history of the United States (1900–99), History of the United States Merchant Marine\} \\
+\{Culture of the United States, Society of the United States\} \\
+\{Halifax (former city), History of the Halifax Regional Municipality\} \\
+\{List of SNK characters, List of The King of Fighters characters\} \\
+\{Toronto Blue Jays, History of the Toronto Blue Jays\} \\
+\{History of Christianity in the United States, History of Protestantism in the United States\} \\
+\{Sri Ranganathaswamy Temple, Srirangam, Šri Ranganata Svami hram\} \\
+\{Individualist anarchism in Europe, Individualist anarchism\} \\
+\{Nutritional neuroscience, Nutrition and cognition\} \\
+\{Jesse Hubbard and Angie Baxter, The Hubbard Family\} \\
+\{History of the Dallas Mavericks, Dallas Mavericks\} \\
+\{Imperial Crypt Vaults, Imperial Crypt\} \\
 \{History of the Roman Empire, Byzantine Empire, History of the Byzantine Empire\} \\
-\{List of American state and local politicians convicted of crimes, List of state and local political scandals in the United States\} \\
-\{Filioque, History of the Filioque controversy\} \\
-\{1960 Major League Baseball season, 1960 in baseball\} \\
-\{Domitian, Flavian dynasty\} \\
-\{Military history of Australia during World War II, Australian Army during World War II\} \\
-\{Kuomintang, History of the Kuomintang\} \\
-\{Interracial marriage, Miscegenation, Eurasian (mixed ancestry)\} \\
+\{May Bukas Pa, List of May Bukas Pa episodes\} \\
+\{Myth: The Fallen Lords, Myth (series)\} \\
+\{Individualist anarchism in the United States, Anarchism in the United States\} \\
+\{Native Americans in the United States, Native American cultures in the United States\} \\
+\{Hockey stick controversy, Hockey stick graph\} \\
+\{Vancouver Canucks, History of the Vancouver Canucks\} \\
+\{Silvio Berlusconi, Controversies surrounding Silvio Berlusconi\} \\
+\{Los Angeles Angels of Anaheim, History of the Los Angeles Angels of Anaheim\} \\
+\{2007 suicide bombings in Iraq, List of terrorist incidents in Iraq in 2007\} \\
+\{List of Canadian tornadoes and tornado outbreaks, List of 21st-century Canadian tornadoes and tornado outbreaks\} \\
 \{Scotland in the modern era, History of Scotland\} \\
-\{History of California, Maritime history of California\} \\
-\{Outline of project management, Glossary of project management\} \\
-\{Wigan Warriors, History of Wigan Warriors\} \\
-\{List of American federal politicians convicted of crimes, List of federal political scandals in the United States\} \\
+\{Libertarian socialism, Libertarian Marxism\} \\
+\{Canti (Leopardi), Giacomo Leopardi\} \\
+\{Jayne Torvill, Christopher Dean, Torvill and Dean\} \\
+\{Government of Mahmoud Ahmadinejad (2005–present), Foreign policy of Mahmoud Ahmadinejad, Mahmoud Ahmadinejad\} \\
 \{Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages\} \\
+\{Go Nagai bibliography, Go Nagai\} \\
 \{Galvatron, Megatron\} \\
-\{Metropolitan Police role in the news media phone hacking scandal, News media phone hacking scandal\} \\
-\{List of Shakespearean characters (L-Z), List of Shakespearean characters (A-K), List of historical figures dramatised by Shakespeare\} \\
-\{Fetal alcohol spectrum disorder, Fetal alcohol syndrome\} \\
-\{List of marine bony fishes of South Africa, List of marine animals of the Cape Peninsula and False Bay\} \\
+\{History of Australia (1901–45), History of Australia\} \\
+\{Interracial marriage, Miscegenation\} \\
+\{List of Prison Break recurring characters, List of Prison Break minor characters\} \\
+\{History of Eastern Orthodox Christian theology, History of the Orthodox Church\} \\
+\{69th Infantry Regiment (United States), 69th Infantry Regiment (New York)\} \\
+\{The Anarchy, Stephen, King of England\} \\
 \{History of painting, Western painting, 20th-century Western painting\} \\
-\{Timeline of the 2007 Burmese anti-government protests, 2007 Burmese anti-government protests\} \\
-\{Precipitation, Rain\} \\
-\{List of Puerto Ricans, List of Puerto Rican military personnel\} \\
-\{Glossary of basketball terms, Outline of basketball\} \\
-\{Hannibal, Conquests of Hannibal\} \\
-\{Bogotá, History of Bogotá\} \\
-\{Pseudotsuga menziesii var. menziesii, Douglas fir\} \\
-\{History of the East-West Schism, East-West Schism\} \\
-\{List of attacks in Lebanon, Lebanon bombings and assassinations (2004-present)\} \\
-\{Zen, Chinese Chán\} \\
+\{Sino-Pacific relations, Foreign relations of China\} \\
+\{History of the East–West Schism, East–West Schism\} \\
+\{History of the Detroit Tigers, Detroit Tigers\} \\
+\{San Francisco Giants, History of the San Francisco Giants\} \\
+\{Hernán Cortés, Oconahua, Jalisco\} \\
 \{List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)\} \\
-\{1991 Major League Baseball season, 1991 in baseball\} \\
+\{Port of Tianjin operations and logistics, Port of Tianjin\} \\
 \{American rock, Rock music\} \\
-\{Test matches in England in 2005, Australian cricket team in England in 2005\} \\
-\{Swedes, Sweden\} \\
-\{Glossary of robotics, Outline of robotics\} \\
+\{One-Day Internationals in England in 2005, Test matches in England in 2005, Australian cricket team in England in 2005\} \\
+\{History of Christianity, History of Christianity of the Middle Ages\} \\
+\{History of the Texas Rangers (baseball), Texas Rangers (baseball)\} \\
+\{List of Irish Americans, List of Americans of Irish descent\} \\
+\{Radeon HD 3000 Series, R600 (ASIC)\} \\
+\{Robert Edmund Strahorn, Battle of Slim Buttes\} \\
+\{Cleveland Indians, History of the Cleveland Indians\} \\
 \{CIA leak scandal criminal investigation, Plame affair grand jury investigation\} \\
-\{History of Australia since 1945, History of Australia\} \\
+\{History of Western civilization, History of Western civilization before AD 500\} \\
+\{Benigno Aquino III, Presidency of Benigno Aquino III\} \\
+\{Kingdom of Greece, History of modern Greece\} \\
 \{List of Russian people, List of Russian scientists\} \\
-    %% 21986867 & 2000 New Year Honours \\ \hline
-    %% 21986897 & 1999 New Year Honours \\ \hline
-    %% 3951586 & Instruments of the United Kingdom, 1994 \\ \hline
-    %% 3951664 & Instruments of the United Kingdom, 1995 \\ \hline
-    %% 1903966 & Management of baldness \\ \hline
-    %% 38088660 & Management of androgenic alopecia \\ \hline
-    %% 1503105 & Jayne Torvill \\ \hline
-    %% 1503115 & Christopher Dean \\ \hline
-    %% 184843 & Henry VI, Part 1 \\ \hline
-    %% 184846 & Henry VI, Part 2 \\ \hline
-    %% 184847 & Henry VI, Part 3 \\ \hline
-    %% 10701462 & List of birds of Zambia \\ \hline
-    %% 10930255 & List of birds of Zimbabwe \\ \hline
-    %% 10930111 & List of birds of Mozambique \\ \hline
-    %% 48711 & Oregon Trail \\ \hline
-    %% 31518964 & History of the Oregon Trail \\
 \hline
@@
 }
-\end{table}
+\label{toparticlegroups}
+\end{figure*}
 
-\section{Conclusion and Future Work}
-This paper presents our work on near-duplicate detection of Wikipedia articles at the sentence-granularity level using MinHash, a LSH technique.
-Our novel MapReduce algorithm tackles the problem by transforming it into more manageable pieces where each piece is handled in parallel.
-Our unique contribution includes empirical analysis of signatures belonging to Wikipedia articles at the sentence level.
-Experimental results verify that the proposed method is able to effectively and efficiently detect similar articles.
+\section{Conclusions and Future Work}
 
-In the future, we would like to investigate revision histories of these articles, correlate them with their timestamps, and better relate similarities based on temporal dimensions.
+Although the LSH technique of minhashing does not perfectly approximate edit distance, we have demonstrated that, when implemented in the Hadoop framework, it is an efficient method for identifying large numbers of Wikipedia sentences that are near duplicates.
+Additionally, we demonstrated that it is possible to apply a simple heuristic and to filter sentences that result from templatification, which make up about half (by our heuristic scoring) of the sentences identified in the similar sentence analysis.
+Because templatification appears quite often as almanac-like lists of facts, quite possibly generated with automated ``bots'' given the large scale of some templatified clusters, it is a worthwhile exercise to identify and quantify such content as distinct from other content found on the Wikipedia site.
+
+Although sentences can be used as a measure of article similarity, identifying similarity at the sentence level allows greater flexibility for finding similar content across documents than a whole document analysis.
+These techniques could be used to automatically suggest corrections to Wikipedia, or to improve plagiarism detection across web content in general.
+
+Future work could investigate revision histories of articles and correlate similar sentence with article edit timestamps to better relate similarities on a temporal dimension.
+An analysis on a multi-sentence level could identify more similarities where user edits change sentence boundaries by merging or breaking up content which our present analysis would not detect.
+Additionally, a more sophisticated template detection heuristic could be developed, as the one used here is a very rough measure that makes assumptions specific to English language text.
 
@@
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+\bibliography{article-draft}  % sigproc.bib is the name of the Bibliography in this case
 

### 2013-11-24 article/clarticle/article-draft.tex
Updates to original article and new article draft

--- 2013-11-24 article/article-draft.tex
@@
 
-\title{Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia}
+\title{Cross Language Similar Sentence Detection}
 
@@
 \author{
-\alignauthor Samet Ayhan\\
-       \affaddr{University of Maryland}\\
-       \affaddr{Dept. of Computer Science}
-       \email{sayhan@cs.umd.edu}
-\alignauthor Joshua Bradley\\
-       \affaddr{University of Maryland}\\
-       \affaddr{Dept. of Computer Science}
-       \email{jgbrad1@cs.umd.edu}
 \alignauthor Sarah E. Weissman\\
@@
 
-\date{October 9, 2013}
+\date{November 24, 2013}
 
@@
 \begin{abstract}
-On collaboratively authored sites like Wikipedia (\url{http://www.wikipedia.org}), where information is propagated on a large scale by a large number of authors, finding (and correcting) factual errors is difficult.
-Wikipedia articles, which are written and edited by an open community of mostly anonymous users are a prime candidate for copying of information.
-With few exceptions, the reader of any article can edit the text by copying from another article or an outside source without prior approval or confirmation of correctness and such errors may be duplicated many times over in different locations.
-Although Wikipedia has its own policies and procedures for maintaining articles and monitoring article quality, questions of the accuracy of information on the website remain.
-Although we do not directy attempt to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
-Such near duplicate sentences may reflect factual information that has been updated in one article and not another, redundant content that should be merged, or merely inconsistencies that should be flagged and addressed.
-
-In this paper, we describe a similarity detection algorithm for Wikipedia articles that uses a locality sensitive hashing (LSH) technique implemened on the Hadoop MapReduce framework.
-The algorithm has been designed and implemented to detect similar content at the sentence level using large Wikipedia dumps.
-We also describe a heuristic method for classifying types of duplications on Wikipedia, which could be used for selecting and prioritizing editing efforts.
 \end{abstract}
@@
 
-\terms{Algorithms, Design, MapReduce}
+\terms{Minhash, MapReduce}
 
 \section{Introduction}
-The online encyclopedia Wikipedia is a collaboratively edited, multilingual, free resource.
-As of November 2013, there are over 31 million wiki pages with over 4 million articles in English and over 20,086,301 registered user accounts on the system \cite{wiki:weblink}.
-Most articles can be edited by anyone with internet access and an account is not required to edit.
-
-Because of its open nature, Wikipedia has a history of generating controversy over editorial quality and factual correctness.
-Although some studies have found Wikipedia's accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.[References??] Since Wikipedia may be edited anonymously, information may freely copied between web sources and even between Wikipedia articles without verification.
-Additionally, many articles in Wikipedia lack citations.
-Although there are active communities of editors who contribute to the upkeep of various articles, often focusing on a partiular subject area and expanding and improving the related content, still much of Wikipedia content is created in an unsupervised manner.
-Wilkinson found the distribution of article edits on Wikipedia to have a long tail, meaning that a small number of articles have many edits while most articles have few, and that the number of edits is directly related to article quality.
-Articles with low edits and low editorial attention, are less likely to be updated when new information is available \cite{wilkinson:wiki}.
-
-Under such conditions, this type of large-scale collaborative effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity.
-For our purposes, we focus primarily on the sentence level.
-Near duplicate sentences may reflect factual information that has been updated in one article and not another (for example, information that varies over time, like populations or a country's GDP), or merely inconsistencies that should be flagged and addressed.
-
-Our approach applies minhashing, a well known, scalable, locality sensitive hashing (LSH) technique for near duplicate document detection.
-Since we are assuming the content we are looking for is not just similar, but has diverged due to an editorial process, as part of this work we investigate how well minhash approximates edit distance.
-We investigate the following questions:
-\begin{itemize}[noitemsep,nolistsep]
-\item How effectively does minhashing approximate edit distance?
-Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
-\item How well do techniques for detecting near duplicate documents work when applied at the sentence level?
-\item Do near duplicate sentences correspond to factual errors?
-\end{itemize}
-
-The rest of this paper is organized as follows: In Section 2, we present related work, in Section 3, we explain the algorithm utilizing locality sensitive hashing, in Section 4, we discuss parameter tuning for Minhash.
-In Section 5, we present the working application within the MapReduce framework.
-In Section 6, we discuss our experiments with various Wikipedia datasets.
-The final section contains concluding remarks and future work.
 
 \section{Related Work}
-A number of techniques have been implemented to identify similarity between documents in the literature.
-These techniques usually differ in terms of corpus of interest, signature representing the document, feature-set determined by the system, and the end goal of the analysis.
 
-Broder et al.
-introduced shingling to compute document similarity and containment.
-They also presented methods for using a subset of shingles while still allowing similarity and containment computations \cite{broder:resemblance}.
-
-Seo et al.
-defined a general framework for text reuse detection.
-They introduced Discrete Cosine Transform (DCT) fingerprinting for general or local text reuse detection with high accuracy and efficiency \cite{seo:dct}.
-
-Zhang et al.
-presented partial duplicate detection algorithm using sequence matching that transforms partial-duplicate detection task into three MapReduce jobs: 1.Indexing, 2.Sequence Duplicate Detection, 3.Sequence Matching \cite{zhang:pdc}.
-
-Hajishirzi et al.
-introduced an adaptive near-duplicate detection (ANDD) method by extending term-weighting framework to learn k-gram vectors.
-Provided that each document was represented by an informative real k-gram vector, similarity measures were computed to come up with predicted values of near-duplicates \cite{hajishirzi:andd}.
-
-Lin described three MapReduce algorithms for computing pairwise similarity on document collections \cite{lin:brute}.
-\begin{enumerate}[noitemsep,nolistsep]
-\item Based on brute force.
-\item Treated as large-scale ad hoc retrieval.
-\item Based on Cartesian product of postings lists.
-\end{enumerate}
-
-Manku et al.
-used Charikar's fingerprinting technique for developing near-duplicate detection system.
-They presented an algorithmic technique for identifying existing f-bit fingerprints that differ from a given fingerprint in at most k bit-positions, for small k.
-They demonstrated that their system is useful not only for batch but also for online processing \cite{manku:web}.
-
-Bendersky et al.
-examined two information flow representations: the timeline and the link graph.
-They proposed several simple unsupervised techniques for timeline construction link graph analysis \cite{bendersky:timeline}.
-
-In order to handle large Wikipedia dumps with the order of tens or hundreds of gigabytes and even a few terabytes, we used MapReduce framework in this work, that was introduced by Dean and Ghemawat \cite{dean:mapreduce}.
-
-\section{Algorithm Utilizing Locality \\ Sensitive Hashing}
+\section{Locality \\ Sensitive Hashing}
 
@@
 
-\subsection{Jaccard Similarity and Edit Distance}
-
-%Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
-A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \cite{Kirsch06distance-sensitivebloom}.
-
-In order to estimate Jaccard similarity of sentences $X$ and $Y$ in terms of edit distance we assume that $X$ and $Y$ are both of length $N$ and that their shingle sets are of maximum size (i.e.
-all shingles are unique).
-Also assume that $X$ and $Y$ have edit distance $e$.
-We limit type of edits to changing characters in place.
-Additionally, to simplify our calculations, we assume that edits are localized so that no shingle overlaps more than one edit.
-
-(WLOG) Let $S$ be the set of shingles for X and let $S_o$ be the set of shingles of X that overlap edits.
-The maximum number of unique shingles for a sentence of length $N$ is $N - L + 1 = |S|$.
-Also, we can see that $e \le |S_o| \le e + L - 1$.
-Since edits at the start or end of the sentence will overlap with fewer shingles than edit mid-sentence.
-
-Now we can define $|X \cup Y|$ and $|X \cap Y|$ in terms $S$ and $S_o$ as follows:
-\begin{eqnarray*}
-|X \cap Y| & = & |S| - |S_o| \\
-|X \cup Y| & = & 2*|S_o| + |X \cap Y| \\
-           & = & |S_o| + |S|
-\end{eqnarray*}
-
-Plugging in the values above for $|S_o|$ and $|S|$ we get:
-
-\begin{eqnarray*}
-E + N - L + 1  \le & |X \cup Y| & \le E + N \\
-N - L + 1 - E  \ge & |X \cap Y| & \ge N - 2L - E + 2 \\
-\end{eqnarray*}
-\begin{eqnarray*}
-\frac{N - L - E + 1 }{N - L + e + 1} >= & J(X,Y) & >= \frac{N - 2L - E + 2}{N + E}
-\end{eqnarray*}
-
-Note that, at least under this set of assumptions, the Jaccard similarity is always less than the ``edit similarity'' (1 - normalized edit distance):
-
-\begin{eqnarray*}
-J(X,Y) & <= & \frac{N - E}{E + N - L + 1} - \frac{L - 1}{E + N - L + 1} \\
-       & <= & \frac{N - E}{N} \\ 
-       & =  & 1 - \frac{E}{N}
-\end{eqnarray*}
-
-Finally we can divide through the equations for J(X,Y) by N, which gives us:
-
-\begin{eqnarray*}
-\frac{1 - l - e}{1 - l + e} >= J(X,Y) >= \frac{1 - 2l - e}{1 + e}
-\end{eqnarray*}
-
-where $l$ is relative shingle size and $e$ is normalized edit distance.
-
-Note that as relative shingle size goes to 0 there is a nice convergence for Jaccard similarity:
-\[\lim_{l->0}J(X,Y) = \frac{1 - e}{1 + e}\]
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
-\caption{Jaccard Similarity vs. normalized edit distance.}
-\label{jac-ed}
-\end{figure}
-
-As we would expect, Jaccard similarity decreases as edit distance increases, but it also decreases as shingle length increases.
-Figure \ref{jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$.
-At $l = .05$ and $e = .2$ our estimate for Jaccard similarity has already fallen to the range [0.58,0.65].
-Clearly setting $l$ too high can increase the false positive rate, but setting $l$ too low will increase the false positive rate, since it will increase the size of the intersection of the shingle sets.
-
-\subsection{False positives}
-
-In order to estimate the affect of shingle length on false positive rate we ran a number of experiments for a 1 G collection of wikipedia documents.
-For fixed $N=10$ we ran experiments for three values of $K=\{8,9,10\}$ and $8 \le L \le 16$.
-Setting a normalized edit distance threshold of $e = .25$, we calculated the total number of ''good'' ($e <= .25$) and ''bad'' ($e > .25$) (unique) sentence pairs as well as the false positive rate (\# bad pairs divided by the total number of sentences).
-Results are presented in Figure \ref{ed-grid}.
-
-As we might expect, as shingle length increases, the false positive rate decreases.
-However, the total number of good pairs also decreases, implying that our false negative rate is also increasing.
-When applying these techniques, increased recall will come at the price of decreased precision.
-Because of this, in a real implementation, it would likely be desirable to set requirements for recall, then use secondary filtering to increase precision.
-For example, actual edit distance could be applied as a secondary filter.
-
-\begin{figure}
-\centering
-\epsfig{file=edgridl.eps,width=3.5in}
-\caption{False Positive Rate, Good Count, Bad Count for $N=10, K \in \{8,9,10\}, 5 \le L \le 15$}
-\label{ed-grid}
-\end{figure}
-
 \section{Experiments and Discussion}
-
-%We performed several analyses to provide more insight into the occurence of duplicate sentences.
-In particular, we were interested in detecting similar sentences that arose from copying text from one article to another since such instances would represent content that is either redundant, or content that has diverged in the sense that either the original or the copy was edited for clarification of factual correctness and the other was not.
-Such instances give insight into the Wikipedia editing process, and also represent an opportunity to improve article quality on Wikipedia by identifying places where further editing or article merging may be needed.
-
-All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 7/2013) obtained from dumps.wikimedia.org.
-The enwiki dump is approximately 42G in size and contains 10,218,778 articles (after excluding certain non-article page types).
-Running our application on the enwiki dump on a shared cluster of 16 nodes (20 GB RAM and 4?
-cores each) took $\approx$ 25 minutes.
-
-The total number of similar sentence clusters was 1,151,640, including 3,496,074 article/sentence pairs over 1,091,804 article titles.
-The total number of unique sentences over all clusters was 2,361,886.
-
-Cluster sizes ranged from 2 to 42,901.
-(See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, about 99\% of our clusters have size below or equal to 10, but about 1/4 of the output sentence/article pairs fall into clusters with size greater than 10.
-One explanation for this distribution of sentences is the phenomenon we call ''templatification,'' which we describe in more detail below.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
-\caption{Histogram of Cluster Sizes (for cluster size $< 300$, log scale).}
-\label{clust}
-\end{figure}
-
-\subsection{Similar Sentence Types}
-
-Manual inspection of cluster output reveals several different similar sentence types. These types can be summarized as follows:
-
-\begin{itemize}
-\item Templatification
-\item References
-\item Direct Copying
-\item Direct Copying with Copy Editing
-\item Direct Copying with Factual Drift
-\end{itemize}
-
- \emph{Templatification} occurs when one sentence is an exact duplicate of another sentence, but the main topic has been changed by only a few pieces of key information having been modified.
-For example, it could be said that the following two sentences follow a particular \emph{template}.
-\begin{itemize}[noitemsep,nolistsep]
-
-\item Of the agricultural land 40.4\% is used for growing crops and 26.6\% is pastures while 2.2\% is used for orchards or vine crops. [Gondiswil]
-\item Of the agricultural land 26.1\% is used for growing crops and 30.2\% is pastures while 3.0\% is used for orchards or vine crops. [Kleindietwil]
-\item Of the agricultural land 37.8\% is used for growing crops and 35.5\% is pastures while 2.2\% is used for orchards or vine crops. [Leimiswil]
-
-\end{itemize}
-From the perspective of editing/writing Wikipedia articles, this is a strong indicator that the author copied the original sentence and modified the relevant information to pertain to a different topic.
-What remains shared between both sentences though is the inherent structure.
-
-\emph{Direct Copying} occurs when the same sentence has been copied into another (or possibly the same) article.
-This can happen for many reasons, including articles that deal with similar subjects, or articles that are subtopics of other topics Similarly, \emph{Direct Copying with Copy Editing} occurs when the same sentence has been copied into another article and then one or both sentences has been edited for style or clarity.
-For example:
-\begin{itemize}[noitemsep,nolistsep]
-\item In dry areas it may only emerge from its burrow for a few weeks when conditions are right and usually at night but in areas with permanent water bodies and abundant rain it may be active all day.
-[Great Plains toad]
-\item In dry areas it may only emerge from its burrow for a few weeks when conditions are right and only at night but in areas with permanent water bodies and abundant rain it may be active all day.
-[List of amphibians and reptiles of Montana]
-\end{itemize}
-
-\emph{Factual drift} most notably occurs when the same sentence has been copied and a piece of factual information about the \emph{same} topic has changed.
-For example, factual drift can be seen in the following two sentences.
-\begin{itemize}[noitemsep,nolistsep]
-\item The color of the upper rim of an astronomical object could go from green to blue to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
-[Green flash]
-\item The color of the upper limb of an astronomical object could go from blue to green to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
-[Mirage of astronomical objects]
-\end{itemize}
-Although factual drift is similar to copy editing and may occur along with copy editing, we distinguish the two cases since factual errors are more severe than style issues.
-
-\emph{References} refers to citations, typically occurring at the end of a Wikipedia article.
-Since Wikipedia does not adhere to one single citation style, the same work may be referenced on multiple pages in different styles.
-Similarly different portions of the same work may be referenced in different articles.
-Although citation errors might be harder to distinguish from factual errors, errors in citation are arguably no less important.
-(It would also be interesting to compare whether articles that share similar sentences also share similar citations.)
-
-\begin{itemize}[noitemsep,nolistsep]
-\item Neotropical Ichthyology 11 (1): 73-80.
-\item Neotropical Ichthyology 10 (2): 245-253.
-\end{itemize}
-
-\subsubsection{Breakdown of Sentence Types and Filtering}
-
-By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table \ref{counts}.
-The manual analysis reveals that $\approx 75\%$ of the clusters identified are either in the \emph{identical} or the \emph{template} classes.
-We argue that these classes are less interesting, since they represent either large collections of identically formatted and very specific facts, or content that is exactly the same, and such content is at least internally consistent, if redundant, and less likely to contain errors.
-Thus they are candidates for filtering out of the result set.
-
-\begin{table}
-\centering
-\caption{Sentence Breakdown Counts}
-\begin{tabular}{| l | c | c |}
-\hline
-Factual Drift & 121 & 5.78\% \\ \hline
-Template & 632 & 30.18\% \\ \hline
-Reference & 7 & 0.33\% \\ \hline      
-Copy Edit & 283 & 13.51\% \\ \hline
-Identical & 948 & 45.27\% \\ \hline
-Other & 103 & 2.92\% \\ \hline
-\hline
-\end{tabular}
-\label{counts}
-\end{table}
-
-Identical clusters are easy to identify through exact hashing.
-In order to get a rough filter for template clusters, we develop a heuristic score on low frequency words in the cluster word set.
-For our purposes a low-frequency word is one that occurs in less than half of the cluster sentences.
-The score we use is:
-\[(\#numeric + \#proper)/(\#numeric + \#proper + \#other)\]
-Where \#numeric is the number of numeric terms in the cluster word set (all unique low frequency words occuring in the cluster), \#proper is the number of proper nouns in the cluster word set (i.e.
-capitalized words), and \#other is the number of other words.
-
-Applying the score to our hand-classified clusters we see (Figure \ref{heuristic}) that this score does separate between template and non-template clusters.
-(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.)
-
-After applying the score to the entire set of wiki clusters (with a score threshold of .6), we identify 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
-The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196 sentences.
 
@@
 
-\subsection{Sentence Similarity as a Measure of Article Similarity}
-
- For clarity purposes, we define \emph{similarity count} as simply the total number of unique sentences between two articles that were found to share the same hash signature.
-Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure.
-Overall, we found $91,591$ wikipedia article paris that had a similarity count greater than or equal to $25$ and $29,582$ wikipedia article pairs that had a similarity count greater than or equal to $50$, and $\approx 6331$ Wikipedia articles with similarity count greater than or equal to $75$.
-If we perform the same similarity analysis, but filter clusters using the template heuristic described above, we find $5950$ article pairs with similarity count greater than or equal to $25$, $472$ article pairs with similarity greater than or equal to $50$ and $159$ article pairs with similarity greater than or equal to $75$.
-Table \ref{toparticlegroups}) shows the top similar article groups with similarity count greater than 100 (where pairs sharing an element have been merged).
-
-\begin{figure*}[hp!]
-\centering
-\caption{Top Similar Article Groupings, Similarity Count $\ge$ 100}
-{\small
-\begin{tabular}{| l |}
-    \hline
-\{Hindi Cinema, Bollywood\} \\
-\{Telecommunications in the People's Republic of China, Telecommunications in China\} \\
-\{Private equity in the 2000s, History of private equity and venture capital\} \\
-\{List of ethnic cleansings, Ethnic cleansing\} \\
-\{Route of the Oregon Trail, Oregon Trail\} \\
-\{English literature, British literature\} \\
-\{Maritime history of the United States (1900–99), History of the United States Merchant Marine\} \\
-\{Culture of the United States, Society of the United States\} \\
-\{Halifax (former city), History of the Halifax Regional Municipality\} \\
-\{List of SNK characters, List of The King of Fighters characters\} \\
-\{Toronto Blue Jays, History of the Toronto Blue Jays\} \\
-\{History of Christianity in the United States, History of Protestantism in the United States\} \\
-\{Sri Ranganathaswamy Temple, Srirangam, Šri Ranganata Svami hram\} \\
-\{Individualist anarchism in Europe, Individualist anarchism\} \\
-\{Nutritional neuroscience, Nutrition and cognition\} \\
-\{Jesse Hubbard and Angie Baxter, The Hubbard Family\} \\
-\{History of the Dallas Mavericks, Dallas Mavericks\} \\
-\{Imperial Crypt Vaults, Imperial Crypt\} \\
-\{History of the Roman Empire, Byzantine Empire, History of the Byzantine Empire\} \\
-\{May Bukas Pa, List of May Bukas Pa episodes\} \\
-\{Myth: The Fallen Lords, Myth (series)\} \\
-\{Individualist anarchism in the United States, Anarchism in the United States\} \\
-\{Native Americans in the United States, Native American cultures in the United States\} \\
-\{Hockey stick controversy, Hockey stick graph\} \\
-\{Vancouver Canucks, History of the Vancouver Canucks\} \\
-\{Silvio Berlusconi, Controversies surrounding Silvio Berlusconi\} \\
-\{Los Angeles Angels of Anaheim, History of the Los Angeles Angels of Anaheim\} \\
-\{2007 suicide bombings in Iraq, List of terrorist incidents in Iraq in 2007\} \\
-\{List of Canadian tornadoes and tornado outbreaks, List of 21st-century Canadian tornadoes and tornado outbreaks\} \\
-\{Scotland in the modern era, History of Scotland\} \\
-\{Libertarian socialism, Libertarian Marxism\} \\
-\{Canti (Leopardi), Giacomo Leopardi\} \\
-\{Jayne Torvill, Christopher Dean, Torvill and Dean\} \\
-\{Government of Mahmoud Ahmadinejad (2005–present), Foreign policy of Mahmoud Ahmadinejad, Mahmoud Ahmadinejad\} \\
-\{Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages\} \\
-\{Go Nagai bibliography, Go Nagai\} \\
-\{Galvatron, Megatron\} \\
-\{History of Australia (1901–45), History of Australia\} \\
-\{Interracial marriage, Miscegenation\} \\
-\{List of Prison Break recurring characters, List of Prison Break minor characters\} \\
-\{History of Eastern Orthodox Christian theology, History of the Orthodox Church\} \\
-\{69th Infantry Regiment (United States), 69th Infantry Regiment (New York)\} \\
-\{The Anarchy, Stephen, King of England\} \\
-\{History of painting, Western painting, 20th-century Western painting\} \\
-\{Sino-Pacific relations, Foreign relations of China\} \\
-\{History of the East–West Schism, East–West Schism\} \\
-\{History of the Detroit Tigers, Detroit Tigers\} \\
-\{San Francisco Giants, History of the San Francisco Giants\} \\
-\{Hernán Cortés, Oconahua, Jalisco\} \\
-\{List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)\} \\
-\{Port of Tianjin operations and logistics, Port of Tianjin\} \\
-\{American rock, Rock music\} \\
-\{One-Day Internationals in England in 2005, Test matches in England in 2005, Australian cricket team in England in 2005\} \\
-\{History of Christianity, History of Christianity of the Middle Ages\} \\
-\{History of the Texas Rangers (baseball), Texas Rangers (baseball)\} \\
-\{List of Irish Americans, List of Americans of Irish descent\} \\
-\{Radeon HD 3000 Series, R600 (ASIC)\} \\
-\{Robert Edmund Strahorn, Battle of Slim Buttes\} \\
-\{Cleveland Indians, History of the Cleveland Indians\} \\
-\{CIA leak scandal criminal investigation, Plame affair grand jury investigation\} \\
-\{History of Western civilization, History of Western civilization before AD 500\} \\
-\{Benigno Aquino III, Presidency of Benigno Aquino III\} \\
-\{Kingdom of Greece, History of modern Greece\} \\
-\{List of Russian people, List of Russian scientists\} \\
-\hline
-\end{tabular}
-}
-\label{toparticlegroups}
-\end{figure*}
-
 \section{Conclusions and Future Work}
-
-Although the LSH technique of minhashing does not perfectly approximate edit distance, we have demonstrated that, when implemented in the Hadoop framework, it is an efficient method for identifying large numbers of Wikipedia sentences that are near duplicates.
-Additionally, we demonstrated that it is possible to apply a simple heuristic and to filter sentences that result from templatification, which make up about half (by our heuristic scoring) of the sentences identified in the similar sentence analysis.
-Because templatification appears quite often as almanac-like lists of facts, quite possibly generated with automated ``bots'' given the large scale of some templatified clusters, it is a worthwhile exercise to identify and quantify such content as distinct from other content found on the Wikipedia site.
-
-Although sentences can be used as a measure of article similarity, identifying similarity at the sentence level allows greater flexibility for finding similar content across documents than a whole document analysis.
-These techniques could be used to automatically suggest corrections to Wikipedia, or to improve plagiarism detection across web content in general.
-
-Future work could investigate revision histories of articles and correlate similar sentence with article edit timestamps to better relate similarities on a temporal dimension.
-An analysis on a multi-sentence level could identify more similarities where user edits change sentence boundaries by merging or breaking up content which our present analysis would not detect.
-Additionally, a more sophisticated template detection heuristic could be developed, as the one used here is a very rough measure that makes assumptions specific to English language text.
-
-\section{Acknowledgments}
-We would especially like to thank Dr. Jimmy Lin for his advise and directions.
 

### 2013-12-07 article/clarticle/article-draft.tex
Working on new article

@@
 
+\section{Cross-lingual Similarity at the Sentence Level}
+
+We assume a model where a document is represented by a set of features.
+In the single language case the set of features is typically taken directly from the text of a document, either breaking up text on non-word boundaries (a ``bag of words'') or by apply a sliding window technique to create a set of equal-length document ``shingles'' (ref?).
+In cross-language similarity matching, the set of features for a document can no longer be extracted directly from the text, since there is no reason to assume that documents across languages share text features.
+One approach to the problem would be to pick a larget language $E$ and use machine translation to convert all documents into $E$ then proceed as in the single language case.
+The problem with this approach is that most language models are probabilistic, resulting in many possible translations for each document.
+Also, there is evidence that translation approaches do not significantly out perform CLIR techniques, which are generally less computationally expensive than machine translation techniques (REF).
+Finally, in order to build a machine translation model, it is often necessary to produce sets of parallel text, for which one would need a similarity measure, so it does not always make sense for document similarity matching techniques to depend on accurate translation models already existing.
+
+For the purposes of this work, our input documents are sentence, which allows us finer granularity in information retrieval than at the article level.
+Although the sentence level is somewhat arbitrary, it is generally a reliable way to break up documents, since most documents are composed in sentences, and sentences can be reliably extracted from text using regular expression matching for many languages.
+We use the signature based minhashing technique.
+In order to achieve cross language comparison we map each document word set into our target language by using a word-based language model for which we know $p(e|f)$, the conditional probability of a target language word $e$ being the translation of a foreign language word $e$.
+For each foreign word sentence we map the sentence into a set of words $S_F$.
+For each $f \in S_F$ we sample from the set of possible translations according to the distribution $p(f|e)$.
+We repeat this process $N$ times to get $N$ possible word sets (for some fixed $N$).
+These ``translated'' word sets are then each used as input into the minhash signature generation process.
+Although this approach is simplistic, it requires only a single pass over the input document set to process \emph{document} $\rightarrow$ \emph{sentence} $\rightarrow$ \emph{word set} $\rightarrow$ \emph{set of translated word sets}.
+
 \section{Locality \\ Sensitive Hashing}
@@
 A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
-(In our case, input ''documents'' are individual sentences found within the content of Wikipedia articles.) Each document is broken up into n-gram ``shingles'' and for each shingle set $S$ a set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family is produced.
+For each input feature set $S$ (in our case a set of words or translated words) a vector $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family is produced.
 The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes.
@@
 
-%% \subsection{Design}
-%% Many signature techniques such as LSH are embarrassingly parallel. In our project, we designed our algorithm around the MapReduce framework.
-
-%% Because the minhash technique is parametrized by several variables, including shingle length, signature size, and number of signatures to be calculated per document, these values can also be considered as inputs for the MapReduce algorithm.
-
-%% \begin{table}
-%% \begin{algorithm}[H]
-%% \caption{Minhash MapReduce Pseudocode}
-%% \begin{algorithmic}
-%% \Function{initialize}{}
-%% %\Comment{configure and set up algorithm parameters}
-%%  \State $F \gets $ hash family;
-%%  \State $L \gets $ shingle length;
-%%  \State $K \gets $ vector length;
-%%  \State $N \gets $ number of signatures to emit;
-%% \EndFunction
-
-%% \Function{map}{docid $d$, wikipage $p$}
-%%  \State sentencect $\gets 0$
-%%  %\Comment {Break up article text into sentence}
-%%  \While{$s \gets$ nextSentence($p$)}
-%%   %\Comment{Break up sentence into shingles}
-%%   \State shingles $\gets$ shingleSet($s$,$L$);
-%%   \State minhashes = new List(|F|);
-%%    \For{$i \gets 1 \ldots |F|$}
-%%     \State minhashes[$i$] $\gets \infty$;
-%%    \EndFor
-%%    %\Comment{Calculate set of minhash signature for each sentence}
-%%    \For{$g \in$ shingles}
-%%     \For{$i \gets 1 \ldots |F|$}
-%%      \State minhashes[$i$] $\gets$ min($F_i(g)$,minhashes[$i$]);
-%%     \EndFor
-%%    \EndFor
-%%    %\Comment{Emit $N$ $K$-length signatures}
-%%   \For{$i \gets 1 \ldots N$}
-%%    \State sig = select($K$, minhahses);
-%%    \State emit(sig,(docid,sentencect));
-%%   \EndFor
-%%   \State  sentencect++;
-%%  \EndWhile
-%% \EndFunction
-
-%% \Function{reduce}{signature sig, sentenceids $S$}
-%% \If{$|S| > 1$}
-%% \State emit(sig, $S$);
-%% \EndIf
-%% \EndFunction
-%% \end{algorithmic}
-%% \end{algorithm}
-%% \end{table}
-
 \subsection{Implementation Details}
 
-Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 (\url{https://github.com/lintool/Cloud9}) and WikiClean (\url{https://github.com/lintool/wikiclean/}) libraries for parsing Wikipedia page text from the Wikipedia XML dump format.
-An open source implementationis available on Github (\url{https://github.com/seweissman/wikiduper}).
-
-%Sentences are parsed out over each document using a regular expression.
-Sentences that are too large or too small are discarded.
-The family of hash functions is implemented using a ``Multiply Shift'' (\url{http://en.wikipedia.org/wiki/Universal_hashing}) hashing scheme and is generated from a random seed using the Java Random class.
-The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
-
-\section{Parameter Tuning}
-
-The minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
-Each of these parameters has an impact on the error rates in the minhash output.
+Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 (\url{https://github.com/lintool/Cloud9}), Ivory  and WikiClean (\url{https://github.com/lintool/wikiclean/}) libraries for parsing Wikipedia page text from the Wikipedia XML dump format.
+An open source implementation is available on Github (\url{https://github.com/seweissman/wikiduper}).
 

### 2013-12-07 src/main/wikiduper/clir/minhash/JaccardCompare.java

@@ -166,12 +166,12 @@ public class JaccardCompare extends Configured implements Tool {
             IntWritable eLineId = new IntWritable();
             ArrayListWritable<Text> eSentence = new ArrayListWritable<Text>();
             for(int i=0;i<nSentences;i++){
-                System.out.println("eLine " + i);
+                if(i%100 == 0) System.out.println("eLine " + i);
                 //eLineNum.set(2*i);
-              ArrayListOfIntsWritable transIdList = sentence2translation.get(2*i);
-              //ArrayListOfIntsWritable transIdList = new ArrayListOfIntsWritable();
+                ArrayListOfIntsWritable transIdList = sentence2translation.get(2*i);
+                //ArrayListOfIntsWritable transIdList = new ArrayListOfIntsWritable();
                 //sentence2translationReader.get(eLineNum, transIdList);
-               // System.out.println("transIdList " + transIdList);
+                // System.out.println("transIdList " + transIdList);
                 for(int j=0;j<nSentences;j++){
                   // System.out.println("fLine " + j);
                   ArrayListWritable<Text> fSentence = id2sentence.get((2*j+1)*nSamples);

### 2013-12-07 src/main/wikiduper/clir/minhash/MinhashCLIR.java

@@ -135,17 +135,17 @@ public class MinhashCLIR extends Configured implements Tool {
                     for(int i=0; i<K; i++){
                         outsig.add(i, 0);
                     }
-                    System.out.print("tokens : ");        
+                    //System.out.print("tokens : ");        
                     for(int i=0; i<K; i++){
                         int x = r.nextInt(nHash);
                         outsig.set(i, minhash[x]);
-                        System.out.print(hashval[x] + " " );
+                        //System.out.print(hashval[x] + " " );
                     }
-                    System.out.println();
+                    //System.out.println();
                     //System.out.println("fsig " + outsig);
                     output.collect(outsig, key);
-                    System.out.println("outsig: " + outsig);
-                    System.out.println("outid: " + key);
+                    //System.out.println("outsig: " + outsig);
+                    //System.out.println("outid: " + key);
                 }
             //}
 

### 2013-12-08 article/clarticle/article-draft.tex
Article updates

@@
 
-\numberofauthors{3}
+\numberofauthors{1}
 
@@
 
-\section{Locality \\ Sensitive Hashing}
+Following Ture, et.
+al 2011 [ref], we use parallel German and English texts from the Europarl corpus, which contains proceedings from the European Parliament (1996— 2009), to compare empirically the performance of cross-language minhashing to signature matching on a machine translated text.
+(Here our machine translation tool is the Google Translate web tool.)  In the first case we translat each German sentence into English and then process the resulting sentences using a straightforward minhash signature algorithm.
+In the second case, we use our sampling approach to create a number of possible documents, each which gets input into the minhash algorithm.
+We then calculated Jaccard similarity for the translated document pairs.
+Figure \ref{mtclircompare} shows the two distributions of Jaccard similarity scores for each document set, comparing matches and non-matches.
+We can see that the sampling approach performs similarity to the translation approach, finding documents that are similar under machine translation nearly as well as if we had compared the translated texts.
 
-In order to measure document similarity we use a common LSH technique known as MinHash (\cite{broder:resemblance}).
+\begin{figure}
+\centering
+\includegraphics[width=3.5in, keepaspectratio = true]{clirhist.pdf}
+\includegraphics[width=3.5in, keepaspectratio = true]{transhist.pdf}
+\caption{Histograms of Europarl Matches by Jaccard Similarity for both CLIR and translation technique.}
+\label{mtclircompare}
+\end{figure}
+
+\section{Signature Techniques}
+
+In order to measure document similarity we use a common signature technique known as minhash (\cite{broder:resemblance}).
 A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
@@
 
+In order to compare the effectiveness of our cross-language minhashing approach we compare the technique to a second signature technique, random projections as described in Ture, et. al 2011 [ref].
+
 \subsection{Implementation Details}
@@
 An open source implementation is available on Github (\url{https://github.com/seweissman/wikiduper}).
+
+In order to run our tests we use the Random Projections code made available as part of the Ivory library (link).
 

### 2013-12-08 src/main/wikiduper/utils/BruteForcePwsim.java
Utilities for sampling and testing minhash output

@@ -1,0 +1,715 @@
+package wikiduper.utils;
+
+import ivory.core.tokenize.Tokenizer;
+import ivory.core.tokenize.TokenizerFactory;
+
+import java.io.EOFException;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Random;
+import java.util.Set;
+import java.util.TreeMap;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.GnuParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.ParseException;
+import org.apache.hadoop.conf.Configured;
+import org.apache.hadoop.fs.FSDataInputStream;
+import org.apache.hadoop.fs.FileSystem;
+import org.apache.hadoop.fs.Path;
+import org.apache.hadoop.io.SequenceFile;
+import org.apache.hadoop.io.Text;
+import org.apache.hadoop.mapred.FileInputFormat;
+import org.apache.hadoop.mapred.FileOutputFormat;
+import org.apache.hadoop.mapred.JobClient;
+import org.apache.hadoop.mapred.JobConf;
+import org.apache.hadoop.mapred.MapReduceBase;
+import org.apache.hadoop.mapred.Mapper;
+import org.apache.hadoop.mapred.OutputCollector;
+import org.apache.hadoop.mapred.Reporter;
+import org.apache.hadoop.mapred.Reducer;
+import org.apache.hadoop.mapred.SequenceFileInputFormat;
+import org.apache.hadoop.mapred.SequenceFileOutputFormat;
+import org.apache.hadoop.util.Tool;
+import org.apache.hadoop.util.ToolRunner;
+import org.apache.log4j.Logger;
+
+import wikiduper.hash.MultiplyShiftHash;
+import wikiduper.utils.DocSentence;
+import wikiduper.utils.Signature;
+import edu.umd.cloud9.io.array.ArrayListWritable;
+import edu.umd.cloud9.io.map.HMapSIW;
+import edu.umd.cloud9.io.pair.PairOfFloatInt;
+import edu.umd.cloud9.io.pair.PairOfLongInt;
+import edu.umd.cloud9.io.pair.PairOfLongString;
[…]

### 2013-12-08 src/main/wikiduper/utils/SampleSentences.java

@@ -1,0 +1,195 @@
+package wikiduper.utils;
+
+import java.io.IOException;
+import java.util.HashSet;
+import java.util.Random;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.GnuParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.ParseException;
+import org.apache.hadoop.conf.Configured;
+import org.apache.hadoop.fs.FileSystem;
+import org.apache.hadoop.fs.Path;
+import org.apache.hadoop.hdfs.tools.GetConf;
+import org.apache.hadoop.mapred.Counters;
+import org.apache.hadoop.mapred.FileInputFormat;
+import org.apache.hadoop.mapred.FileOutputFormat;
+import org.apache.hadoop.mapred.JobClient;
+import org.apache.hadoop.mapred.JobConf;
+import org.apache.hadoop.mapred.JobID;
+import org.apache.hadoop.mapred.MapReduceBase;
+import org.apache.hadoop.mapred.Mapper;
+import org.apache.hadoop.mapred.OutputCollector;
+import org.apache.hadoop.mapred.Reporter;
+import org.apache.hadoop.mapred.RunningJob;
+import org.apache.hadoop.mapred.SequenceFileInputFormat;
+import org.apache.hadoop.mapred.SequenceFileOutputFormat;
+import org.apache.hadoop.util.Tool;
+import org.apache.hadoop.util.ToolRunner;
+import org.apache.log4j.Logger;
+
+import edu.umd.cloud9.io.pair.PairOfLongInt;
+import edu.umd.cloud9.io.pair.PairOfStrings;
+
+public class SampleSentences extends Configured implements Tool {
+    private static final Logger LOG = Logger.getLogger(SampleSentences.class);
+
+    private static class SampleMapper extends MapReduceBase implements
+    Mapper<PairOfLongInt, PairOfStrings, PairOfLongInt, PairOfStrings> {
+
+        static long rseed;
+        static Random r;
+        static String sampleLang;
+        static long limit;
+        static long count;
+
+        public void map(PairOfLongInt key, PairOfStrings p, OutputCollector<PairOfLongInt, PairOfStrings> output,
+                    Reporter reporter) throws IOException {
+            
+            String lang = p.getLeftElement();
[…]

### 2013-12-08 src/main/wikiduper/utils/SampleSentences.java
Fixing error with getting job id

@@ -91,7 +91,7 @@ public class SampleSentences extends Configured implements Tool {
         options.addOption(OptionBuilder.withArgName("lang")
                 .hasArg().withDescription("language to sample from").create(SAMPLE_LANG));
         options.addOption(OptionBuilder.withArgName("int")
-                .hasArg().withDescription("language to sample from").create(SAMPLES));
+                .hasArg().withDescription("number of samples").create(SAMPLES));
         
         CommandLine cmdline;
         CommandLineParser parser = new GnuParser();
@@ -156,7 +156,7 @@ public class SampleSentences extends Configured implements Tool {
         JobClient.runJob(conf);
         String jobID = args[0];
         JobClient jobClient = new JobClient(new JobConf(getConf())); 
-        RunningJob job = jobClient.getJob(JobID.forName(jobID));
+        RunningJob job = jobClient.getJob(JobID.forName(conf.getJobName()));
         Counters counters = job.getCounters();
         long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_RECORDS);
         

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Fixing error with getting job id

@@ -153,10 +153,8 @@ public class SampleSentences extends Configured implements Tool {
         Path outputDir = new Path("tmppath");
         FileSystem.get(conf).delete(outputDir, true);
         
-        JobClient.runJob(conf);
-        String jobID = args[0];
-        JobClient jobClient = new JobClient(new JobConf(getConf())); 
-        RunningJob job = jobClient.getJob(JobID.forName(conf.getJobName()));
+        RunningJob job = JobClient.runJob(conf);
+
         Counters counters = job.getCounters();
         long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_RECORDS);
         

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Debugging

@@ -157,6 +157,7 @@ public class SampleSentences extends Configured implements Tool {
 
         Counters counters = job.getCounters();
         long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_RECORDS);
+        LOG.info(" Count from job 1 = " + count);
         
         // Job 2
 

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Debugging

@@ -69,6 +69,8 @@ public class SampleSentences extends Configured implements Tool {
                 limit = 1;
             }
             limit = count/nSamples;
+            System.out.println("COUNTER CONFIG " + limit + " " + count + " " + nSamples);
+
         }
 
         

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
added missing call to get conf var for language

@@ -1,7 +1,6 @@
 package wikiduper.utils;
 
 import java.io.IOException;
-import java.util.HashSet;
 import java.util.Random;
 
 import org.apache.commons.cli.CommandLine;
@@ -14,13 +13,11 @@ import org.apache.commons.cli.ParseException;
 import org.apache.hadoop.conf.Configured;
 import org.apache.hadoop.fs.FileSystem;
 import org.apache.hadoop.fs.Path;
-import org.apache.hadoop.hdfs.tools.GetConf;
 import org.apache.hadoop.mapred.Counters;
 import org.apache.hadoop.mapred.FileInputFormat;
 import org.apache.hadoop.mapred.FileOutputFormat;
 import org.apache.hadoop.mapred.JobClient;
 import org.apache.hadoop.mapred.JobConf;
-import org.apache.hadoop.mapred.JobID;
 import org.apache.hadoop.mapred.MapReduceBase;
 import org.apache.hadoop.mapred.Mapper;
 import org.apache.hadoop.mapred.OutputCollector;
@@ -64,12 +61,12 @@ public class SampleSentences extends Configured implements Tool {
             rseed = job.getLong("rseed", 112345);
             r = new Random(rseed);    
             count = job.getLong("count", 1000000);
+            sampleLang = job.get("sampleLang","de");
             int nSamples = job.getInt("nSamples", 1000000);
             if(nSamples > count){
                 limit = 1;
             }
             limit = count/nSamples;
-            System.out.println("COUNTER CONFIG " + limit + " " + count + " " + nSamples);
 
         }
 
@@ -142,7 +139,7 @@ public class SampleSentences extends Configured implements Tool {
         conf.setOutputValueClass(PairOfStrings.class);
 
         // Job 1
-        conf.setJobName(String.format("SampleSentences-2[%s: %s]", OUTPUT, outputPath));
+        conf.setJobName(String.format("SampleSentences-1[%s: %s]", OUTPUT, outputPath));
 
         conf.setNumMapTasks(20);
         conf.setNumReduceTasks(0);

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Debugging

@@ -67,7 +67,6 @@ public class SampleSentences extends Configured implements Tool {
                 limit = 1;
             }
             limit = count/nSamples;
-
         }
 
         
@@ -156,8 +155,12 @@ public class SampleSentences extends Configured implements Tool {
 
         Counters counters = job.getCounters();
         long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_RECORDS);
+        long splitbytes = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.SPLIT_RAW_BYTES);
+        long bytes = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_BYTES);
+        long maps = bytes/splitbytes;
         LOG.info(" Count from job 1 = " + count);
-        
+        LOG.info(" Number of maps from job 1 = " + count);
+        LOG.info(" Split guess = " + maps);
         // Job 2
 
         conf.setLong("rseed", 1123456);

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Debugging

@@ -25,6 +25,7 @@ import org.apache.hadoop.mapred.Reporter;
 import org.apache.hadoop.mapred.RunningJob;
 import org.apache.hadoop.mapred.SequenceFileInputFormat;
 import org.apache.hadoop.mapred.SequenceFileOutputFormat;
+import org.apache.hadoop.mapreduce.JobCounter;
 import org.apache.hadoop.util.Tool;
 import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
@@ -155,12 +156,9 @@ public class SampleSentences extends Configured implements Tool {
 
         Counters counters = job.getCounters();
         long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_RECORDS);
-        long splitbytes = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.SPLIT_RAW_BYTES);
-        long bytes = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_BYTES);
-        long maps = bytes/splitbytes;
+        long maps = counters.getCounter(JobCounter.TOTAL_LAUNCHED_MAPS);
         LOG.info(" Count from job 1 = " + count);
-        LOG.info(" Number of maps from job 1 = " + count);
-        LOG.info(" Split guess = " + maps);
+        LOG.info(" Maps = " + maps);
         // Job 2
 
         conf.setLong("rseed", 1123456);

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Added job to count only chosen language for sentence sampling code

@@ -36,6 +36,30 @@ import edu.umd.cloud9.io.pair.PairOfStrings;
 public class SampleSentences extends Configured implements Tool {
     private static final Logger LOG = Logger.getLogger(SampleSentences.class);
 
+    private static class LangFilterMapper extends MapReduceBase implements
+    Mapper<PairOfLongInt, PairOfStrings, PairOfLongInt, PairOfStrings> {
+
+        static String sampleLang;
+
+        public void map(PairOfLongInt key, PairOfStrings p, OutputCollector<PairOfLongInt, PairOfStrings> output,
+                    Reporter reporter) throws IOException {
+            
+            String lang = p.getLeftElement();
+            if(lang.equals(sampleLang)){
+                    output.collect(key, p);
+                
+            }
+        }
+        
+
+        public void configure(JobConf job) {
+            sampleLang = job.get("sampleLang","de");
+        }
+
+        
+    }
+
+    
     private static class SampleMapper extends MapReduceBase implements
     Mapper<PairOfLongInt, PairOfStrings, PairOfLongInt, PairOfStrings> {
 
@@ -64,10 +88,11 @@ public class SampleSentences extends Configured implements Tool {
             count = job.getLong("count", 1000000);
             sampleLang = job.get("sampleLang","de");
             int nSamples = job.getInt("nSamples", 1000000);
+            long nMaps = job.getLong("nMaps", 300);
             if(nSamples > count){
                 limit = 1;
             }
-            limit = count/nSamples;
+            limit = count/(nMaps*nSamples);
         }
 
         
@@ -113,7 +138,8 @@ public class SampleSentences extends Configured implements Tool {
 
         String inputPath = cmdline.getOptionValue(INPUT);
         String outputPath = cmdline.getOptionValue(OUTPUT);
-
+        String tmpPath = "tmppath";
+        
         String sampleLang = cmdline.getOptionValue(SAMPLE_LANG);
         int nSamples = Integer.parseInt(cmdline.getOptionValue(SAMPLES));
                 
@@ -137,19 +163,21 @@ public class SampleSentences extends Configured implements Tool {
         
         conf.setOutputKeyClass(PairOfLongInt.class);
         conf.setOutputValueClass(PairOfStrings.class);
+        conf.set("sampleLang", sampleLang);
 
         // Job 1
         conf.setJobName(String.format("SampleSentences-1[%s: %s]", OUTPUT, outputPath));
 
[…]

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
changed ref to input records to output records counter

@@ -47,7 +47,6 @@ public class SampleSentences extends Configured implements Tool {
             String lang = p.getLeftElement();
             if(lang.equals(sampleLang)){
                     output.collect(key, p);
-                
             }
         }
         
@@ -183,7 +182,7 @@ public class SampleSentences extends Configured implements Tool {
         RunningJob job = JobClient.runJob(conf);
 
         Counters counters = job.getCounters();
-        long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_INPUT_RECORDS);
+        long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_OUTPUT_RECORDS);
         long maps = counters.getCounter(JobCounter.TOTAL_LAUNCHED_MAPS);
         LOG.info(" Count from job 1 = " + count);
         LOG.info(" Maps = " + maps);

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
changed ref to input records to output records counter

@@ -25,7 +25,6 @@ import org.apache.hadoop.mapred.Reporter;
 import org.apache.hadoop.mapred.RunningJob;
 import org.apache.hadoop.mapred.SequenceFileInputFormat;
 import org.apache.hadoop.mapred.SequenceFileOutputFormat;
-import org.apache.hadoop.mapreduce.JobCounter;
 import org.apache.hadoop.util.Tool;
 import org.apache.hadoop.util.ToolRunner;
 import org.apache.log4j.Logger;
@@ -65,7 +64,7 @@ public class SampleSentences extends Configured implements Tool {
         static long rseed;
         static Random r;
         static String sampleLang;
-        static long limit;
+        static long nSamples;
         static long count;
 
         public void map(PairOfLongInt key, PairOfStrings p, OutputCollector<PairOfLongInt, PairOfStrings> output,
@@ -73,7 +72,7 @@ public class SampleSentences extends Configured implements Tool {
             
             String lang = p.getLeftElement();
             if(lang.equals(sampleLang)){
-                if(Math.abs(r.nextLong())%count <= limit){
+                if(Math.abs(r.nextLong())%count <= nSamples){
                     output.collect(key, p);
                 }
                 
@@ -86,14 +85,8 @@ public class SampleSentences extends Configured implements Tool {
             r = new Random(rseed);    
             count = job.getLong("count", 1000000);
             sampleLang = job.get("sampleLang","de");
-            int nSamples = job.getInt("nSamples", 1000000);
-            long nMaps = job.getLong("nMaps", 300);
-            if(nSamples > count){
-                limit = 1;
-            }
-            limit = count/(nMaps*nSamples);
+            nSamples = job.getInt("nSamples", 1000);
         }
-
         
     }
 
@@ -183,15 +176,12 @@ public class SampleSentences extends Configured implements Tool {
 
         Counters counters = job.getCounters();
         long count = counters.getCounter(org.apache.hadoop.mapred.Task.Counter.MAP_OUTPUT_RECORDS);
-        long maps = counters.getCounter(JobCounter.TOTAL_LAUNCHED_MAPS);
         LOG.info(" Count from job 1 = " + count);
-        LOG.info(" Maps = " + maps);
         // Job 2
 
         conf.setLong("rseed", 1123456);
         conf.setLong("count", count);
         conf.setInt("nSamples", nSamples);
-        conf.setLong("nMaps", maps);
         
         conf.setNumMapTasks(1);
         conf.setNumReduceTasks(0);

### 2013-12-09 src/main/wikiduper/utils/SampleSentences.java
Added back in filter

@@ -71,12 +71,12 @@ public class SampleSentences extends Configured implements Tool {
                     Reporter reporter) throws IOException {
             
             String lang = p.getLeftElement();
-            if(lang.equals(sampleLang)){
+            //if(lang.equals(sampleLang)){
                 if(Math.abs(r.nextLong())%count <= nSamples){
                     output.collect(key, p);
                 }
                 
-            }
+            //}
         }
         
 
@@ -191,7 +191,7 @@ public class SampleSentences extends Configured implements Tool {
 
         conf.setJobName(String.format("SampleSentences-2[%s: %s]", OUTPUT, outputPath));
 
-        FileInputFormat.setInputPaths(conf, new Path(inputPath));
+        FileInputFormat.setInputPaths(conf, new Path(tmpPath));
         FileOutputFormat.setOutputPath(conf, new Path(outputPath));
 
         // Delete the output directory if it exists already.

### 2013-12-29 article/article-draft.tex
Shorter labels for histogram bins

@@
-\documentclass{acm_proc_article-sp}
+%File: formatting-instruction.tex
+\documentclass[letterpaper]{article}
+\usepackage{epsfig}
+\usepackage{graphicx}
 \usepackage{url}
-\usepackage{algpseudocode}
-\usepackage{verbatim}
-\usepackage{microtype}
-\usepackage{enumerate}
-\usepackage{enumitem}
-\usepackage{epsfig}
-\usepackage{algorithmicx}
-\usepackage{algorithm}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
+\usepackage{aaai}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\usepackage{color}
+
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+
+\frenchspacing
+\setlength{\pdfpagewidth}{8.5in}
+\setlength{\pdfpageheight}{11in}
+\pdfinfo{
+/Title (Insert Your Title Here)
+/Author (Put All Your Authors Here, Separated by Commas)}
+\setcounter{secnumdepth}{0}  
  \begin{document}
-
-\title{Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia}
-
-\numberofauthors{3}
-
+% The file aaai.sty is the style file for AAAI Press 
+% proceedings, working notes, and technical reports.
+%
+\title{Identifying Duplicate and Contradictory Information in Wikipedia}
+% with Near-Duplicate Sentence Detection}
 \author{
-\alignauthor Samet Ayhan\\
-       \affaddr{University of Maryland}\\
-       \affaddr{Dept. of Computer Science}
-       \email{sayhan@cs.umd.edu}
-\alignauthor Joshua Bradley\\
-       \affaddr{University of Maryland}\\
-       \affaddr{Dept. of Computer Science}
-       \email{jgbrad1@cs.umd.edu}
-\alignauthor Sarah E. Weissman\\
-       \affaddr{University of Maryland}\\
-       \affaddr{College of Information Studies}\\
-       \email{sew@umd.edu}
+BLINDED FOR REVIEW
+%AAAI Press\\
+%Association for the Advancement of Artificial Intelligence\\
+%2275 East Bayshore Road, Suite 160\\
+%Palo Alto, California 94303\\
 }
-
-\date{October 9, 2013}
-
 \maketitle
 \begin{abstract}
-On collaboratively authored sites like Wikipedia (\url{http://www.wikipedia.org}), where information is propagated on a large scale by a large number of authors, finding (and correcting) factual errors is difficult.
-Wikipedia articles, which are written and edited by an open community of mostly anonymous users are a prime candidate for copying of information.
-With few exceptions, the reader of any article can edit the text by copying from another article or an outside source without prior approval or confirmation of correctness and such errors may be duplicated many times over in different locations.
-Although Wikipedia has its own policies and procedures for maintaining articles and monitoring article quality, questions of the accuracy of information on the website remain.
-Although we do not directy attempt to measure the quality of Wikipedia articles, we are interested in finding near-duplicate occurrences at various granularity levels.
-Such near duplicate sentences may reflect factual information that has been updated in one article and not another, redundant content that should be merged, or merely inconsistencies that should be flagged and addressed.
-
-In this paper, we describe a similarity detection algorithm for Wikipedia articles that uses a locality sensitive hashing (LSH) technique implemened on the Hadoop MapReduce framework.
-The algorithm has been designed and implemented to detect similar content at the sentence level using large Wikipedia dumps.
-We also describe a heuristic method for classifying types of duplications on Wikipedia, which could be used for selecting and prioritizing editing efforts.
+\begin{quote}
+Our study identifies Wikipedia articles that contain
+highly-similar content by applying techniques for near-duplicate
+detection at the sentence level. This is accomplished with a MapReduce
+implementation of minhash, a locality-sensitive hashing technique, to
+identify clusters of sentences with high Jaccard similarity. Analysis
+shows that these cluster can be categorize into six different types, two
+of which are particularly interesting:\ identical sentences
+quantify the extent to which content in Wikipedia is copied and
+pasted, and near-duplicate sentences that state contradictory facts
+point to quality issues in Wikipedia articles.
+\end{quote}
 \end{abstract}
 
-% A category with the (minimum) three required fields
-\category{H.3.3}{Information Storage and Retrieval}[Information Search and Retrieval]
+\section{Introduction}
 
-\terms{Algorithms, Design, MapReduce}
+Readers of Wikipedia often notice that multiple articles contain
+highly-similar or even identical passages. In some cases they represent
+duplicate articles that require merging, but content overlap arises
+naturally as well. For example, the article about a hurricane and the
+article about the location where it made landfall might share the same
+content about the impact of the natural disaster. Identical content is
+most likely the result of copy and paste between articles, but
+interestingly, readers occasionally come across highly-similar content that
+state contradictory facts. In a distributed environment where anyone can
+edit content, these observations are perhaps not surprising, 
+%but we are not aware of any formal studies. 
+but in this paper we attempt to
+rigorously characterize these phenomena by treating the
+problem as that of near-duplicate sentence detection. We
+adapt standard locality-sensitive hashing (LSH) techniques to identify
+clusters of near-duplicate sentences in Wikipedia.
 
-\section{Introduction}
-The online encyclopedia Wikipedia is a collaboratively edited, multilingual, free resource.
-As of November 2013, there are over 31 million wiki pages with over 4 million articles in English and over 20,086,301 registered user accounts on the system \cite{wiki:weblink}.
-Most articles can be edited by anyone with internet access and an account is not required to edit.
+We believe this problem is interesting in a few ways:\ 
+For duplicate sentences,
+our analyses quantify the extent to which Wikipedia content is simply
+{\it replicated}, as opposed to {\it written} from scratch. 
+In the case of {\it near} duplicates, some differences represent
+minor copyediting that do not change the substance of the content, but
+in other case the differences 
+represent contradictory facts. Quantifying these cases
+provides an indirect measure of the quality of Wikipedia in terms of
+self consistency. We could imagine a robot that continuously monitors
+Wikipedia to flag these inconsistencies and requests editors
+to intervene and resolve.
 
-Because of its open nature, Wikipedia has a history of generating controversy over editorial quality and factual correctness.
-Although some studies have found Wikipedia's accuracy to rival that of traditional encyclopedias, other studies have found numerous factual errors.[References??] Since Wikipedia may be edited anonymously, information may freely copied between web sources and even between Wikipedia articles without verification.
-Additionally, many articles in Wikipedia lack citations.
-Although there are active communities of editors who contribute to the upkeep of various articles, often focusing on a partiular subject area and expanding and improving the related content, still much of Wikipedia content is created in an unsupervised manner.
-Wilkinson found the distribution of article edits on Wikipedia to have a long tail, meaning that a small number of articles have many edits while most articles have few, and that the number of edits is directly related to article quality.
-Articles with low edits and low editorial attention, are less likely to be updated when new information is available \cite{wilkinson:wiki}.
-
-Under such conditions, this type of large-scale collaborative effort may result in duplicate or near duplicate articles at various granular levels, such as sentence-level or multi-gram granularity.
-For our purposes, we focus primarily on the sentence level.
-Near duplicate sentences may reflect factual information that has been updated in one article and not another (for example, information that varies over time, like populations or a country's GDP), or merely inconsistencies that should be flagged and addressed.
-
-Our approach applies minhashing, a well known, scalable, locality sensitive hashing (LSH) technique for near duplicate document detection.
-Since we are assuming the content we are looking for is not just similar, but has diverged due to an editorial process, as part of this work we investigate how well minhash approximates edit distance.
-We investigate the following questions:
-\begin{itemize}[noitemsep,nolistsep]
-\item How effectively does minhashing approximate edit distance?
-Edit distance seems like a reasonable metric for near duplicate sentences, however LSH does not map naturally to the edit distance metric.
-\item How well do techniques for detecting near duplicate documents work when applied at the sentence level?
-\item Do near duplicate sentences correspond to factual errors?
-\end{itemize}
-
-The rest of this paper is organized as follows: In Section 2, we present related work, in Section 3, we explain the algorithm utilizing locality sensitive hashing, in Section 4, we discuss parameter tuning for Minhash.
-In Section 5, we present the working application within the MapReduce framework.
-In Section 6, we discuss our experiments with various Wikipedia datasets.
-The final section contains concluding remarks and future work.
+This work makes no claims about the novelty of our
+techniques nor our implementation for near-duplicate sentence
+detection. Rather, our contribution lies in using existing techniques
+to analyze Wikipedia. To our knowledge, we have not seen
+near-duplicate detection applied to Wikipedia in this way before.
 
 \section{Related Work}
-A number of techniques have been implemented to identify similarity between documents in the literature.
-These techniques usually differ in terms of corpus of interest, signature representing the document, feature-set determined by the system, and the end goal of the analysis.
 
-Broder et al.
-introduced shingling to compute document similarity and containment.
-They also presented methods for using a subset of shingles while still allowing similarity and containment computations \cite{broder:resemblance}.
+The problem we tackle in this paper is related to a few other problems
+that have been studied before. Near-duplicate detection is important
+in web search because web pages are often copied or mirrored with only
+minor differences (e.g., ads or navigation bars); it would be
+desirable to return only the ``canonical'' version in search
+results. In fact, the algorithm that we use in this paper,
+minhash~\cite{broder:resemblance}, was originally developed for
+near-duplicate detection of webpages. Another closely-related problem
+is plagiarism detection~\cite{}, or more generally, ``text
+reuse''~\cite{seo:dct,bendersky:timeline}. In contrast to near-duplicate detection, the
+focus is usually on smaller segments of text as opposed to entire
+documents. However, similar approaches such as shingling are
+applicable to both problems.
 
-Seo et al.
-defined a general framework for text reuse detection.
-They introduced Discrete Cosine Transform (DCT) fingerprinting for general or local text reuse detection with high accuracy and efficiency \cite{seo:dct}.
+Other similar manifestations of the problem are what the data mining
+community calls pairwise similarity search or ``all pairs''
+search~\cite{Bayardo_etal_WWW2007} and what the database community
+calls set similarity join~\cite{Vernica_etal_SIGMOD2010}. The idea is the same:\ given a
+potentially large collection of objects, identify all pairs whose
+similarity is above a threshold according to some similarity metric
+(e.g., cosine similarity).
 
-Zhang et al.
-presented partial duplicate detection algorithm using sequence matching that transforms partial-duplicate detection task into three MapReduce jobs: 1.Indexing, 2.Sequence Duplicate Detection, 3.Sequence Matching \cite{zhang:pdc}.
+There are two large classes of solutions for the above problems:\ in
+the {\it index-based} approach, an inverted index is constructed from
+objects in the collection and a traversal of this index allows the
+similiar pairs to be extraced,
+e.g.,~\cite{Bayardo_etal_WWW2007,lin:brute}; with {\it hash-based}
+approach, the basic idea is to use locality-sensitive hashing (LSH) to
+identify similar pairs based on hash collisions, e.g., minhash~\cite{broder:resemblance}
+and others~\cite{}. Of course, hybrid solutions are also
+possible. Previously, scaling up of these solutions has been
+accomplished by MapReduce~\cite{zhang:pdc,lin:brute,Vernica_etal_SIGMOD2010}. Our approach
+take advantage of minhash using a straightforward MapReduce
+implementation in Hadoop.
 
-Hajishirzi et al.
-introduced an adaptive near-duplicate detection (ANDD) method by extending term-weighting framework to learn k-gram vectors.
-Provided that each document was represented by an informative real k-gram vector, similarity measures were computed to come up with predicted values of near-duplicates \cite{hajishirzi:andd}.
+Because of its open nature, Wikipedia has a history of generating
+controversy over editorial quality and factual correctness. Although
+some studies have found Wikipedia's accuracy to rival that of
+traditional encyclopedias, other studies have found numerous factual
+errors.[References??] Since Wikipedia may be edited anonymously,
+information may freely copied between web sources and even between
+Wikipedia articles without verification. Additionally, many articles
+in Wikipedia lack citations. Although there are active communities of
+editors who contribute to the upkeep of various articles, often
+focusing on a partiular subject area and expanding and improving the
+related content, still much of Wikipedia content is created in an
+unsupervised manner. Wilkinson found the distribution of article edits
+on Wikipedia to have a long tail, meaning that a small number of
+articles have many edits while most articles have few, and that the
+number of edits is directly related to article quality. Articles with
+low edits and low editorial attention, are less likely to be updated
+when new information is available \cite{wilkinson:wiki}.
 
-Lin described three MapReduce algorithms for computing pairwise similarity on document collections \cite{lin:brute}.
-\begin{enumerate}[noitemsep,nolistsep]
-\item Based on brute force.
-\item Treated as large-scale ad hoc retrieval.
-\item Based on Cartesian product of postings lists.
-\end{enumerate}
+\section{Near-Duplicate Detection}
 
-Manku et al.
-used Charikar's fingerprinting technique for developing near-duplicate detection system.
-They presented an algorithmic technique for identifying existing f-bit fingerprints that differ from a given fingerprint in at most k bit-positions, for small k.
-They demonstrated that their system is useful not only for batch but also for online processing \cite{manku:web}.
+In order to measure document similarity we use a common LSH technique
+known as MinHash \cite{broder:resemblance}. A minhash signature on a
+text document is calculated using a parametrized family of hash
+functions $F_i$, $1 \le i \le N$. (In our case, input ''documents''
+are individual sentences found within the content of Wikipedia
+articles.) Each document is broken up into n-gram ``shingles'' and for
+each shingle set $S$ a set $\{min_{s \in S}(F_i(s)\}$ of minimum
+hashes over the hash family is produced. The signature on a document
+$d$ is represented as a vector of $K$ minhashes, chosen from the set
+$\{min_{s \in S}(F_i(s)\}$ of minimum hashes. In order to minimize
+false negatives we generate multiple signatures ($M$ signatures) for
+each input sentence.
 
-Bendersky et al.
-examined two information flow representations: the timeline and the link graph.
-They proposed several simple unsupervised techniques for timeline construction link graph analysis \cite{bendersky:timeline}.
+$K$, $N$, $M$, $n$, as well as the size in bits of the
+hashes are all parameters that must be set for the minhash algorithm.
 
-In order to handle large Wikipedia dumps with the order of tens or hundreds of gigabytes and even a few terabytes, we used MapReduce framework in this work, that was introduced by Dean and Ghemawat \cite{dean:mapreduce}.
-
-\section{Algorithm Utilizing Locality \\ Sensitive Hashing}
-
-In order to measure document similarity we use a common LSH technique known as MinHash (\cite{broder:resemblance}).
-A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$.
-(In our case, input ''documents'' are individual sentences found within the content of Wikipedia articles.) Each document is broken up into n-gram ``shingles'' and for each shingle set $S$ a set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family is produced.
-The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes.
-In order to minimize false negatives we apply a technique sometimes known as ``banding'' \cite{ullman:massive} where multiple signatures are produced for each input document.
+\red{I think I misunderstood banding (which appears to be hashing of
+  hash signatures) and it is not what we are doing here, so I took out
+  the reference.}
 
@@
 
-\subsection{Implementation Details}
+\subsection{MapReduce Implementation}
 
-Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 (\url{https://github.com/lintool/Cloud9}) and WikiClean (\url{https://github.com/lintool/wikiclean/}) libraries for parsing Wikipedia page text from the Wikipedia XML dump format.
-An open source implementationis available on Github (\url{https://github.com/seweissman/wikiduper}).
+In our MapReduce algorithm, the mapper receives a Wikipedia article
+(value) that is identified by a unique docid (key). Inside the mapper
+we break the article into sentences using a regular expression;
+sentences that are shorter than 75 shingles words or longer than 600
+shingles are discarded. For each sentence, the minhash signatures are
+then computed. The family of hash functions is implemented using a
+``Multiply Shift'' hashing scheme\footnote{\small
+  http://en.wikipedia.org/wiki/Universal\_hashing} and is generated
+from a random seed. The hash family is also parametrized by hash
+output key size, which is also configurable. For our experiments we
+use a 60 bit hash and a hash family of size 20.
 
-%Sentences are parsed out over each document using a regular expression.
-Sentences that are too large or too small are discarded.
-The family of hash functions is implemented using a ``Multiply Shift'' (\url{http://en.wikipedia.org/wiki/Universal_hashing}) hashing scheme and is generated from a random seed using the Java Random class.
-The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.
+Each signature is emitted as the key of an intermediate key--value
+pair with the sentence id as the value (constructed from the docid and
+the sentence count).
 
-\section{Parameter Tuning}
+The MapReduce programming model guarantees that all values associated
+with the same key are shuffled to the same reducer---in effect,
+collecting the hash collisions for us. In the reducer we receive a
+signature as a key and as values all sentence ids that share the
+signature. If there is more than one value per key, we write out all
+sentence ids as a cluster. This serves as input to the final cluster
+generation stage (see below).
 
-The minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size.
-Each of these parameters has an impact on the error rates in the minhash output.
+\subsection{Parameter Tuning}
 
-\subsection{Jaccard Similarity and Edit Distance}
+The minhash algorithm is parametrized by several values, including
+shingle length, length of hash vectors, number of hash signatures per
+input document, and hash output size. Each of these parameters has an
+impact on the error rates in the minhash output. For our experiments
+we choose 10 signatures ($M$ = 10) per input sentence, since sentences
+themselves are small and we will be processing many of them. Once we
+have fixed $M$ we can use the property that the probability of a match
+between two sentences is equal to the Jaccard similarity of their
+shingle sets. Thus the probability of a match for two sentences $A$
+and $B$ can be expressed as follows:
+\[P[match(A,B)] = 1 - (1 - s^K)^M\]
+where $s$ = Jaccard($A$,$B$). Here we choose $K = 10$. Given these
+settings, if we choose .9 Jaccard similarity as our goal (90\% overlap
+in shingle sets), then there is a 99\% chance of a match, while
+sentences similarity .7 have only a 25\% chance of being a match and
+sentences with similarity .6 have only a 6\% chance of being a match.
 
-%Jaccard similarity is a measure of set similarity while our stated goal is to find sentences in Wikipedia that have been copied from one article to another and possibly edited.
-A more natural measure to use for this application is edit distance, but there is no known good locality sensitive hashing family for edit distance \cite{Kirsch06distance-sensitivebloom}.
+With the above settings we can make a conservative estimate of the
+amount of data generated by our signature generation code: (60 bit
+signatures) $\times$ (10 hashes per signature) $\times$ (10 signatures
+per document) $\times$ (10m Wikipedia articles) $\times$ (100
+sentences per article) $\approx$ 70GB of minhash output.
 
-In order to estimate Jaccard similarity of sentences $X$ and $Y$ in terms of edit distance we assume that $X$ and $Y$ are both of length $N$ and that their shingle sets are of maximum size (i.e.
-all shingles are unique).
-Also assume that $X$ and $Y$ have edit distance $e$.
-We limit type of edits to changing characters in place.
-Additionally, to simplify our calculations, we assume that edits are localized so that no shingle overlaps more than one edit.
+We choose a shingle length of 12 with the goal of shingle sets that
+cross word boundaries in order to preserve sentence order.
 
-(WLOG) Let $S$ be the set of shingles for X and let $S_o$ be the set of shingles of X that overlap edits.
-The maximum number of unique shingles for a sentence of length $N$ is $N - L + 1 = |S|$.
-Also, we can see that $e \le |S_o| \le e + L - 1$.
-Since edits at the start or end of the sentence will overlap with fewer shingles than edit mid-sentence.
+Observe that it is possible to improve precision by filtering results
+with secondary testing on the output signature groups, thus allowing
+one to improve recall by relaxing parameters. The current work does
+not investigate parameter tuning with filtering.
 
-Now we can define $|X \cup Y|$ and $|X \cap Y|$ in terms $S$ and $S_o$ as follows:
-\begin{eqnarray*}
-|X \cap Y| & = & |S| - |S_o| \\
-|X \cup Y| & = & 2*|S_o| + |X \cap Y| \\
-           & = & |S_o| + |S|
-\end{eqnarray*}
-
-Plugging in the values above for $|S_o|$ and $|S|$ we get:
-
-\begin{eqnarray*}
-E + N - L + 1  \le & |X \cup Y| & \le E + N \\
-N - L + 1 - E  \ge & |X \cap Y| & \ge N - 2L - E + 2 \\
-\end{eqnarray*}
-\begin{eqnarray*}
-\frac{N - L - E + 1 }{N - L + e + 1} >= & J(X,Y) & >= \frac{N - 2L - E + 2}{N + E}
-\end{eqnarray*}
-
-Note that, at least under this set of assumptions, the Jaccard similarity is always less than the ``edit similarity'' (1 - normalized edit distance):
-
-\begin{eqnarray*}
-J(X,Y) & <= & \frac{N - E}{E + N - L + 1} - \frac{L - 1}{E + N - L + 1} \\
-       & <= & \frac{N - E}{N} \\ 
-       & =  & 1 - \frac{E}{N}
-\end{eqnarray*}
-
-Finally we can divide through the equations for J(X,Y) by N, which gives us:
-
-\begin{eqnarray*}
-\frac{1 - l - e}{1 - l + e} >= J(X,Y) >= \frac{1 - 2l - e}{1 + e}
-\end{eqnarray*}
-
-where $l$ is relative shingle size and $e$ is normalized edit distance.
-
-Note that as relative shingle size goes to 0 there is a nice convergence for Jaccard similarity:
-\[\lim_{l->0}J(X,Y) = \frac{1 - e}{1 + e}\]
+\red{Is this sufficient discussion for recall?
+The probability curve gives us a recall estimation at each level of similarity, which I think is better than an overall recall estimation via experiment.}
 
@@
 \centering
-\includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
-\caption{Jaccard Similarity vs. normalized edit distance.}
-\label{jac-ed}
+\includegraphics[width=3.25in, keepaspectratio = true]{jacmatchprobs.png}
+\caption{Minhash Parameter tuning.}
+\label{clust}
 \end{figure}
 
-As we would expect, Jaccard similarity decreases as edit distance increases, but it also decreases as shingle length increases.
-Figure \ref{jac-ed} shows Jaccard Similarity plotted against edit distance for $l = .05$ and $l = .2$.
-At $l = .05$ and $e = .2$ our estimate for Jaccard similarity has already fallen to the range [0.58,0.65].
-Clearly setting $l$ too high can increase the false positive rate, but setting $l$ too low will increase the false positive rate, since it will increase the size of the intersection of the shingle sets.
+\subsection{Final Cluster Generation}
 
-\subsection{False positives}
+The output of our minhash algorithm is a set of clusters, where each
+cluster represents a signature collision. Since we generate multiple
+signatures per document, it is possible (and frequently observed) that
+a sentence appears in multiple clusters. We adopt the standard
+practice of merging all clusters that share at least one common
+sentence. (If we were applying secondary filtering to remove false
+positives, it would make sense to apply it before merging clusters.)
+Cluster merging is accomplished in one pass with a union find data
+structure. In union find each node maintains a pointer to a head node
+for the set. We maintain a lookup table from each sentence id to its
+node in the union find structure. As we read the input clusters we
+look up the node for each sentence as merge clusters or create new
+ones as needed. Merging two clusters involves changing the head node
+of one cluster to point to the head of the other. In practice when
+walking up the tree to find the head we change all nodes along the way
+to point to the head node to reduce search time. Once clusters are
+merged we do a pass over our lookup table to obtain the mapping from
+clusters to nodes.
 
-In order to estimate the affect of shingle length on false positive rate we ran a number of experiments for a 1 G collection of wikipedia documents.
-For fixed $N=10$ we ran experiments for three values of $K=\{8,9,10\}$ and $8 \le L \le 16$.
-Setting a normalized edit distance threshold of $e = .25$, we calculated the total number of ''good'' ($e <= .25$) and ''bad'' ($e > .25$) (unique) sentence pairs as well as the false positive rate (\# bad pairs divided by the total number of sentences).
-Results are presented in Figure \ref{ed-grid}.
+\subsection{Mapping Back to Sentences}
 
-As we might expect, as shingle length increases, the false positive rate decreases.
-However, the total number of good pairs also decreases, implying that our false negative rate is also increasing.
-When applying these techniques, increased recall will come at the price of decreased precision.
-Because of this, in a real implementation, it would likely be desirable to set requirements for recall, then use secondary filtering to increase precision.
-For example, actual edit distance could be applied as a secondary filter.
+Once we have merged clusters we typically wish to map the sentence ids
+back to their corresponding text so that we can analyze the content of
+each cluster. To accomplish this we use another MapReduce job that
+reads the merged cluster output as side data and creates a hashmap
+from the original docid (contained in the sentenceid) to a
+sentence/cluster pair. The MapReduce job maps back over the original
+Wikipedia data, using the same regular expression to break up
+documents into sentences. For each input sentence, the mapper checks
+to see if the sentence is in the cluster hashmap. If so, it emits a
+key value pair with the cluster id as the key and an (article title,
+sentence text) pair as the value. Once again, the MapReduce framework
+takes care of grouping output by key so that sentences in the same
+cluster are grouped together. Since no further processing is necessary
+for the clusters, we use the identify reducer, which passes on the
+keys and values as received.
 
@@
 \centering
-\epsfig{file=edgridl.eps,width=3.5in}
-\caption{False Positive Rate, Good Count, Bad Count for $N=10, K \in \{8,9,10\}, 5 \le L \le 15$}
-\label{ed-grid}
+\includegraphics[width=3.25in, keepaspectratio = true]{clusterhistogram.png}
+\caption{Histogram of Cluster Sizes.}
+\label{params}
 \end{figure}
 
-\section{Experiments and Discussion}
+\section{Experimental Results}
 
-%We performed several analyses to provide more insight into the occurence of duplicate sentences.
-In particular, we were interested in detecting similar sentences that arose from copying text from one article to another since such instances would represent content that is either redundant, or content that has diverged in the sense that either the original or the copy was edited for clarification of factual correctness and the other was not.
-Such instances give insight into the Wikipedia editing process, and also represent an opportunity to improve article quality on Wikipedia by identifying places where further editing or article merging may be needed.
+Our analysis was conducted on an XML dump of English Wikipedia from
+July 2013. The entire corpus is approximately 42 GB and contains 10.2m
+articles (after excluding certain non-article pages). Based on our
+simple sentence chunker, there are a total 135.8m sentences in the
+corpus.
 
-All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 7/2013) obtained from dumps.wikimedia.org.
-The enwiki dump is approximately 42G in size and contains 10,218,778 articles (after excluding certain non-article page types).
-Running our application on the enwiki dump on a shared cluster of 16 nodes (20 GB RAM and 4?
-cores each) took $\approx$ 25 minutes.
+Running our Hadoop implementation of minhash on the entire collection
+took approximately 25 minutes on our cluster consisting 16 nodes (128
+cores). Code necessary for replicating these experiments have been
+made open source.\footnote{\small BLINDED}
 
-The total number of similar sentence clusters was 1,151,640, including 3,496,074 article/sentence pairs over 1,091,804 article titles.
-The total number of unique sentences over all clusters was 2,361,886.
+%https://github.com/seweissman/wikiduper}.
 
-Cluster sizes ranged from 2 to 42,901.
-(See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, about 99\% of our clusters have size below or equal to 10, but about 1/4 of the output sentence/article pairs fall into clusters with size greater than 10.
-One explanation for this distribution of sentences is the phenomenon we call ''templatification,'' which we describe in more detail below.
+After the processing pipeline, we identified 1.15m clusters, 3.50m
+article/sentence pairs over 1.09m articles. The clusters contain 2.36m
+unique sentences in total. Cluster sizes range from 2 to 42,901; see
+Figure~\ref{clust} for histogram. Most clusters are small; about 99\%
+of the clusters have sizes less than or equal to ten, but about a
+quarter of the output sentence/article pairs fall into clusters with
+size greater than ten.
 
-\begin{figure}
-\centering
-\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
-\caption{Histogram of Cluster Sizes (for cluster size $< 300$, log scale).}
-\label{clust}
-\end{figure}
+Of the 14,488 clusters greater than size 10, 2722 (18.8\%) contain
+identical sentences. 3890 (26.8\%) have fewer than 50\% of their
+sentences unique. 5725 contain entirely unique sentences. Manual
+inspection shows that many of the large clusters, including most of
+the clusters of entirely unique sentences consist of ``template''
+sentences, where sentences follow strict patterns of construction (See
+discussion of sentence types below). Non-unique clusters consist of
+such templates, but also largely identical groupings of sentences
+where some of the sentences have been edited, e.g. the following
+cluster contains 663 sentences, 661 of which are identical
 
-\subsection{Similar Sentence Types}
-
-Manual inspection of cluster output reveals several different similar sentence types. These types can be summarized as follows:
+\red{I can confirm the relation between large clusters and templates by looking at results, but cannot confirm that template articles are mostly stubs.
+I guess it would be possible to look at whether articles in large clusters have shorter length on average.}
 
 \begin{itemize}
-\item Templatification
-\item References
-\item Direct Copying
-\item Direct Copying with Copy Editing
-\item Direct Copying with Factual Drift
+\item They are capable of "stinging" humans therefore live ones should be handled carefully or not at all. [661 sentences]
+\item They are capable of "stinging" therefore live ones should be handled carefully or not at all. [1 senence]
+\item They are capable of "stinging" humans; therefore live ones should be handled carefully or not at all. [1 sentence]
 \end{itemize}
 
- \emph{Templatification} occurs when one sentence is an exact duplicate of another sentence, but the main topic has been changed by only a few pieces of key information having been modified.
-For example, it could be said that the following two sentences follow a particular \emph{template}.
-\begin{itemize}[noitemsep,nolistsep]
+Other clusters show distributions of sentences that imply that appear to reflect more complex editing patterns.
+E.g., the following sentences are part of a cluster of size 299.
+Each is plausibly a variation of one original sentence that has been edited and replicated multiple times:
 
-\item Of the agricultural land 40.4\% is used for growing crops and 26.6\% is pastures while 2.2\% is used for orchards or vine crops. [Gondiswil]
-\item Of the agricultural land 26.1\% is used for growing crops and 30.2\% is pastures while 3.0\% is used for orchards or vine crops. [Kleindietwil]
-\item Of the agricultural land 37.8\% is used for growing crops and 35.5\% is pastures while 2.2\% is used for orchards or vine crops. [Leimiswil]
-
-\end{itemize}
-From the perspective of editing/writing Wikipedia articles, this is a strong indicator that the author copied the original sentence and modified the relevant information to pertain to a different topic.
-What remains shared between both sentences though is the inherent structure.
-
-\emph{Direct Copying} occurs when the same sentence has been copied into another (or possibly the same) article.
-This can happen for many reasons, including articles that deal with similar subjects, or articles that are subtopics of other topics Similarly, \emph{Direct Copying with Copy Editing} occurs when the same sentence has been copied into another article and then one or both sentences has been edited for style or clarity.
-For example:
-\begin{itemize}[noitemsep,nolistsep]
-\item In dry areas it may only emerge from its burrow for a few weeks when conditions are right and usually at night but in areas with permanent water bodies and abundant rain it may be active all day.
-[Great Plains toad]
-\item In dry areas it may only emerge from its burrow for a few weeks when conditions are right and only at night but in areas with permanent water bodies and abundant rain it may be active all day.
-[List of amphibians and reptiles of Montana]
+\begin{itemize}
+\item In the Commonwealth of Pennsylvania pension and Social Security income are exempted from state personal income tax and local earned income tax regardless of the individual's wealth.
+[67 sentences]
+\item In the Commonwealth of Pennsylvania pension income and Social Security income are exempted from state personal income tax and local earned income tax regardless of the level of the individual’s personal wealth.
+[63 sentences]
+\item In the Commonwealth of Pennsylvania pension income and Social Security income are exempted from state personal income tax and local earned income tax regardless of the individual's level of wealth.
+[18 sentences]
+\item In Pennsylvania pension income and Social Security income are exempted from state personal income tax and local earned income tax regardless of the level of wealth. [15 sentences]
+\item In the Commonwealth of Pennsylvania pension income and Social Security income are exempted from state personal income tax and local earned income tax regardless the of income level.
+[13 sentences]
+\item In the Commonwealth of Pennsylvania pension income and Social Security income are exempted from state personal income tax and local earned income tax regardless of the person's wealth.
+[12 sentences]
 \end{itemize}
 
-\emph{Factual drift} most notably occurs when the same sentence has been copied and a piece of factual information about the \emph{same} topic has changed.
-For example, factual drift can be seen in the following two sentences.
-\begin{itemize}[noitemsep,nolistsep]
-\item The color of the upper rim of an astronomical object could go from green to blue to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
-[Green flash]
-\item The color of the upper limb of an astronomical object could go from blue to green to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
-[Mirage of astronomical objects]
-\end{itemize}
-Although factual drift is similar to copy editing and may occur along with copy editing, we distinguish the two cases since factual errors are more severe than style issues.
+%\subsection{Similar Sentence Types}
 
-\emph{References} refers to citations, typically occurring at the end of a Wikipedia article.
-Since Wikipedia does not adhere to one single citation style, the same work may be referenced on multiple pages in different styles.
-Similarly different portions of the same work may be referenced in different articles.
-Although citation errors might be harder to distinguish from factual errors, errors in citation are arguably no less important.
-(It would also be interesting to compare whether articles that share similar sentences also share similar citations.)
+\begin{figure*}[t]
+{\small
+{\bf Templates}\\
+Of the agricultural land 40.4\% is used for growing crops and 26.6\% is pastures while 2.2\% is used for orchards or vine crops. [Gondiswil] \\
+Of the agricultural land 26.1\% is used for growing crops and 30.2\% is pastures while 3.0\% is used for orchards or vine crops. [Kleindietwil] \\
+Of the agricultural land 37.8\% is used for growing crops and 35.5\% is pastures while 2.2\% is used for orchards or vine crops. [Leimiswil] \\[1ex]
+{\bf Identical}\\
+Professional organizers help redirect paradigms into more useful cross-applications that ensure properly co-sustainable futures for their clients' spaces and processes. [Professional organizing] \\
+Professional organizers help redirect paradigms into more useful cross-applications that ensure properly co-sustainable futures for their clients' spaces and processes.
+[Professional organizer] \\[1ex]
+{\bf Copyediting}\\
+In dry areas it may only emerge from its burrow for a few weeks when conditions are right and usually at night but in areas with permanent water bodies and abundant rain it may be active all day.
+[Great Plains toad] \\
+In dry areas it may only emerge from its burrow for a few weeks when conditions are right and only at night but in areas with permanent water bodies and abundant rain it may be active all day.
+[List of amphibians and reptiles of Montana]\\[1ex]
+{\bf Factual Drift}\\
+The color of the upper rim of an astronomical object could go from green to blue to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
+[Green flash] \\
+The color of the upper limb of an astronomical object could go from blue to green to violet depending on the decrease in concentration of pollutants as they spread throughout an increasing volume of atmosphere.
+[Mirage of astronomical objects] \\[1ex]
+{\bf References}\\
+Neotropical Ichthyology 11 (1): 73-80. \\
+Neotropical Ichthyology 10 (2): 245-253. \\[1ex]
+{\bf Other}\\
+Army Medical Research Institute of Infectious Diseases (USAMRIID) microbiologist Bruce E. [Timeline of the 2001 anthrax attacks] \\
+Army Medical Research Institute of Infectious Diseases (USAMRIID) which transitioned from the previous U.S. [Fort Detrick]}
+\caption{Categories of near-duplicate sentences in Wikipedia.}
+\label{toparticlegroups}
+\end{figure*}
 
-\begin{itemize}[noitemsep,nolistsep]
-\item Neotropical Ichthyology 11 (1): 73-80.
-\item Neotropical Ichthyology 10 (2): 245-253.
-\end{itemize}
+Based on manual inspection of cluster output, we can categorize
+near-duplicate clusters into one of six types. Examples are shown in
+Figure~\ref{toparticlegroups} %(with article titles in brackets) 
+and discussed below.
 
-\subsubsection{Breakdown of Sentence Types and Filtering}
+\emph{Templates} describe sentences that have identical structure, but
+with different entities, facts, or figures for {\it different} topics
+(and thus are not contradictory). They reflect conscious attempts to
+impose structure across groups of articles that may be related. Since
+several of the largest template clusters contain tens of thousands of
+sentences (the largest over 40,000), it is likely that some
+template groups are automatically generated using bots.
 
-By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table \ref{counts}.
-The manual analysis reveals that $\approx 75\%$ of the clusters identified are either in the \emph{identical} or the \emph{template} classes.
-We argue that these classes are less interesting, since they represent either large collections of identically formatted and very specific facts, or content that is exactly the same, and such content is at least internally consistent, if redundant, and less likely to contain errors.
-Thus they are candidates for filtering out of the result set.
+\emph{Identical} sentences are the result of copy and paste, and are
+often found in articles that cover similar topics or articles that are
+subtopics of other topics.
+
+Non-identical but highly-similar sentences break down into two types:
+\emph{Copyediting} refers to nearly identical sentences that differ in
+stylistic or otherwise non-substantive ways. They arise with minor
+editing after a copy and paste. \emph{Factual drift} describes
+sentences about the {\it same} topic that provide contradictory
+facts. Although without detailed research, there is no way to
+ascertain which version (if any) is correct, we can identify a common
+scenario. After a copy and past, a fact becomes out of date (e.g., the
+tallest building or the death toll in a disaster) and is corrected in
+one instance but not the others.
+
+\emph{References} refers to citations, typically occurring at the end
+of articles. Since Wikipedia does not adhere to one single citation
+style, the same work may be cited differently, or multiple citations
+to the same venue may be similar.
+
+Finally, all clusters that do not fit into any of the above category
+are classified as \emph{other}. These typically represent sentences
+that are highly similar, but otherwise bear no semantic relationship
+with each other. Sentence chunking errors often contribute to these
+spurious results.
+
+%\subsection{Breakdown of Sentence Types and Filtering}
+
+To quantify the distribution of these six cases, we randomly sampled
+2094 clusters and performed manual classification. The results are
+shown in Table~\ref{counts}. Nearly three quarters of all clusters
+are either \emph{identical} or the \emph{template}.
 
@@
 \caption{Sentence Breakdown Counts}
-\begin{tabular}{| l | c | c |}
+\vspace{0.2cm}
+\begin{tabular}{| l | r | r |}
 \hline
-Factual Drift & 121 & 5.78\% \\ \hline
-Template & 632 & 30.18\% \\ \hline
-Reference & 7 & 0.33\% \\ \hline      
-Copy Edit & 283 & 13.51\% \\ \hline
+type & count & fraction \\
+\hline
+\hline
+Templates     & 632 & 30.18\% \\ \hline
 Identical     & 948 & 45.27\% \\ \hline
+Copyediting   & 283 & 13.51\% \\ \hline
+Factual drift & 121 &  5.78\% \\ \hline
+References    &   7 &  0.33\% \\ \hline      
 Other         & 103 &  2.92\% \\ \hline
-\hline
 \end{tabular}
@@
 
-Identical clusters are easy to identify through exact hashing.
-In order to get a rough filter for template clusters, we develop a heuristic score on low frequency words in the cluster word set.
-For our purposes a low-frequency word is one that occurs in less than half of the cluster sentences.
-The score we use is:
-\[(\#numeric + \#proper)/(\#numeric + \#proper + \#other)\]
-Where \#numeric is the number of numeric terms in the cluster word set (all unique low frequency words occuring in the cluster), \#proper is the number of proper nouns in the cluster word set (i.e.
-capitalized words), and \#other is the number of other words.
+\section{Future Work and Conclusions}
 
-Applying the score to our hand-classified clusters we see (Figure \ref{heuristic}) that this score does separate between template and non-template clusters.
-(Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.)
+Currently, our technique only identifies clusters of sentences that
+are above a certain threshold in Jaccard similarity. Missing from our
+analysis is the notion of information flow:\ Which was the source
+article and which was the target? Are there copy ``chains'' where
+content was progressively copied from one article to the next, with
+possible ``branches''? This information
 
-After applying the score to the entire set of wiki clusters (with a score threshold of .6), we identify 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters.
-The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196 sentences.
-
-\begin{figure}
-\centering
-\includegraphics[width=3.5in, keepaspectratio = true]{classifyscoreswikinew.pdf}
-\caption{Histogram of Hand Labeled Clusters by Template Heuristic Score.}
-\label{heuristic}
-\end{figure}
-
-\subsection{Sentence Similarity as a Measure of Article Similarity}
-
- For clarity purposes, we define \emph{similarity count} as simply the total number of unique sentences between two articles that were found to share the same hash signature.
-Using the output of the minhashing routine, we performed a pairwise similarity count across all articles that shared similar sentences to identify the articles that are most similar by this measure.
-Overall, we found $91,591$ wikipedia article paris that had a similarity count greater than or equal to $25$ and $29,582$ wikipedia article pairs that had a similarity count greater than or equal to $50$, and $\approx 6331$ Wikipedia articles with similarity count greater than or equal to $75$.
-If we perform the same similarity analysis, but filter clusters using the template heuristic described above, we find $5950$ article pairs with similarity count greater than or equal to $25$, $472$ article pairs with similarity greater than or equal to $50$ and $159$ article pairs with similarity greater than or equal to $75$.
-Table \ref{toparticlegroups}) shows the top similar article groups with similarity count greater than 100 (where pairs sharing an element have been merged).
-
-\begin{figure*}[hp!]
-\centering
-\caption{Top Similar Article Groupings, Similarity Count $\ge$ 100}
-{\small
-\begin{tabular}{| l |}
-    \hline
-\{Hindi Cinema, Bollywood\} \\
-\{Telecommunications in the People's Republic of China, Telecommunications in China\} \\
-\{Private equity in the 2000s, History of private equity and venture capital\} \\
-\{List of ethnic cleansings, Ethnic cleansing\} \\
-\{Route of the Oregon Trail, Oregon Trail\} \\
-\{English literature, British literature\} \\
-\{Maritime history of the United States (1900–99), History of the United States Merchant Marine\} \\
-\{Culture of the United States, Society of the United States\} \\
-\{Halifax (former city), History of the Halifax Regional Municipality\} \\
-\{List of SNK characters, List of The King of Fighters characters\} \\
-\{Toronto Blue Jays, History of the Toronto Blue Jays\} \\
-\{History of Christianity in the United States, History of Protestantism in the United States\} \\
-\{Sri Ranganathaswamy Temple, Srirangam, Šri Ranganata Svami hram\} \\
-\{Individualist anarchism in Europe, Individualist anarchism\} \\
-\{Nutritional neuroscience, Nutrition and cognition\} \\
-\{Jesse Hubbard and Angie Baxter, The Hubbard Family\} \\
-\{History of the Dallas Mavericks, Dallas Mavericks\} \\
-\{Imperial Crypt Vaults, Imperial Crypt\} \\
-\{History of the Roman Empire, Byzantine Empire, History of the Byzantine Empire\} \\
-\{May Bukas Pa, List of May Bukas Pa episodes\} \\
-\{Myth: The Fallen Lords, Myth (series)\} \\
-\{Individualist anarchism in the United States, Anarchism in the United States\} \\
-\{Native Americans in the United States, Native American cultures in the United States\} \\
-\{Hockey stick controversy, Hockey stick graph\} \\
-\{Vancouver Canucks, History of the Vancouver Canucks\} \\
-\{Silvio Berlusconi, Controversies surrounding Silvio Berlusconi\} \\
-\{Los Angeles Angels of Anaheim, History of the Los Angeles Angels of Anaheim\} \\
-\{2007 suicide bombings in Iraq, List of terrorist incidents in Iraq in 2007\} \\
-\{List of Canadian tornadoes and tornado outbreaks, List of 21st-century Canadian tornadoes and tornado outbreaks\} \\
-\{Scotland in the modern era, History of Scotland\} \\
-\{Libertarian socialism, Libertarian Marxism\} \\
-\{Canti (Leopardi), Giacomo Leopardi\} \\
-\{Jayne Torvill, Christopher Dean, Torvill and Dean\} \\
-\{Government of Mahmoud Ahmadinejad (2005–present), Foreign policy of Mahmoud Ahmadinejad, Mahmoud Ahmadinejad\} \\
-\{Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages\} \\
-\{Go Nagai bibliography, Go Nagai\} \\
-\{Galvatron, Megatron\} \\
-\{History of Australia (1901–45), History of Australia\} \\
-\{Interracial marriage, Miscegenation\} \\
-\{List of Prison Break recurring characters, List of Prison Break minor characters\} \\
-\{History of Eastern Orthodox Christian theology, History of the Orthodox Church\} \\
-\{69th Infantry Regiment (United States), 69th Infantry Regiment (New York)\} \\
-\{The Anarchy, Stephen, King of England\} \\
-\{History of painting, Western painting, 20th-century Western painting\} \\
-\{Sino-Pacific relations, Foreign relations of China\} \\
-\{History of the East–West Schism, East–West Schism\} \\
-\{History of the Detroit Tigers, Detroit Tigers\} \\
-\{San Francisco Giants, History of the San Francisco Giants\} \\
-\{Hernán Cortés, Oconahua, Jalisco\} \\
-\{List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)\} \\
-\{Port of Tianjin operations and logistics, Port of Tianjin\} \\
-\{American rock, Rock music\} \\
-\{One-Day Internationals in England in 2005, Test matches in England in 2005, Australian cricket team in England in 2005\} \\
-\{History of Christianity, History of Christianity of the Middle Ages\} \\
-\{History of the Texas Rangers (baseball), Texas Rangers (baseball)\} \\
-\{List of Irish Americans, List of Americans of Irish descent\} \\
-\{Radeon HD 3000 Series, R600 (ASIC)\} \\
-\{Robert Edmund Strahorn, Battle of Slim Buttes\} \\
-\{Cleveland Indians, History of the Cleveland Indians\} \\
-\{CIA leak scandal criminal investigation, Plame affair grand jury investigation\} \\
-\{History of Western civilization, History of Western civilization before AD 500\} \\
-\{Benigno Aquino III, Presidency of Benigno Aquino III\} \\
-\{Kingdom of Greece, History of modern Greece\} \\
-\{List of Russian people, List of Russian scientists\} \\
-\hline
-\end{tabular}
-}
-\label{toparticlegroups}
-\end{figure*}
-
-\section{Conclusions and Future Work}
+\red{Need to rework rest...}
 
@@
 
-\section{Acknowledgments}
-We would especially like to thank Dr. Jimmy Lin for his advise and directions.
+%\section{Acknowledgments}
+%We would especially like to thank Dr. Jimmy Lin for his advise and directions.
 
-\bibliographystyle{abbrv}
-\bibliography{article-draft}  % sigproc.bib is the name of the Bibliography in this case
+\bibliographystyle{aaai}
+\small
+\bibliography{wikisentences}
 
-\balancecolumns
 \end{document}

### 2013-12-29 src/main/wikiduper/analysis/HistogramClusters.java

@@ -350,8 +350,8 @@ public class HistogramClusters extends Configured implements Tool {
         histkeys.append(",");
         histkeys.append("\"");
         histkeys.append(rangel);
-        histkeys.append("-");
-        histkeys.append(rangeh);
+       // histkeys.append("-");
+       // histkeys.append(rangeh);
         histkeys.append("\"");
         histvals.append(",");
       histvals.append(sum);

### 2013-12-29 src/main/wikiduper/analysis/HistogramClusters.java
Shorter labels for histogram bins

@@ -315,8 +315,8 @@ public class HistogramClusters extends Configured implements Tool {
                 histkeys.append(",");
                 histkeys.append("\"");
                 histkeys.append(rangel);
-                histkeys.append("-");
-                histkeys.append(rangeh);
+                //histkeys.append("-");
+                //histkeys.append(rangeh);
                 histkeys.append("\"");
             histvals.append(",");
 //            histvals.append("{");

### 2013-12-29 src/main/wikiduper/analysis/HistogramClusters.java
Shorter labels for histogram bins

@@ -350,6 +350,7 @@ public class HistogramClusters extends Configured implements Tool {
         histkeys.append(",");
         histkeys.append("\"");
         histkeys.append(rangel);
+        histkeys.append("+");
        // histkeys.append("-");
        // histkeys.append(rangeh);
         histkeys.append("\"");

### 2013-12-29 src/main/wikiduper/analysis/HistogramClusters.java
Shorter labels for histogram bins

@@ -313,11 +313,13 @@ public class HistogramClusters extends Configured implements Tool {
                 int rangel = i-binsize;
                 int rangeh = i-1;
                 histkeys.append(",");
+                if(i%1000 == 0){
                 histkeys.append("\"");
                 histkeys.append(rangel);
                 //histkeys.append("-");
                 //histkeys.append(rangeh);
                 histkeys.append("\"");
+                }
             histvals.append(",");
 //            histvals.append("{");
             histvals.append(sum);
